### 2021-02-02 GALI.Rmd
rmds

---
title: "Data Responsive-report"
author: "Ouafaa Hmaddi"
date: "January 18, 2021"
output: html_document 
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}

#load libraries
#if (!requireNamespace("BiocManager", quietly = TRUE))
    #install.packages("BiocManager")

#BiocManager::install("preprocessCore")

library(rio)
library(tidyverse)
library(lubridate)
library(janitor)
library(ggplot2)
library(readxl)
library(reshape2)
library(readr)
library(psych)
library(foreign)
library(plm)
library(lme4)
library(lattice)
library(lmerTest)
library(EFAutilities)
library(haven)
library(sjPlot)
library(XLConnect)
library(preprocessCore)

```

##Function to extract summary model tables  
```{r}
lmOut <- function(res, file="test.csv", ndigit=3, writecsv=T) {
  if (length(grep('summary', class(res)))==0) res <- summary(res)
  co <- res$coefficients
  nvar <- nrow(co)
  ncoll <- ncol(co)
  f <- res$fstatistic
  formatter <- function(x) format(round(x,ndigit),nsmall=ndigit)
  # This sets the number of rows before we start recording the coefficients
  nstats <- 4
  # G matrix stores data for output
  G <- matrix("", nrow=nvar+nstats, ncol=ncoll+1)
  G[1,1] <- toString(res$call)
  # Save rownames and colnames
  G[(nstats+1):(nvar+nstats),1] <- rownames(co)
  G[nstats, 2:(ncoll+1)] <- colnames(co)
  # Save Coefficients
  G[(nstats+1):(nvar+nstats), 2:(ncoll+1)] <- formatter(co)
  # Save F-stat
  G[1,2] <- paste0("F(",f[2],",",f[3],")")
  G[2,2] <- formatter(f[1])
  # Save F-p value
  G[1,3] <- "Prob > P"
  G[2,3] <- formatter(1-pf(f[1],f[2],f[3]))
  # Save R2
  G[1,4] <- "R-Squared"
  G[2,4] <- formatter(res$r.squared)
  # Save Adj-R2
  G[1,5] <- "Adj-R2"
  G[2,5] <- formatter(res$adj.r.squared)
  print(G)
  if (writecsv) write.csv(G, file=file, row.names=F)
}

```

```{r Clean data from big firms, non-profit, and non respondants to follow-up survey}
gali <- import("GALI CLEANED 2019.xlsx") #19412 obs
gali <- filter(gali, fins_ft_employees_m1 <500 | is.na(fins_ft_employees_m1) ) #19401
gali <- filter(gali, info_legal_status == "For-profit company") #15433
gali <- filter(gali, found_additional_cnt < 10 | is.na(found_additional_cnt))

gali <- filter(gali, found_name1_prior_fp <10 | is.na(found_name1_prior_fp))
gali <- filter(gali, found_name2_prior_fp <10 | is.na(found_name2_prior_fp))
gali <- filter(gali, found_name3_prior_fp <10 | is.na(found_name3_prior_fp))
gali <- filter(gali, found_name1_prior_other <10 | is.na(found_name1_prior_other))
gali <- filter(gali, found_name2_prior_other <10 | is.na(found_name2_prior_other))
gali <- filter(gali, found_name3_prior_other <10 | is.na(found_name3_prior_other))
gali <- filter(gali, found_name1_prior_np <10 | is.na(found_name1_prior_np))
gali <- filter(gali, found_name2_prior_np <10 | is.na(found_name2_prior_np))
gali <- filter(gali, found_name3_prior_np <10 | is.na(found_name3_prior_np))
gali <- filter(gali, found_name1_age > 14 | is.na(found_name1_age))
gali <- filter(gali, found_name2_age > 14 | is.na(found_name2_age))
gali <- filter(gali, found_name3_age > 14 | is.na(found_name3_age))
gali <- filter(gali, found_name1_age < 70 | is.na(found_name1_age))
gali <- filter(gali, found_name2_age < 70 | is.na(found_name2_age))
gali <- filter(gali, found_name3_age < 70 | is.na(found_name3_age))

#gali <- filter(gali, finished == 1 | `fu1-report_any_prior_accelerator` == 1)
#gali$receivedHC <- ifelse(gali$finished == 0 & (gali$`fu1-report_any_prior_accelerator` == 0 | is.na(gali$`fu1-report_any_prior_accelerator`)) , 0, 1 )

#Keep only ventures with post acceleration information 
gali <- filter(gali, `fu1-report_followup_yes` == 1)

count(gali,info_venture_country_hq)

#Removing countries with less than 30 ventures.

#First, let's remove the US from the sample, 
gali <- filter(gali, info_venture_country_hq != "United States of America")

countries_to_keep <- gali %>% 
  group_by(gali$info_venture_country_hq) %>%
  summarize(Count=n()) %>%
  mutate(Percent = round((Count/sum(Count)*100))) %>%
  arrange(desc(Count))

#X countries have fewer than 70 firms in the sample. Because so few observations may not offer good representation, I excluded firms headquartered in these countries from the analysis, keeping X firms in Y countries and Z industries.

countries_to_keep <- filter(countries_to_keep, `gali$info_venture_country_hq` != 'NA')

countries_to_keep <- filter(countries_to_keep, Count >70)
countries_to_keep$`gali$info_venture_country_hq`

gali <- gali %>%
  filter(info_venture_country_hq  %in% countries_to_keep$`gali$info_venture_country_hq`)

#firms that are 5 years or younger when they entered the acceleration program (when data was collected)

if (gali$application_year == 2013) { gali <- filter(gali, info_founding_year > 2007)
}  else if (gali$application_year == 2014) {gali <- filter(gali, info_founding_year > 2008)
} else if (gali$application_year == 2015) {gali <- filter(gali, info_founding_year > 2009)
}  else if (gali$application_year == 2016) {gali <- filter(gali, info_founding_year > 2010)
} else if (gali$application_year == 2017) {gali <- filter(gali, info_founding_year > 2011)
}  else gali <- filter(gali, info_founding_year > 2012)

```

##Constrcuting human capital index (control variable)
###Graduate percentage, Prior C-level Executive Percentage, Average Team Tenure , Team Prior Founding

```{r Human capital index}
#Graduate percentage

gali$founder1_grad = ifelse(gali$found_name1_education == "Masters Degree" | 
                              gali$found_name1_education =="PhD" |
                              gali$found_name1_education == "Some graduate degree", 1, 0) 
gali$founder1_grad[is.na(gali$founder1_grad)] <- 0

gali$founder2_grad = ifelse(gali$found_name2_education == "Masters Degree" | 
                              gali$found_name2_education =="PhD" |
                              gali$found_name2_education == "Some graduate degree", 1, 0) 
gali$founder2_grad[is.na(gali$founder2_grad)] <- 0

gali$founder3_grad = ifelse(gali$found_name3_education == "Masters Degree" |
                              gali$found_name3_education =="PhD" |
                              gali$found_name3_education == "Some graduate degree", 1, 0)
gali$founder3_grad[is.na(gali$founder3_grad)] <- 0

gali$nb_of_founders <- gali$found_name1_present + gali$found_name2_present + gali$found_name3_present

gali <- filter(gali, nb_of_founders > 0)

gali$grad_pct = ((gali$founder1_grad + gali$founder2_grad + gali$founder3_grad) / gali$nb_of_founders)

#Prior C-level Executive Percentage

gali$founder1_job1_clevel = ifelse(is.na(gali$found_name1_job1_role) | gali$found_name1_job1_role !=  "CEO/Executive Director" , 0, 1)
gali$founder1_job2_clevel = ifelse(is.na(gali$found_name1_job2_role) | gali$found_name1_job2_role !=  "CEO/Executive Director" , 0, 1)
gali$founder2_job1_clevel = ifelse(is.na(gali$found_name2_job1_role) | gali$found_name2_job1_role !=  "CEO/Executive Director" , 0, 1)
gali$founder2_job2_clevel = ifelse(is.na(gali$found_name2_job2_role) | gali$found_name2_job2_role !=  "CEO/Executive Director" , 0, 1)
gali$founder3_job1_clevel = ifelse(is.na(gali$found_name3_job1_role) | gali$found_name3_job1_role !=  "CEO/Executive Director" , 0, 1)
gali$founder3_job2_clevel = ifelse(is.na(gali$found_name3_job2_role) | gali$found_name3_job2_role !=  "CEO/Executive Director" , 0, 1)

gali$prior_clevel_pct = ((gali$founder1_job1_clevel + gali$founder1_job2_clevel + gali$founder2_job1_clevel + 
  gali$founder2_job2_clevel + gali$founder3_job1_clevel + gali$founder3_job2_clevel) / (gali$nb_of_founders*2))

#Average Team Tenure

gali$avg_teamtenure <- rowMeans(subset(gali, select = c('found_name1_job1_tenure', 'found_name1_job2_tenure', 'found_name2_job1_tenure', 'found_name2_job2_tenure', 'found_name3_job1_tenure', 'found_name3_job2_tenure')), na.rm = TRUE)

gali$avg_teamtenure[is.nan(gali$avg_teamtenure)] <- 0

#Team Prior Founding
gali$team_prior_founding <- gali$found_name1_prior_fp + gali$found_name2_prior_fp + gali$found_name3_prior_fp + gali$found_name1_prior_other + gali$found_name2_prior_other + gali$found_name3_prior_other + gali$found_name1_prior_np + gali$found_name2_prior_np + gali$found_name3_prior_np

#Final Human Capital Index

gali$z_team_prior_founding <- scale(gali$team_prior_founding, center = TRUE, scale = TRUE)
gali$z_prior_clevel_pct <- scale(gali$prior_clevel_pct, center = TRUE, scale = TRUE)
gali$z_avg_teamtenure <- scale(gali$avg_teamtenure, center = TRUE, scale = TRUE)
gali$z_grad_pct <- scale(gali$grad_pct, center = TRUE, scale = TRUE)

#Cite Bolstad et al, Bioinformatics (2003)

gali$normq_team_prior_founding <- normalize.quantiles(gali$z_team_prior_founding,copy=TRUE)
gali$normq_prior_clevel_pct <- normalize.quantiles(gali$z_prior_clevel_pct,copy=TRUE)
gali$normq_avg_teamtenure <- normalize.quantiles(gali$z_avg_teamtenure,copy=TRUE)
gali$normq_grad_pct <- normalize.quantiles(gali$z_grad_pct,copy=TRUE)

#group all into an index

gali$HC_index <- (gali$normq_team_prior_founding + gali$normq_prior_clevel_pct + gali$normq_avg_teamtenure + gali$normq_grad_pct)

```

##Constrcuting social capital index (control variable)

```{r}

```

##Constrcuting financial capital index (control variable)

```{r}

```

##Gender decomposition variable

```{r Gender decomposition variable}
gali <- gali %>% drop_na(found_name1_gender)

gali$found_name2_gender[is.na(gali$found_name2_gender)] <- 0
gali$found_name3_gender[is.na(gali$found_name3_gender)] <- 0

gali$founder1_f <- ifelse(gali$found_name1_gender == "F", 1,0)
gali$founder2_f <- ifelse(gali$found_name2_gender == "F", 1,0)
gali$founder3_f <- ifelse(gali$found_name3_gender == "F", 1,0)

gali$female_pct <- round(((gali$founder1_f + gali$founder2_f + gali$founder3_f) / gali$nb_of_founders ), 2)

```

```{r Cleaning data of acceleration benefit ranking }

#Removing ventures that ranked benefits outside of given scale (i.e. 1 to 7)

gali <- filter(gali, accel_ben_rank_network <= 7 & accel_ben_rank_business_skills
<= 7 & accel_ben_rank_mentorship <= 7 & accel_ben_rank_access_investors <= 7 & accel_ben_rank_direct_funding <= 7 & accel_ben_rank_access_entreprene <= 7 & accel_ben_rank_aware_cred <= 7 )

#Removing ventures that gave the same ranking to two or more benefits 
gali <- filter(gali, 
               accel_ben_rank_network != accel_ben_rank_business_skills &
                 accel_ben_rank_network != accel_ben_rank_mentorship & 
                 accel_ben_rank_network != accel_ben_rank_access_investors &
                 accel_ben_rank_network != accel_ben_rank_direct_funding &
                 accel_ben_rank_network != accel_ben_rank_access_entreprene &
                 accel_ben_rank_network != accel_ben_rank_aware_cred )

gali <- filter(gali, 
                 accel_ben_rank_business_skills != accel_ben_rank_mentorship & 
              accel_ben_rank_business_skills != accel_ben_rank_access_investors &
                 accel_ben_rank_business_skills != accel_ben_rank_direct_funding &
              accel_ben_rank_business_skills != accel_ben_rank_access_entreprene &
                 accel_ben_rank_business_skills != accel_ben_rank_aware_cred )

gali <- filter(gali, 
                accel_ben_rank_mentorship != accel_ben_rank_access_investors &
                 accel_ben_rank_mentorship != accel_ben_rank_direct_funding &
                 accel_ben_rank_mentorship != accel_ben_rank_access_entreprene &
                 accel_ben_rank_mentorship != accel_ben_rank_aware_cred )

gali <- filter(gali, 
              accel_ben_rank_access_investors != accel_ben_rank_direct_funding &
            accel_ben_rank_access_investors != accel_ben_rank_access_entreprene &
                 accel_ben_rank_access_investors != accel_ben_rank_aware_cred )

gali <- filter(gali, 
              accel_ben_rank_direct_funding != accel_ben_rank_access_entreprene &
                 accel_ben_rank_direct_funding != accel_ben_rank_aware_cred )

gali <- filter(gali, 
              accel_ben_rank_access_entreprene != accel_ben_rank_aware_cred )

```

#Rnak 1 shows the most important benefit (highest attention)

```{r}

#Calculating the average of different benifits to group them into one of the 3 categories of capital plus signaling. Then making the range of values between 0 and 1

gali$attention_HC <- round((rowMeans(gali[,
                                  c('accel_ben_rank_business_skills',
                                    'accel_ben_rank_mentorship')],
                              na.rm=TRUE) / 7),2)

gali$attention_signaling <- round((gali$accel_ben_rank_aware_cred / 7),2)

gali$attention_SC <- round((rowMeans(gali[,
                                  c('accel_ben_rank_network',
                                'accel_ben_rank_access_entreprene')],
                              na.rm=TRUE) / 7),2)

gali$attention_FC <- round((rowMeans(gali[,
                                c('accel_ben_rank_access_investors',
                                  'accel_ben_rank_direct_funding')],
                              na.rm=TRUE) / 7),2)

#the lowest the value the highest the attention 
#I will then mutiply this by the country index to measure the congruence level

range(gali$attention_signaling)
```

```{r Capital structure study variables}

##Total invesmtment
gali_0$tot_cap_m1 <- rowSums(gali_0[ , c('inv_ownmoney_m1', 'inv_outequity_m1', 'inv_totaldebt_m1', 'inv_philan_m1')],na.rm = TRUE)

gali_0$tot_cap_sincefound <- rowSums(gali_0[ , c('inv_ownmoney_sincefound', 'inv_outequity_sincefound', 'inv_totaldebt_sincefound', 'inv_philan_sincefound')],na.rm = TRUE)

gali_0$fu1_tot_cap_m1 <- rowSums(gali_0[ , c('fu1-inv_ownmoney_m1', 'fu1-inv_outequity_m1', 'fu1-inv_totaldebt_m1', 'fu1-inv_philan_m1')],na.rm = TRUE)

##Percentage of each capital type 
###Equity
gali_0$pctequity_m1 <- gali_0$inv_outequity_m1 / gali_0$tot_cap_m1
gali_0$pctequity_sincefound <- gali_0$inv_outequity_sincefound / gali_0$tot_cap_sincefound
gali_0$fu1_pctequity_m1 <- gali_0$`fu1-inv_outequity_m` / gali_0$fu1_tot_cap_m1

###Debt
gali_0$pctdebt_m1 <- gali_0$inv_totaldebt_m1 / gali_0$tot_cap_m1
gali_0$pctdebt_sincefound <- gali_0$inv_totaldebt_sincefound / gali_0$tot_cap_sincefound
gali_0$fu1_pctdebt_m1 <- gali_0$`fu1-inv_totaldebt_m` / gali_0$fu1_tot_cap_m1

###Own Money
gali_0$pctownmoney_m1 <- gali_0$inv_ownmoney_m1 / gali_0$tot_cap_m1
gali_0$pctownmoney_sincefound <- gali_0$inv_ownmoney_sincefound / gali_0$tot_cap_sincefound
gali_0$fu1_pctownmoney_m1 <- gali_0$`fu1-inv_ownmoney_m` / gali_0$fu1_tot_cap_m1

###Phillantropy
gali_0$pctphilan_m1 <- gali_0$inv_philan_m1 / gali_0$tot_cap_m1
gali_0$pctphilan_sincefound <- gali_0$inv_philan_sincefound / gali_0$tot_cap_sincefound
gali_0$fu1_pctphilan_m1 <- gali_0$`fu1-inv_philan_m` / gali_0$fu1_tot_cap_m1

##Single source vs dominant source (> 90%)
###Single source
gali_0$single_source_m1 <- ifelse(gali_0$pctequity_m1 == 1 | 
                                  gali_0$pctdebt_m1 == 1|
                                  gali_0$pctownmoney_m1 == 1 |
                                  gali_0$pctphilan_m1 ==1 , 1, 0)

gali_0$single_source_sincefound <- ifelse(gali_0$pctequity_sincefound == 1 | 
                                  gali_0$pctdebt_sincefound == 1|
                                  gali_0$pctownmoney_sincefound == 1 |
                                  gali_0$pctphilan_sincefound ==1 , 1, 0)

gali_0$single_fu1_source_m1 <- ifelse(gali_0$fu1_pctequity_m1 == 1 | 
                                  gali_0$fu1_pctdebt_m1 == 1|
                                  gali_0$fu1_pctownmoney_m1 == 1 |
                                  gali_0$fu1_pctphilan_m1 ==1 , 1, 0)

###Dominant source
gali_0$dominant_source_m1 <- ifelse((gali_0$pctequity_m1 >= .9 | 
                                  gali_0$pctdebt_m1 >= .9 |
                                  gali_0$pctownmoney_m1 >= .9 |
                                  gali_0$pctphilan_m1 >= .9) &
                                    gali_0$single_source_m1 == 0, 1, 0)

gali_0$dominant_source_sincefound <- ifelse((gali_0$pctequity_sincefound >= .9 | 
                                  gali_0$pctdebt_sincefound >= .9 |
                                  gali_0$pctownmoney_sincefound >= .9 |
                                  gali_0$pctphilan_sincefound >= .9) &
                                  gali_0$single_source_m1 == 0, 1, 0)

gali_0$dominant_fu1_source_m1 <- ifelse((gali_0$fu1_pctequity_m1 >= .9 | 
                                  gali_0$fu1_pctdebt_m1 >= .9 |
                                  gali_0$fu1_pctownmoney_m1 >= .9 |
                                  gali_0$fu1_pctphilan_m1 >= .9) &
                                  gali_0$single_source_m1 == 0, 1, 0)
```

```{r Apirations for capital structure in 12 months and 3 years }
##Total aspired  invesmtment Pre-acceleration 
gali_0$tot_plans_cap_12m <- rowSums(gali_0[ , c('inv_plans_outequity_12months', 'inv_plans_debt_12months', 'inv_plans_philan_12months')],na.rm = TRUE)

gali_0$tot_plans_cap_3y <- rowSums(gali_0[ , c('inv_plans_outequity_3years', 'inv_plans_debt_3years', 'inv_plans_philan_3years')], na.rm = TRUE)

##Total aspired  invesmtment Post-acceleration 
gali_0$fu1_tot_plans_cap_12m <- rowSums(gali_0[ , c('fu1-inv_plans_outequity_12months', 'fu1-inv_plans_debt_12months', 'fu1-inv_plans_philan_12months')], na.rm = TRUE)

gali_0$fu1_tot_plans_cap_3y <- rowSums(gali_0[ , c('fu1-inv_plans_outequity_3years', 'fu1-inv_plans_debt_3years', 'fu1-inv_plans_philan_3years')], na.rm = TRUE)

##Aspired percentage of each capital type pre-acceleration 
###Equity
gali_0$pctequity_plan12m <- gali_0$inv_plans_outequity_12months / gali_0$tot_plans_cap_12m
gali_0$pctequity_plan3y <- gali_0$inv_plans_outequity_3years / gali_0$tot_plans_cap_3y

###Debt
gali_0$pctdebt_m1 <- gali_0$inv_plans_debt_12months / gali_0$tot_plans_cap_12m
gali_0$pctdebt_sincefound <- gali_0$inv_plans_debt_3years / gali_0$tot_plans_cap_3y

###Phillantropy
gali_0$pctphilan_m1 <- gali_0$inv_plans_philan_12months / gali_0$tot_plans_cap_12m
gali_0$pctphilan_sincefound <- gali_0$inv_plans_philan_3years / gali_0$tot_plans_cap_3y

##Aspired percentage of each capital type post-acceleration 
###Equity
gali_0$fu1_pctequity_plan12m <- gali_0$`fu1-inv_plans_outequity_12months` / gali_0$fu1_tot_plans_cap_12m
gali_0$fu1_pctequity_plan3y <- gali_0$`fu1-inv_plans_outequity_3years` / gali_0$fu1_tot_plans_cap_3y

###Debt
gali_0$fu1_pctdebt_plan12m <- gali_0$`fu1-inv_plans_debt_12months` / gali_0$fu1_tot_plans_cap_12m
gali_0$fu1_pctdebt_plan3y <- gali_0$`fu1-inv_plans_debt_3years` / gali_0$fu1_tot_plans_cap_3y

###Phillantropy
gali_0$fu1_pctphilan_plan12m <- gali_0$`fu1-inv_plans_philan_12months` / gali_0$fu1_tot_plans_cap_12m
gali_0$fu1_pctphilan_plan3y <- gali_0$`fu1-inv_plans_philan_3years` / gali_0$fu1_tot_plans_cap_3y

```

#Country indices to interact with venture attention and construct conguence level

```{r Merge with GEM NES NATIONAL data}

gem15 <- import("GEM 2015 NES NATIONAL.sav")
gem14 <- import("GEM 2014 NES NATIONAL.sav")
gem13 <- import("GEM 2013 NES NATIONAL.sav")

#GEM Selecting only Human Capital Variables (HC = human capital)

gem_HC15 <-gem15 %>%
  select(NES15COUNTRY, NES15RNAME, NES15_C02_MEAN9, NES15_D01_MEAN9, NES15_D02_MEAN9, NES15_D03_MEAN9, NES15_D04_MEAN9, NES15_D05_MEAN9, NES15_D06_MEAN9, ZNES15D1SUM9, ZNES15D2SUM9,   EU, OECD, BRICS)

gem_HC14 <-gem14 %>%
  select(NES14COUNTRY, NES14RNAME, NES14_C02_MEAN, NES14_D01_MEAN, NES14_D02_MEAN, NES14_D03_MEAN, NES14_D04_MEAN, NES14_D05_MEAN, NES14_D06_MEAN, ZNES14D1SUM, ZNES14D2SUM,   EU, OECD, BRICS)

gem_HC13 <-gem13 %>%
  select(NES13COUNTRY, NES13RNAME, NES13_C02_MEAN, NES13_D01_MEAN, NES13_D02_MEAN, NES13_D03_MEAN, NES13_D04_MEAN, NES13_D05_MEAN, NES13_D06_MEAN, ZNES13D1SUM, ZNES13D2SUM,   EU, OECD, BRICS)

gem <- bind_rows(gem_HC15, gem_HC14, gem_HC13)

gem$NES15RNAME[gem$NES15RNAME == "UK"] <-"UNITED KINGDOM OF GREAT BRITAIN AND NORTHERN IRELAND"

gem$NES15RNAME[gem$NES15RNAME == "NETEHERLANDS"] <- "NETHERLANDS"

gem1 <- bind_rows(gem_HC14, gem_HC15, gem_HC13)

gem1$NES14RNAME[gem1$NES14RNAME == "UK"] <-"UNITED KINGDOM OF GREAT BRITAIN AND NORTHERN IRELAND"
gem1$NES14RNAME[gem1$NES14RNAME == "NETEHERLANDS"] <- "NETHERLANDS"

gem2 <- bind_rows(gem_HC13, gem_HC15, gem_HC14)

gem2$NES13RNAME[gem2$NES13RNAME == "UK"] <-"UNITED KINGDOM OF GREAT BRITAIN AND NORTHERN IRELAND"
gem2$NES13RNAME[gem2$NES13RNAME == "NETEHERLANDS"] <- "NETHERLANDS"

gali[,8] <- toupper(gali[,8])

gem_HC <- rename(gem, "info_venture_country_hq" = "NES15RNAME")

gem_HC1 <- rename(gem1, "info_venture_country_hq" = "NES14RNAME")

gem_HC2 <- rename(gem2, "info_venture_country_hq" = "NES13RNAME")

gali_NES <- left_join( gali, gem_HC,  by = "info_venture_country_hq")

gali_NES1 <- left_join(gali, gem_HC1, by = "info_venture_country_hq")

gali_NES1 <- filter(gali_NES1 , info_venture_country_hq == "UGANDA" | info_venture_country_hq == "EL SALVADOR")

gali_NES2 <- left_join(gali, gem_HC2, by = "info_venture_country_hq")

gali_NES2 <- filter(gali_NES2 , info_venture_country_hq == "ZAMBIA" | info_venture_country_hq == "GHANA" | info_venture_country_hq == "NIGERIA")

galiNES <- bind_rows(gali_NES, gali_NES1, gali_NES2)

countries_list <- galiNES %>% 
  group_by(galiNES$info_venture_country_hq) %>%
  summarize(Count=n()) %>%
  mutate(Percent = round((Count/sum(Count)*100))) %>%
  arrange(desc(Count))

```

```{r Merge with GEM APS data}
#APS0 <- import("GEM 2016 APS Global.sav")
APS <- APS0 %>% 
  select(suskill, country, ctryalp) %>%
  group_by(country) %>%
  summarise(skill_mean = mean(suskill, na.rm=TRUE))

APS <- rename(APS, "NES15COUNTRY" = "country")

gali_NESAPS <- merge(gali_NES, APS, by = "NES15COUNTRY")

countries_list <- filter(countries_list, Count > 25)

gali_GEM <- gali_NESAPS %>%
  filter(info_venture_country_hq  %in% countries_list$`gali_NES$info_venture_country_hq`)

```

```{r}
# Create dummy variables
gali_GEM$res_man <- ifelse(gali_GEM$most_important_benefit=="acc_managerial", 1, 0)
gali_GEM$res_fin <- ifelse(gali_GEM$most_important_benefit=="acc_financial_max", 1, 0)
gali_GEM$res_soc <- ifelse(gali_GEM$most_important_benefit=="acc_social_max", 1, 0)
gali_GEM$res_sig <- ifelse(gali_GEM$most_important_benefit=="acc_signaling", 1, 0)

#Renaming for plot purposes 
gali_GEM$info_venture_country_hq[gali_GEM$info_venture_country_hq == "UNITED STATES OF AMERICA"] <-"USA"

gali_GEM$info_venture_country_hq[gali_GEM$info_venture_country_hq == "UNITED KINGDOM OF GREAT BRITAIN AND NORTHERN IRELAND"] <-"UNITED KINGDOM"

gali_GEM_noUS <- filter(gali_GEM, info_venture_country_hq != "USA")

```

###ANALYSIS BASED ON GALI_GEM data to evaluate normative and cognitive differences and the impact of human capital as an acceleration resource

```{r}
#Summary table

#ls(gali_GEM)

#IV res_man Attention to human capital by the founders 
#DVs fins_revenues_m1 fu1-fins_revenues_m1 fins_revenues_sincefound

gali_GEM$y1_revenue <- gali_GEM$`fu1-fins_revenues_m1` - gali_GEM$fins_revenues_m1
gali_GEM$y1_ownmoeny <- gali_GEM$`fu1-inv_ownmoney_m1` - gali_GEM$inv_ownmoney_m1
gali_GEM$y1_aspiration_cap <- gali_GEM$fu1_tot_plans_cap_12m - gali_GEM$tot_plans_cap_12m
gali_GEM$y1_raised_cap <- gali_GEM$fu1_tot_cap_m1 - gali_GEM$tot_cap_m1

fu1-inv_plans_outequity_12months
fu1-inv_plans_outequity_3years
fu1_tot_plans_cap_12m

#Controls

fu1-report_any_prior_accelerator

#Revenue as a DV

revenue_lm_b <- lm(`fu1-fins_revenues_m1` ~ res_man, data = gali_GEM_noUS)
summary(revenue_lm_b)

revenue_lm <- lm(`fu1-fins_revenues_m1` ~ res_man + `fu1-report_any_prior_accelerator` + finished + fins_ft_employees_m1 ,
                 data = gali_GEM)
summary(revenue_lm)

revenue_lm_cog <- lm(`fu1-fins_revenues_m1` ~ res_man + res_man*skill_mean + `fu1-report_any_prior_accelerator` + fins_ft_employees_m1, data = gali_GEM)
summary(revenue_lm_cog)

revenue_lm_norm <- lm(`fu1-fins_revenues_m1` ~ res_man + res_man*ZNES15D2SUM9 +  res_man*skill_mean+ `fu1-report_any_prior_accelerator` + fins_ft_employees_m1+ finished, data = gali_GEM)
summary(revenue_lm_norm)
+ fins_ft_employees_m1 + finished

#Capital aspirations as a DV

lm_b <- lm(fins_revenues_m1  ~ receivedHC*res_man  , data = gali_GEM)

summary(lm_b)

lmOut(lm_b, file =  "results_asp22.csv")

ggplot(gali_GEM, aes(skill_mean, ZNES15D2SUM9, label= info_venture_country_hq))+
  geom_point(colour = "Light Blue")+
  geom_text(check_overlap = TRUE, size = 2.5, nudge_y = 0.1)+
  theme_minimal()+
  xlab("Cognitive acceptance")+
  ylab("Normative acceptance")

gali_GEM %>% 
  group_by(info_venture_country_hq) %>%
  summarise(mean(NES15D2SUM_MEAN9))

gali_GEM %>% 
  group_by(info_venture_country_hq) %>%
  summarise(mean(NES15_D01_MEAN9))

```

```{r fig.width=15}
ggplot(gali_GEM, aes(info_venture_country_hq))+
  geom_histogram(stat = "count")+
  theme(axis.text.x = element_text(angle = -80))

```

```{r Merge with VIMBI data}
vimbi <-  import("vimbi2017.xlsx") #211 obs
vimbi <- rename(vimbi, "info_venture_country_hq" = "Country: World Bank name")
vimbi <- clean_names(vimbi)

gali_vimbi <- merge(gali_0,vimbi, by = "info_venture_country_hq")

```

```{r}
# Create dummy variables
gali_vimbi$res_man <- ifelse(gali_vimbi$most_important_benefit=="acc_managerial", 1, 0)
gali_vimbi$res_fin <- ifelse(gali_vimbi$most_important_benefit=="acc_financial_max", 1, 0)
gali_vimbi$res_soc <- ifelse(gali_vimbi$most_important_benefit=="acc_social_max", 1, 0)
gali_vimbi$res_sig <- ifelse(gali_vimbi$most_important_benefit=="acc_signaling", 1, 0)

gali_vimbi <- filter(gali_vimbi, tot_cap_sincefound < 10000000)

#res_fe_mod <- lm(res_sig ~ x3_cp_capital_rank_percent_2016_h_good, 
                    #data = gali_vimbi)

vimbi$gni_capita_10_year_growth_2006_2015 <- as.numeric(vimbi$gni_capita_10_year_growth_2006_2015)

ggplot(gali_vimbi, aes(x=fins_revenues_sincefound, y=x1_lb_labour_flexibility_education_support_2016_h_good, colour=factor(res_sig))) +
  geom_point() +
  scale_x_log10()

hlm <- lmer(log1p(fins_revenues_sincefound)~1+(1|x1_lb_labour_flexibility_education_support_2016_h_good), gali_vimbi)

summary(hlm)

with(gali_vimbi, tapply(fins_revenues_sincefound, x1_lb_labour_flexibility_education_support_2016_h_good, mean))
coef(hlm)

dt_matrix <- cor(na.omit(vimbi[ ,3:8]))

cortest.bartlett(na.omit(vimbi[ ,3:8]))

det(dt_matrix)

pc1 <- principal(na.omit(vimbi[ ,3:8]), nfactors=3, rotate="none")
plot(pc1$values, type = "b")

efaMR(x=na.omit(vimbi[ ,3:8]), factors=3, covmat=NULL, n.obs=151, 
      dist='normal', fm='ols', rtype='orthogonal', rotation = 'CF-varimax', 
      input.A=NULL, additionalRC = NULL, 
      nstart = 100, compare = 'First', plot = T, cex = .5,
      normalize = FALSE, geomin.delta = .01, 
      MTarget = NULL, MWeight = NULL, PhiTarget = NULL, PhiWeight = NULL, 
      useorder = FALSE, mnames = NULL, fnames = NULL, wxt2 = 1)

bwplot(x1_lb_labour_flexibility_education_support_2016_h_good~resid(hlm), gali_vimbi)

```

```{r Clean data from for profit ventures that included philantropy in their capital structure }

#gali_0 <- filter(gali_0,pctphilan_sincefound == 0 )

```

```{r fig.width=15}
ggplot(gali_0, aes(info_venture_country_hq))+
  geom_histogram(stat = "count")+
  theme(axis.text.x = element_text(angle = -80))

```

### 2021-02-02 GALI_2020.Rmd
rmds

--- 2021-02-02 GALI.Rmd
@@
 #if (!requireNamespace("BiocManager", quietly = TRUE))
-    #install.packages("BiocManager")
+#install.packages("caret")
 
@@
 library(preprocessCore)
+library(knitr)
+library(caret)
 
@@
 
-```{r Clean data from big firms, non-profit, and non respondants to follow-up survey}
-gali <- import("GALI CLEANED 2019.xlsx") #19412 obs
-gali <- filter(gali, fins_ft_employees_m1 <500 | is.na(fins_ft_employees_m1) ) #19401
-gali <- filter(gali, info_legal_status == "For-profit company") #15433
-gali <- filter(gali, found_additional_cnt < 10 | is.na(found_additional_cnt))
-
-gali <- filter(gali, found_name1_prior_fp <10 | is.na(found_name1_prior_fp))
-gali <- filter(gali, found_name2_prior_fp <10 | is.na(found_name2_prior_fp))
-gali <- filter(gali, found_name3_prior_fp <10 | is.na(found_name3_prior_fp))
-gali <- filter(gali, found_name1_prior_other <10 | is.na(found_name1_prior_other))
-gali <- filter(gali, found_name2_prior_other <10 | is.na(found_name2_prior_other))
-gali <- filter(gali, found_name3_prior_other <10 | is.na(found_name3_prior_other))
-gali <- filter(gali, found_name1_prior_np <10 | is.na(found_name1_prior_np))
-gali <- filter(gali, found_name2_prior_np <10 | is.na(found_name2_prior_np))
-gali <- filter(gali, found_name3_prior_np <10 | is.na(found_name3_prior_np))
-gali <- filter(gali, found_name1_age > 14 | is.na(found_name1_age))
-gali <- filter(gali, found_name2_age > 14 | is.na(found_name2_age))
-gali <- filter(gali, found_name3_age > 14 | is.na(found_name3_age))
-gali <- filter(gali, found_name1_age < 70 | is.na(found_name1_age))
-gali <- filter(gali, found_name2_age < 70 | is.na(found_name2_age))
-gali <- filter(gali, found_name3_age < 70 | is.na(found_name3_age))
-
-#gali <- filter(gali, finished == 1 | `fu1-report_any_prior_accelerator` == 1)
-#gali$receivedHC <- ifelse(gali$finished == 0 & (gali$`fu1-report_any_prior_accelerator` == 0 | is.na(gali$`fu1-report_any_prior_accelerator`)) , 0, 1 )
-
-#Keep only ventures with post acceleration information 
-gali <- filter(gali, `fu1-report_followup_yes` == 1)
+```{r Countries to analyse in main sample}
+gali <- import("Data/GALI_External_DataRelease_2020.xlsx")
 
@@
 
-#Removing countries with less than 30 ventures.
-
-#First, let's remove the US from the sample, 
-gali <- filter(gali, info_venture_country_hq != "United States of America")
+#Removing countries with less than 6 ventures.
 
@@
 
-countries_to_keep <- filter(countries_to_keep, Count >70)
+countries_to_keep <- filter(countries_to_keep, Count >6)
 countries_to_keep$`gali$info_venture_country_hq`
@@
   filter(info_venture_country_hq  %in% countries_to_keep$`gali$info_venture_country_hq`)
+
+#Number of ventures in main sample 
+#kable(countries_to_keep)
+
+```
+
+```{r}
+gali <- filter(gali, found_name1_age > 14 | is.na(found_name1_age))
+gali <- filter(gali, found_name2_age > 14 | is.na(found_name2_age))
+gali <- filter(gali, found_name3_age > 14 | is.na(found_name3_age))
+gali <- filter(gali, found_name1_age < 70 | is.na(found_name1_age))
+gali <- filter(gali, found_name2_age < 70 | is.na(found_name2_age))
+gali <- filter(gali, found_name3_age < 70 | is.na(found_name3_age))
+
+#Keep only ventures with 3 years of post acceleration information 
+gali <- filter(gali, fu1report_followup_yes == 1 & fu2report_followup_yes == 1 & fu3report_followup_yes == 1)
 
@@
 }  else gali <- filter(gali, info_founding_year > 2012)
+```
+
+```{r Countries to keep in sample with valid data}
+
+gali <- gali %>%
+  rename(country = info_venture_country_hq) %>%
+  rename(year = program_year)
+
+gali$country[gali$country == "United States of America"] <-"USA"
+gali$country[gali$country == "Tanzania, United Republic of"] <-"Tanzania"
+
+countries_to_keep <- gali %>% 
+  group_by(gali$country) %>%
+  summarize(Count=n()) %>%
+  mutate(Percent = round((Count/sum(Count)*100))) %>%
+  arrange(desc(Count))
+
+countries_to_keep <- filter(countries_to_keep, `gali$country` != 'NA')
+
+countries_to_keep <- filter(countries_to_keep, Count >6)
+countries_to_keep$`gali$country`
+
+gali <- gali %>%
+  filter(country  %in% countries_to_keep$`gali$country`)
+
+#Number of ventures in main sample 
+#kable(countries_to_keep)
+```
+
+#GEM NES Data
+
+```{r}
+gem_nes <- import("Data/GEM-NES.csv")
+
+#Clean and tidy gem NES
+gem_nes <- clean_names(gem_nes)
+gem_nes <- gem_nes %>%
+  row_to_names(row_number = 2)
+
+gem_nes[,-2] <- gem_nes[,-2] %>% mutate_if(is.character,as.numeric)
+
+gem_nes$inst_hc_nes <- rowMeans(gem_nes[,(5:6)])
+gem_nes <- clean_names(gem_nes)
+gem_nes <- gem_nes %>%
+  rename(country = economy) %>%
+  rename(inst_fc_gem = 	financing_for_entrepreneurs)
+
+gem_nes <- gem_nes [, -(5:6)]
+
+#Normalize NES data (all data is based on a scale from 1 to 5)
+preproc_nes <- preProcess(gem_nes[,(4:5)], method=c("range"))
+gem_nes <- predict(preproc_nes, gem_nes)
+
+```
+
+#GEM APS data
+
+```{r}
+gem_aps <- import("Data/GEM-APS.csv")
+#Clean and tidy gem APS
+gem_aps <- clean_names(gem_aps)
+gem_aps <- gem_aps %>%
+  row_to_names(row_number = 2)
+gem_aps[,-2] <- gem_aps[,-2] %>% mutate_if(is.character,as.numeric)
+gem_aps <- clean_names(gem_aps)
+gem_aps <- gem_aps %>%
+  rename(country = economy) %>%
+  rename(inst_signaling_aps = high_status_to_successful_entrepreneurs)%>%
+  rename(inst_hc_aps = established_business_ownership) %>%
+  rename(inst_sc_aps = total_early_stage_entrepreneurial_activity_tea)
+
+#All APS data is a percentage. We devide by 100 to gat [0,1] range
+gem_aps$inst_signaling_gem <- gem_aps$inst_signaling_aps /100
+gem_aps$inst_hc_aps <- gem_aps$inst_hc_aps /100
+gem_aps$inst_sc_gem <- gem_aps$inst_sc_aps /100
+
+```
+
+#Final GEM data
+
+```{r}
+#join nes and aps on country and year 
+gem <- left_join(gem_nes, gem_aps, by=c("country", "year", "code"))
+gem$inst_hc_gem <- rowMeans(gem[,c("inst_hc_nes", "inst_hc_aps")])
+
+gem <- gem %>%
+  select(code, country, year, ends_with('_gem'))
+
+gem$country[gem$country == "United States"] <-"USA"
+
+gem <- gem %>%
+  group_by(country) %>%
+  mutate(inst_fc_gem = mean(inst_fc_gem, na.rm= TRUE),
+  inst_hc_gem = mean(inst_hc_gem, na.rm= TRUE),
+  inst_sc_gem = mean(inst_sc_gem, na.rm= TRUE),
+  inst_signaling_gem = mean(inst_signaling_gem, na.rm= TRUE))
+
+gem <- select(gem, -year)
+
+gem <- gem %>% distinct()
+
+```
+
+#CGI data
+```{r}
+gci <- import("Data/GCI_2018.xlsx")
+
+gci <- filter(gci, `Series Global ID` == "EOSQ089" |
+                   `Series Global ID` == "EOSQ425" )
+gci <- filter(gci, Edition ==2018 )
+
+gci <- filter(gci, Attribute == "VALUE")
+gci <- select(gci, -c("Index", "Edition", "Freeze date", "Series units", "Series order", "Series code (if applicable)", "Attribute", "Series name"))
+
+gci <- gci %>%
+  gather(country, score, -`Series Global ID`)
+
+gci$country[gci$country == "United States"] <-"USA"
+
+gci <- gci %>%
+  filter(country  %in% countries_to_keep$`gali$country`)
+
+gci$score <- round(as.numeric(gci$score),2)
+
+gci <- clean_names(gci)
+
+gci <- gci %>%
+  pivot_wider(names_from = series_global_id, 
+              values_from = score)
+preproc_gci <- preProcess(gci %>%
+                            select(starts_with("EOSQ"))
+                          , method=c("range"))
+gci <- predict(preproc_gci, gci)
+
+gci$inst_fc_gci <- rowMeans(gci[,c('EOSQ425','EOSQ089')], na.rm = TRUE)
+
+gci <- select(gci, !starts_with('EOSQ'))
+
+```
+
+#Attention to capital - venture data
+
+```{r}
+#Rank 1 shows the most important benefit (highest attention)
+#After normalizing, I will substract 1 and take absolute value to make sure higher value in range 0 to 1 goes to higher attention.
+This is to ensure that country and ventures variables move on the same directions, in order to construct a congurance level.
+
+#Normalize Attention data (all data is based on a scale from 1 to 7)
+preproc_gali <- preProcess(gali %>%
+                            select(starts_with("accel_ben_rank_"))
+                          , method=c("range"))
+gali <- predict(preproc_gali, gali)
+
+#Calculating the average of different benifits to group them into one of the 3 categories of capital plus signaling.
+
+gali$attention_hc <- 1- round((rowMeans(gali[,
+                                  c('accel_ben_rank_business_skills',
+                                    'accel_ben_rank_mentorship')],
+                              na.rm=TRUE)),2)
+
+gali$attention_signaling <- 1- round((gali$accel_ben_rank_aware_cred),2)
+
+gali$attention_sc <- 1- round((rowMeans(gali[,
+                                  c('accel_ben_rank_network',
+                                'accel_ben_rank_access_entreprene')],
+                              na.rm=TRUE)),2)
+
+gali$attention_fc <- 1- round((rowMeans(gali[,
+                                c('accel_ben_rank_access_investors',
+                                  'accel_ben_rank_direct_funding')],
+                              na.rm=TRUE)),2)
+
+#I will then mutiply this by the country index to measure the congruence level
+```
+
+```{r Cleaning data of acceleration benefit ranking }
+
+#Removing ventures that ranked benefits outside of given scale (i.e. 1 to 7)
+
+gali <- filter(gali, accel_ben_rank_network <= 7 & accel_ben_rank_business_skills
+<= 7 & accel_ben_rank_mentorship <= 7 & accel_ben_rank_access_investors <= 7 & accel_ben_rank_direct_funding <= 7 & accel_ben_rank_access_entreprene <= 7 & accel_ben_rank_aware_cred <= 7 )
+
+#Removing ventures that gave the same ranking to two or more benefits 
+gali <- filter(gali, 
+               accel_ben_rank_network != accel_ben_rank_business_skills &
+                 accel_ben_rank_network != accel_ben_rank_mentorship & 
+                 accel_ben_rank_network != accel_ben_rank_access_investors &
+                 accel_ben_rank_network != accel_ben_rank_direct_funding &
+                 accel_ben_rank_network != accel_ben_rank_access_entreprene &
+                 accel_ben_rank_network != accel_ben_rank_aware_cred )
+
+gali <- filter(gali, 
+                 accel_ben_rank_business_skills != accel_ben_rank_mentorship & 
+              accel_ben_rank_business_skills != accel_ben_rank_access_investors &
+                 accel_ben_rank_business_skills != accel_ben_rank_direct_funding &
+              accel_ben_rank_business_skills != accel_ben_rank_access_entreprene &
+                 accel_ben_rank_business_skills != accel_ben_rank_aware_cred )
+
+gali <- filter(gali, 
+                accel_ben_rank_mentorship != accel_ben_rank_access_investors &
+                 accel_ben_rank_mentorship != accel_ben_rank_direct_funding &
+                 accel_ben_rank_mentorship != accel_ben_rank_access_entreprene &
+                 accel_ben_rank_mentorship != accel_ben_rank_aware_cred )
+
+gali <- filter(gali, 
+              accel_ben_rank_access_investors != accel_ben_rank_direct_funding &
+            accel_ben_rank_access_investors != accel_ben_rank_access_entreprene &
+                 accel_ben_rank_access_investors != accel_ben_rank_aware_cred )
+
+gali <- filter(gali, 
+              accel_ben_rank_direct_funding != accel_ben_rank_access_entreprene &
+                 accel_ben_rank_direct_funding != accel_ben_rank_aware_cred )
+
+gali <- filter(gali, 
+              accel_ben_rank_access_entreprene != accel_ben_rank_aware_cred )
+
+```
+
+#Join all 3 datasets 
+```{r}
+gali_joined <- left_join(gali, gem, by = "country")
+
+gali_joined <- left_join(gali_joined, gci, by = "country")
+
+#Checking if the two methods of measring institutional fc are correlated. We want them to be highly correlated 
+cor(gali_joined$inst_fc_gem, gali_joined$inst_fc_gci, use="complete.obs")
+
+```
+
+#Panel data structure. Revenues in year t-1 as revenue 
+```{r}
+revenue_data <- select(gali_joined, starts_with('country') | starts_with("attention") | starts_with("inst") | ends_with("fins_revenues_m1") | ends_with("External_ID"))
+
+revenue_data <- select(revenue_data, -fu4fins_revenues_m1)
+
+revenue_data <- revenue_data %>% 
+  gather(year, revenue, ends_with("fins_revenues_m1"))
+
+revenue_data$year[revenue_data$year == "fins_revenues_m1"] <- -1
+revenue_data$year[revenue_data$year == "fu1fins_revenues_m1"] <- 0
+revenue_data$year[revenue_data$year == "fu2fins_revenues_m1"] <- 1
+revenue_data$year[revenue_data$year == "fu3fins_revenues_m1"] <- 2
+
+revenue_data$year <- as.numeric(revenue_data$year)
+
+```
+
+#Initial FE regression without controls 
+```{r}
+gali_fe_mod <- plm(revenue ~ (attention_fc*inst_fc_gci) , 
+                   data = revenue_data, 
+                   index = c("country", "year"),
+                   model = "within")
 
@@
 
-```
-
-```{r Cleaning data of acceleration benefit ranking }
-
-#Removing ventures that ranked benefits outside of given scale (i.e. 1 to 7)
-
-gali <- filter(gali, accel_ben_rank_network <= 7 & accel_ben_rank_business_skills
-<= 7 & accel_ben_rank_mentorship <= 7 & accel_ben_rank_access_investors <= 7 & accel_ben_rank_direct_funding <= 7 & accel_ben_rank_access_entreprene <= 7 & accel_ben_rank_aware_cred <= 7 )
-
-#Removing ventures that gave the same ranking to two or more benefits 
-gali <- filter(gali, 
-               accel_ben_rank_network != accel_ben_rank_business_skills &
-                 accel_ben_rank_network != accel_ben_rank_mentorship & 
-                 accel_ben_rank_network != accel_ben_rank_access_investors &
-                 accel_ben_rank_network != accel_ben_rank_direct_funding &
-                 accel_ben_rank_network != accel_ben_rank_access_entreprene &
-                 accel_ben_rank_network != accel_ben_rank_aware_cred )
-
-gali <- filter(gali, 
-                 accel_ben_rank_business_skills != accel_ben_rank_mentorship & 
-              accel_ben_rank_business_skills != accel_ben_rank_access_investors &
-                 accel_ben_rank_business_skills != accel_ben_rank_direct_funding &
-              accel_ben_rank_business_skills != accel_ben_rank_access_entreprene &
-                 accel_ben_rank_business_skills != accel_ben_rank_aware_cred )
-
-gali <- filter(gali, 
-                accel_ben_rank_mentorship != accel_ben_rank_access_investors &
-                 accel_ben_rank_mentorship != accel_ben_rank_direct_funding &
-                 accel_ben_rank_mentorship != accel_ben_rank_access_entreprene &
-                 accel_ben_rank_mentorship != accel_ben_rank_aware_cred )
-
-gali <- filter(gali, 
-              accel_ben_rank_access_investors != accel_ben_rank_direct_funding &
-            accel_ben_rank_access_investors != accel_ben_rank_access_entreprene &
-                 accel_ben_rank_access_investors != accel_ben_rank_aware_cred )
-
-gali <- filter(gali, 
-              accel_ben_rank_direct_funding != accel_ben_rank_access_entreprene &
-                 accel_ben_rank_direct_funding != accel_ben_rank_aware_cred )
-
-gali <- filter(gali, 
-              accel_ben_rank_access_entreprene != accel_ben_rank_aware_cred )
-
-```
-
-#Rnak 1 shows the most important benefit (highest attention)
-
-```{r}
-
-#Calculating the average of different benifits to group them into one of the 3 categories of capital plus signaling. Then making the range of values between 0 and 1
-
-gali$attention_HC <- round((rowMeans(gali[,
-                                  c('accel_ben_rank_business_skills',
-                                    'accel_ben_rank_mentorship')],
-                              na.rm=TRUE) / 7),2)
-
-gali$attention_signaling <- round((gali$accel_ben_rank_aware_cred / 7),2)
-
-gali$attention_SC <- round((rowMeans(gali[,
-                                  c('accel_ben_rank_network',
-                                'accel_ben_rank_access_entreprene')],
-                              na.rm=TRUE) / 7),2)
-
-gali$attention_FC <- round((rowMeans(gali[,
-                                c('accel_ben_rank_access_investors',
-                                  'accel_ben_rank_direct_funding')],
-                              na.rm=TRUE) / 7),2)
-
-#the lowest the value the highest the attention 
-#I will then mutiply this by the country index to measure the congruence level
-
-range(gali$attention_signaling)
 ```
@@
 ```
-
-#Country indices to interact with venture attention and construct conguence level
-
-```{r Merge with GEM NES NATIONAL data}
-
-gem15 <- import("GEM 2015 NES NATIONAL.sav")
-gem14 <- import("GEM 2014 NES NATIONAL.sav")
-gem13 <- import("GEM 2013 NES NATIONAL.sav")
-
-#GEM Selecting only Human Capital Variables (HC = human capital)
-
-gem_HC15 <-gem15 %>%
-  select(NES15COUNTRY, NES15RNAME, NES15_C02_MEAN9, NES15_D01_MEAN9, NES15_D02_MEAN9, NES15_D03_MEAN9, NES15_D04_MEAN9, NES15_D05_MEAN9, NES15_D06_MEAN9, ZNES15D1SUM9, ZNES15D2SUM9,   EU, OECD, BRICS)
-
-gem_HC14 <-gem14 %>%
-  select(NES14COUNTRY, NES14RNAME, NES14_C02_MEAN, NES14_D01_MEAN, NES14_D02_MEAN, NES14_D03_MEAN, NES14_D04_MEAN, NES14_D05_MEAN, NES14_D06_MEAN, ZNES14D1SUM, ZNES14D2SUM,   EU, OECD, BRICS)
-
-gem_HC13 <-gem13 %>%
-  select(NES13COUNTRY, NES13RNAME, NES13_C02_MEAN, NES13_D01_MEAN, NES13_D02_MEAN, NES13_D03_MEAN, NES13_D04_MEAN, NES13_D05_MEAN, NES13_D06_MEAN, ZNES13D1SUM, ZNES13D2SUM,   EU, OECD, BRICS)
-
-gem <- bind_rows(gem_HC15, gem_HC14, gem_HC13)
-
-gem$NES15RNAME[gem$NES15RNAME == "UK"] <-"UNITED KINGDOM OF GREAT BRITAIN AND NORTHERN IRELAND"
-
-gem$NES15RNAME[gem$NES15RNAME == "NETEHERLANDS"] <- "NETHERLANDS"
-
-gem1 <- bind_rows(gem_HC14, gem_HC15, gem_HC13)
-
-gem1$NES14RNAME[gem1$NES14RNAME == "UK"] <-"UNITED KINGDOM OF GREAT BRITAIN AND NORTHERN IRELAND"
-gem1$NES14RNAME[gem1$NES14RNAME == "NETEHERLANDS"] <- "NETHERLANDS"
-
-gem2 <- bind_rows(gem_HC13, gem_HC15, gem_HC14)
-
-gem2$NES13RNAME[gem2$NES13RNAME == "UK"] <-"UNITED KINGDOM OF GREAT BRITAIN AND NORTHERN IRELAND"
-gem2$NES13RNAME[gem2$NES13RNAME == "NETEHERLANDS"] <- "NETHERLANDS"
-
-gali[,8] <- toupper(gali[,8])
-
-gem_HC <- rename(gem, "info_venture_country_hq" = "NES15RNAME")
-
-gem_HC1 <- rename(gem1, "info_venture_country_hq" = "NES14RNAME")
-
-gem_HC2 <- rename(gem2, "info_venture_country_hq" = "NES13RNAME")
-
-gali_NES <- left_join( gali, gem_HC,  by = "info_venture_country_hq")
-
-gali_NES1 <- left_join(gali, gem_HC1, by = "info_venture_country_hq")
-
-gali_NES1 <- filter(gali_NES1 , info_venture_country_hq == "UGANDA" | info_venture_country_hq == "EL SALVADOR")
-
-gali_NES2 <- left_join(gali, gem_HC2, by = "info_venture_country_hq")
-
-gali_NES2 <- filter(gali_NES2 , info_venture_country_hq == "ZAMBIA" | info_venture_country_hq == "GHANA" | info_venture_country_hq == "NIGERIA")
-
-galiNES <- bind_rows(gali_NES, gali_NES1, gali_NES2)
-
-countries_list <- galiNES %>% 
-  group_by(galiNES$info_venture_country_hq) %>%
-  summarize(Count=n()) %>%
-  mutate(Percent = round((Count/sum(Count)*100))) %>%
-  arrange(desc(Count))
-
-```
-
-```{r Merge with GEM APS data}
-#APS0 <- import("GEM 2016 APS Global.sav")
-APS <- APS0 %>% 
-  select(suskill, country, ctryalp) %>%
-  group_by(country) %>%
-  summarise(skill_mean = mean(suskill, na.rm=TRUE))
-
-APS <- rename(APS, "NES15COUNTRY" = "country")
-
-gali_NESAPS <- merge(gali_NES, APS, by = "NES15COUNTRY")
-
-countries_list <- filter(countries_list, Count > 25)
-
-gali_GEM <- gali_NESAPS %>%
-  filter(info_venture_country_hq  %in% countries_list$`gali_NES$info_venture_country_hq`)
-
-```
-
-```{r}
-# Create dummy variables
-gali_GEM$res_man <- ifelse(gali_GEM$most_important_benefit=="acc_managerial", 1, 0)
-gali_GEM$res_fin <- ifelse(gali_GEM$most_important_benefit=="acc_financial_max", 1, 0)
-gali_GEM$res_soc <- ifelse(gali_GEM$most_important_benefit=="acc_social_max", 1, 0)
-gali_GEM$res_sig <- ifelse(gali_GEM$most_important_benefit=="acc_signaling", 1, 0)
-
-#Renaming for plot purposes 
-gali_GEM$info_venture_country_hq[gali_GEM$info_venture_country_hq == "UNITED STATES OF AMERICA"] <-"USA"
-
-gali_GEM$info_venture_country_hq[gali_GEM$info_venture_country_hq == "UNITED KINGDOM OF GREAT BRITAIN AND NORTHERN IRELAND"] <-"UNITED KINGDOM"
-
-gali_GEM_noUS <- filter(gali_GEM, info_venture_country_hq != "USA")
-
-```
-
-###ANALYSIS BASED ON GALI_GEM data to evaluate normative and cognitive differences and the impact of human capital as an acceleration resource
-
-```{r}
-#Summary table
-
-#ls(gali_GEM)
-
-#IV res_man Attention to human capital by the founders 
-#DVs fins_revenues_m1 fu1-fins_revenues_m1 fins_revenues_sincefound
-
-gali_GEM$y1_revenue <- gali_GEM$`fu1-fins_revenues_m1` - gali_GEM$fins_revenues_m1
-gali_GEM$y1_ownmoeny <- gali_GEM$`fu1-inv_ownmoney_m1` - gali_GEM$inv_ownmoney_m1
-gali_GEM$y1_aspiration_cap <- gali_GEM$fu1_tot_plans_cap_12m - gali_GEM$tot_plans_cap_12m
-gali_GEM$y1_raised_cap <- gali_GEM$fu1_tot_cap_m1 - gali_GEM$tot_cap_m1
-
-fu1-inv_plans_outequity_12months
-fu1-inv_plans_outequity_3years
-fu1_tot_plans_cap_12m
-
-#Controls
-
-fu1-report_any_prior_accelerator
-
-#Revenue as a DV
-
-revenue_lm_b <- lm(`fu1-fins_revenues_m1` ~ res_man, data = gali_GEM_noUS)
-summary(revenue_lm_b)
-
-revenue_lm <- lm(`fu1-fins_revenues_m1` ~ res_man + `fu1-report_any_prior_accelerator` + finished + fins_ft_employees_m1 ,
-                 data = gali_GEM)
-summary(revenue_lm)
-
-revenue_lm_cog <- lm(`fu1-fins_revenues_m1` ~ res_man + res_man*skill_mean + `fu1-report_any_prior_accelerator` + fins_ft_employees_m1, data = gali_GEM)
-summary(revenue_lm_cog)
-
-revenue_lm_norm <- lm(`fu1-fins_revenues_m1` ~ res_man + res_man*ZNES15D2SUM9 +  res_man*skill_mean+ `fu1-report_any_prior_accelerator` + fins_ft_employees_m1+ finished, data = gali_GEM)
-summary(revenue_lm_norm)
-+ fins_ft_employees_m1 + finished
-
-#Capital aspirations as a DV
-
-lm_b <- lm(fins_revenues_m1  ~ receivedHC*res_man  , data = gali_GEM)
-
-summary(lm_b)
-
-lmOut(lm_b, file =  "results_asp22.csv")
-
-ggplot(gali_GEM, aes(skill_mean, ZNES15D2SUM9, label= info_venture_country_hq))+
-  geom_point(colour = "Light Blue")+
-  geom_text(check_overlap = TRUE, size = 2.5, nudge_y = 0.1)+
-  theme_minimal()+
-  xlab("Cognitive acceptance")+
-  ylab("Normative acceptance")
-
-gali_GEM %>% 
-  group_by(info_venture_country_hq) %>%
-  summarise(mean(NES15D2SUM_MEAN9))
-
-gali_GEM %>% 
-  group_by(info_venture_country_hq) %>%
-  summarise(mean(NES15_D01_MEAN9))
-
-```
-
-```{r fig.width=15}
-ggplot(gali_GEM, aes(info_venture_country_hq))+
-  geom_histogram(stat = "count")+
-  theme(axis.text.x = element_text(angle = -80))
-
-```
-
-```{r Merge with VIMBI data}
-vimbi <-  import("vimbi2017.xlsx") #211 obs
-vimbi <- rename(vimbi, "info_venture_country_hq" = "Country: World Bank name")
-vimbi <- clean_names(vimbi)
-
-gali_vimbi <- merge(gali_0,vimbi, by = "info_venture_country_hq")
-
-```
-
-```{r}
-# Create dummy variables
-gali_vimbi$res_man <- ifelse(gali_vimbi$most_important_benefit=="acc_managerial", 1, 0)
-gali_vimbi$res_fin <- ifelse(gali_vimbi$most_important_benefit=="acc_financial_max", 1, 0)
-gali_vimbi$res_soc <- ifelse(gali_vimbi$most_important_benefit=="acc_social_max", 1, 0)
-gali_vimbi$res_sig <- ifelse(gali_vimbi$most_important_benefit=="acc_signaling", 1, 0)
-
-gali_vimbi <- filter(gali_vimbi, tot_cap_sincefound < 10000000)
-
-#res_fe_mod <- lm(res_sig ~ x3_cp_capital_rank_percent_2016_h_good, 
-                    #data = gali_vimbi)
-
-vimbi$gni_capita_10_year_growth_2006_2015 <- as.numeric(vimbi$gni_capita_10_year_growth_2006_2015)
-
-ggplot(gali_vimbi, aes(x=fins_revenues_sincefound, y=x1_lb_labour_flexibility_education_support_2016_h_good, colour=factor(res_sig))) +
-  geom_point() +
-  scale_x_log10()
-
-hlm <- lmer(log1p(fins_revenues_sincefound)~1+(1|x1_lb_labour_flexibility_education_support_2016_h_good), gali_vimbi)
-
-summary(hlm)
-
-with(gali_vimbi, tapply(fins_revenues_sincefound, x1_lb_labour_flexibility_education_support_2016_h_good, mean))
-coef(hlm)
-
-dt_matrix <- cor(na.omit(vimbi[ ,3:8]))
-
-cortest.bartlett(na.omit(vimbi[ ,3:8]))
-
-det(dt_matrix)
-
-pc1 <- principal(na.omit(vimbi[ ,3:8]), nfactors=3, rotate="none")
-plot(pc1$values, type = "b")
-
-efaMR(x=na.omit(vimbi[ ,3:8]), factors=3, covmat=NULL, n.obs=151, 
-      dist='normal', fm='ols', rtype='orthogonal', rotation = 'CF-varimax', 
-      input.A=NULL, additionalRC = NULL, 
-      nstart = 100, compare = 'First', plot = T, cex = .5,
-      normalize = FALSE, geomin.delta = .01, 
-      MTarget = NULL, MWeight = NULL, PhiTarget = NULL, PhiWeight = NULL, 
-      useorder = FALSE, mnames = NULL, fnames = NULL, wxt2 = 1)
-
-bwplot(x1_lb_labour_flexibility_education_support_2016_h_good~resid(hlm), gali_vimbi)
-
-```
-
-```{r Clean data from for profit ventures that included philantropy in their capital structure }
-
-#gali_0 <- filter(gali_0,pctphilan_sincefound == 0 )
-
-```
-
-```{r fig.width=15}
-ggplot(gali_0, aes(info_venture_country_hq))+
-  geom_histogram(stat = "count")+
-  theme(axis.text.x = element_text(angle = -80))
-
-```

### 2021-02-04 GALI_2020.Rmd
index issues

@@
 ```{r}
+revenue_data <- transform(revenue_data, id=match(paste(revenue_data$country,revenue_data$New_External_ID,sep="_"), unique(paste(revenue_data$country,revenue_data$New_External_ID,sep="_")))) #create a column called id which assigns a unique id to the unique combinations of origin and destination countries
+
 gali_fe_mod <- plm(revenue ~ (attention_fc*inst_fc_gci) , 
                    data = revenue_data, 
-                   index = c("country", "year"),
+                   index = c("id", "year"),
                    model = "within")

### 2021-02-08 GALI_2020.Rmd
data wrangling - constructing all predictors

--- 2021-02-02 GALI_2020.Rmd
@@
 
-#Panel data structure. Revenues in year t-1 as revenue 
+#Fiancial Capital acquisiton total
 ```{r}
-revenue_data <- select(gali_joined, starts_with('country') | starts_with("attention") | starts_with("inst") | ends_with("fins_revenues_m1") | ends_with("External_ID"))
+gali_joined  <- gali_joined %>% mutate(capital_raised0 = gali_joined %>% select(starts_with("inv_") & ends_with("_m1")) %>% 
+                         rowSums(na.rm = TRUE))
 
-revenue_data <- select(revenue_data, -fu4fins_revenues_m1)
+gali_joined  <- gali_joined %>% mutate(capital_raised1 = gali_joined %>% select(starts_with("fu1inv_") & ends_with("_m1")) %>% 
+                         rowSums(na.rm = TRUE))
 
-revenue_data <- revenue_data %>% 
-  gather(year, revenue, ends_with("fins_revenues_m1"))
+gali_joined  <- gali_joined %>% mutate(capital_raised2 = gali_joined %>% select(starts_with("fu2inv_") & ends_with("_m1")) %>% 
+                         rowSums(na.rm = TRUE))
 
-revenue_data$year[revenue_data$year == "fins_revenues_m1"] <- -1
-revenue_data$year[revenue_data$year == "fu1fins_revenues_m1"] <- 0
-revenue_data$year[revenue_data$year == "fu2fins_revenues_m1"] <- 1
-revenue_data$year[revenue_data$year == "fu3fins_revenues_m1"] <- 2
+gali_joined  <- gali_joined %>% mutate(capital_raised3 = gali_joined %>% select(starts_with("fu3inv_") & ends_with("_m1")) %>% 
+                         rowSums(na.rm = TRUE))
 
-revenue_data$year <- as.numeric(revenue_data$year)
+gali_joined  <- gali_joined %>% mutate(capital_raised4 = gali_joined %>% select(starts_with("fu4inv_") & ends_with("_m1")) %>% 
+                         rowSums(na.rm = TRUE))
+
+gali_joined  <- gali_joined %>% mutate(capital_raised_tot = gali_joined %>% select(starts_with("capital_raised")) %>% 
+                         rowSums(na.rm = TRUE))
 
@@
 
-#Initial FE regression without controls 
+#Human capital acquisition 
 ```{r}
-gali_fe_mod <- plm(revenue ~ (attention_fc*inst_fc_gci) , 
-                   data = revenue_data, 
-                   index = c("country", "year"),
-                   model = "within")
+gali_joined  <- gali_joined %>% mutate(hr_tot = gali_joined %>%
+                         select(contains("_employees")) %>% 
+                         rowSums(na.rm = TRUE))
+```
+
+#Social capital acquisition 
+```{r}
+gali_joined <- gali_joined %>% mutate(equity_sources_tot = gali_joined %>%
+                         select(contains("equityfrom")) %>% 
+                         rowSums(na.rm = TRUE))
+```
+
+#Revenues
+```{r}
+gali_joined <- gali_joined %>% mutate(revenue_tot = gali_joined %>%
+                         select(contains("revenues")) %>% 
+                         rowSums(na.rm = TRUE))
+```
+
+#Exploring with plots
+```{r}
+ggplot(gali_joined, aes()) +
 

### 2021-02-08 GALI_2020.Rmd
exploring plots

@@
 library(caret)
-
-```
-
-##Function to extract summary model tables  
-```{r}
-lmOut <- function(res, file="test.csv", ndigit=3, writecsv=T) {
-  if (length(grep('summary', class(res)))==0) res <- summary(res)
-  co <- res$coefficients
-  nvar <- nrow(co)
-  ncoll <- ncol(co)
-  f <- res$fstatistic
-  formatter <- function(x) format(round(x,ndigit),nsmall=ndigit)
-  # This sets the number of rows before we start recording the coefficients
-  nstats <- 4
-  # G matrix stores data for output
-  G <- matrix("", nrow=nvar+nstats, ncol=ncoll+1)
-  G[1,1] <- toString(res$call)
-  # Save rownames and colnames
-  G[(nstats+1):(nvar+nstats),1] <- rownames(co)
-  G[nstats, 2:(ncoll+1)] <- colnames(co)
-  # Save Coefficients
-  G[(nstats+1):(nvar+nstats), 2:(ncoll+1)] <- formatter(co)
-  # Save F-stat
-  G[1,2] <- paste0("F(",f[2],",",f[3],")")
-  G[2,2] <- formatter(f[1])
-  # Save F-p value
-  G[1,3] <- "Prob > P"
-  G[2,3] <- formatter(1-pf(f[1],f[2],f[3]))
-  # Save R2
-  G[1,4] <- "R-Squared"
-  G[2,4] <- formatter(res$r.squared)
-  # Save Adj-R2
-  G[1,5] <- "Adj-R2"
-  G[2,5] <- formatter(res$adj.r.squared)
-  print(G)
-  if (writecsv) write.csv(G, file=file, row.names=F)
-}
 
@@
 
-```{r}
-#Rank 1 shows the most important benefit (highest attention)
-#After normalizing, I will substract 1 and take absolute value to make sure higher value in range 0 to 1 goes to higher attention.
-This is to ensure that country and ventures variables move on the same directions, in order to construct a congurance level.
-
-#Normalize Attention data (all data is based on a scale from 1 to 7)
-preproc_gali <- preProcess(gali %>%
-                            select(starts_with("accel_ben_rank_"))
-                          , method=c("range"))
-gali <- predict(preproc_gali, gali)
-
-#Calculating the average of different benifits to group them into one of the 3 categories of capital plus signaling.
-
-gali$attention_hc <- 1- round((rowMeans(gali[,
-                                  c('accel_ben_rank_business_skills',
-                                    'accel_ben_rank_mentorship')],
-                              na.rm=TRUE)),2)
-
-gali$attention_signaling <- 1- round((gali$accel_ben_rank_aware_cred),2)
-
-gali$attention_sc <- 1- round((rowMeans(gali[,
-                                  c('accel_ben_rank_network',
-                                'accel_ben_rank_access_entreprene')],
-                              na.rm=TRUE)),2)
-
-gali$attention_fc <- 1- round((rowMeans(gali[,
-                                c('accel_ben_rank_access_investors',
-                                  'accel_ben_rank_direct_funding')],
-                              na.rm=TRUE)),2)
-
-#I will then mutiply this by the country index to measure the congruence level
-```
-
 ```{r Cleaning data of acceleration benefit ranking }
@@
 
+```
+
+```{r}
+#Rank 1 shows the most important benefit (highest attention)
+#After normalizing, I will substract 1 and take absolute value to make sure higher value in range 0 to 1 goes to higher attention.
+This is to ensure that country and ventures variables move on the same directions, in order to construct a congurance level.
+
+#Normalize Attention data (all data is based on a scale from 1 to 7)
+preproc_gali <- preProcess(gali %>%
+                            select(starts_with("accel_ben_rank_"))
+                          , method=c("range"))
+gali <- predict(preproc_gali, gali)
+
+#Calculating the average of different benifits to group them into one of the 3 categories of capital plus signaling.
+
+gali$attention_hc <- 1- round((rowMeans(gali[,
+                                  c('accel_ben_rank_business_skills',
+                                    'accel_ben_rank_mentorship')],
+                              na.rm=TRUE)),2)
+
+gali$attention_signaling <- 1- round((gali$accel_ben_rank_aware_cred),2)
+
+gali$attention_sc <- 1- round((rowMeans(gali[,
+                                  c('accel_ben_rank_network',
+                                'accel_ben_rank_access_entreprene')],
+                              na.rm=TRUE)),2)
+
+gali$attention_fc <- 1- round((rowMeans(gali[,
+                                c('accel_ben_rank_access_investors',
+                                  'accel_ben_rank_direct_funding')],
+                              na.rm=TRUE)),2)
+
+#I will then mutiply this by the country index to measure the congruence level
 ```
@@
 ```{r}
-ggplot(gali_joined, aes()) +
+ggplot(gali_joined, aes(inst_hc_gem,inst_fc_gem)) +
+  geom_point()
 

### 2021-02-16 GALI_2020.Rmd
mixed model analysis

@@
 preproc_nes <- preProcess(gem_nes[,(4:5)], method=c("range"))
+
 gem_nes <- predict(preproc_nes, gem_nes)
@@
 ```{r}
-gem_aps <- import("Data/GEM-APS.csv")
+#gem_aps <- import("Data/GEM-APS.csv")
 #Clean and tidy gem APS
-gem_aps <- clean_names(gem_aps)
-gem_aps <- gem_aps %>%
-  row_to_names(row_number = 2)
-gem_aps[,-2] <- gem_aps[,-2] %>% mutate_if(is.character,as.numeric)
-gem_aps <- clean_names(gem_aps)
-gem_aps <- gem_aps %>%
-  rename(country = economy) %>%
-  rename(inst_signaling_aps = high_status_to_successful_entrepreneurs)%>%
-  rename(inst_hc_aps = established_business_ownership) %>%
-  rename(inst_sc_aps = total_early_stage_entrepreneurial_activity_tea)
+#gem_aps <- clean_names(gem_aps)
+#gem_aps <- gem_aps %>%
+  #row_to_names(row_number = 2)
+#gem_aps[,-2] <- gem_aps[,-2] %>% mutate_if(is.character,as.numeric)
+#gem_aps <- clean_names(gem_aps)
+#gem_aps <- gem_aps %>%
+  #rename(country = economy) %>%
+  #rename(inst_signaling_aps = high_status_to_successful_entrepreneurs) #%>%
+  #rename(inst_hc_aps = established_business_ownership) %>%
+  #rename(inst_sc_aps = total_early_stage_entrepreneurial_activity_tea)
 
 #All APS data is a percentage. We devide by 100 to gat [0,1] range
-gem_aps$inst_signaling_gem <- gem_aps$inst_signaling_aps /100
-gem_aps$inst_hc_aps <- gem_aps$inst_hc_aps /100
-gem_aps$inst_sc_gem <- gem_aps$inst_sc_aps /100
+#gem_aps$inst_signaling_gem <- gem_aps$inst_signaling_aps /100 
+#gem_aps$inst_hc_aps <- gem_aps$inst_hc_aps /100 + 1
+#gem_aps$inst_sc_gem <- gem_aps$inst_sc_aps /100 + 1
 
@@
 ```{r}
+gem <- gem_nes
 #join nes and aps on country and year 
-gem <- left_join(gem_nes, gem_aps, by=c("country", "year", "code"))
-gem$inst_hc_gem <- rowMeans(gem[,c("inst_hc_nes", "inst_hc_aps")])
+#gem <- left_join(gem_nes, gem_aps, by=c("country", "year", "code"))
+#gem$inst_hc_gem <- rowMeans(gem[,c("inst_hc_nes", "inst_hc_aps")]) + 1
+#gem$inst_hc_gem <- gem$inst_hc_nes
 
-gem <- gem %>%
-  select(code, country, year, ends_with('_gem'))
+#gem <- gem %>%
+  #select(code, country, year, ends_with('_gem'))
 
@@
   group_by(country) %>%
-  mutate(inst_fc_gem = mean(inst_fc_gem, na.rm= TRUE),
-  inst_hc_gem = mean(inst_hc_gem, na.rm= TRUE),
-  inst_sc_gem = mean(inst_sc_gem, na.rm= TRUE),
-  inst_signaling_gem = mean(inst_signaling_gem, na.rm= TRUE))
+  mutate(inst_fc_gem = mean(inst_fc_gem, na.rm= TRUE))
+#  inst_hc_gem = mean(inst_hc_gem, na.rm= TRUE),
+  #inst_sc_gem = mean(inst_sc_gem, na.rm= TRUE),
+#  inst_signaling_gem = mean(inst_signaling_gem, na.rm= TRUE))
 
-gem <- select(gem, -year)
+#gem <- select(gem, -year, -inst_hc_nes)
 
@@
 gci <- filter(gci, `Series Global ID` == "EOSQ089" |
-                   `Series Global ID` == "EOSQ425" )
+                   `Series Global ID` == "EOSQ425" |
+                   `Series Global ID` == "EOSQ109")
 gci <- filter(gci, Edition ==2018 )
@@
               values_from = score)
-preproc_gci <- preProcess(gci %>%
-                            select(starts_with("EOSQ"))
-                          , method=c("range"))
-gci <- predict(preproc_gci, gci)
 
-gci$inst_fc_gci <- rowMeans(gci[,c('EOSQ425','EOSQ089')], na.rm = TRUE)
+#preproc_gci <- preProcess(gci %>%
+#                           select(starts_with("EOSQ"))
+#                          , method=c("range"))
+#gci <- predict(preproc_gci, gci)
 
-gci <- select(gci, !starts_with('EOSQ'))
+#gci$inst_fc_gci <- rowMeans(gci[,c('EOSQ425','EOSQ089')], na.rm = TRUE)
+
+#gci$inst_sc_gci <- gci$EOSQ109
+
+#gci <- select(gci, !starts_with('EOSQ'))
 
@@
 #Rank 1 shows the most important benefit (highest attention)
-#After normalizing, I will substract 1 and take absolute value to make sure higher value in range 0 to 1 goes to higher attention.
-This is to ensure that country and ventures variables move on the same directions, in order to construct a congurance level.
 
@@
 
-gali$attention_hc <- 1- round((rowMeans(gali[,
-                                  c('accel_ben_rank_business_skills',
-                                    'accel_ben_rank_mentorship')],
-                              na.rm=TRUE)),2)
+gali$attention_hc <- 1- round(gali$accel_ben_rank_business_skills,2)
 
@@
                                   c('accel_ben_rank_network',
-                                'accel_ben_rank_access_entreprene')],
+                                'accel_ben_rank_access_entreprene',
+                                'accel_ben_rank_access_investors')],
                               na.rm=TRUE)),2)
 
-gali$attention_fc <- 1- round((rowMeans(gali[,
-                                c('accel_ben_rank_access_investors',
-                                  'accel_ben_rank_direct_funding')],
-                              na.rm=TRUE)),2)
+gali$attention_fc <- 1- round(gali$accel_ben_rank_direct_funding,2)
 
-#I will then mutiply this by the country index to measure the congruence level
 ```
@@
 ```{r}
-gali_joined <- left_join(gali, gem, by = "country")
+gali_joined <- left_join(gali, gem, by = c("country", "year"))
 
 gali_joined <- left_join(gali_joined, gci, by = "country")
-
-#Checking if the two methods of measring institutional fc are correlated. We want them to be highly correlated 
-cor(gali_joined$inst_fc_gem, gali_joined$inst_fc_gci, use="complete.obs")
 
@@
 
+#Mixed model analysis 
+```{r}
+fit0 <- lmer(capital_raised_tot ~  attention_fc + (attention_fc|country), data = gali_joined, REML = F)
+
+fit1 <- lmer(capital_raised_tot ~ attention_fc + attention_fc*EOSQ425 + (1 |country), data = gali_joined, REML = F)
+
+fit2 <- lmer(capital_raised_tot ~ attention_fc + attention_fc*EOSQ089 + (1 |country), data = gali_joined, REML = F)
+
+fit3 <- lmer(capital_raised_tot ~ attention_fc + attention_fc*inst_fc_gem + (1 |country), data = gali_joined, REML = F)
+
+summary(fit2)
+
+```
+
 #Exploring with plots
@@
 
-gali$founder1_grad = ifelse(gali$found_name1_education == "Masters Degree" | 
-                              gali$found_name1_education =="PhD" |
-                              gali$found_name1_education == "Some graduate degree", 1, 0) 
-gali$founder1_grad[is.na(gali$founder1_grad)] <- 0
+gali_joined$founder1_grad = ifelse(gali_joined$found_name1_education == "Masters Degree" | 
+                              gali_joined$found_name1_education =="PhD" |
+                              gali_joined$found_name1_education == "Some graduate degree", 1, 0) 
+gali_joined$founder1_grad[is.na(gali_joined$founder1_grad)] <- 0
 
-gali$founder2_grad = ifelse(gali$found_name2_education == "Masters Degree" | 
-                              gali$found_name2_education =="PhD" |
-                              gali$found_name2_education == "Some graduate degree", 1, 0) 
-gali$founder2_grad[is.na(gali$founder2_grad)] <- 0
+gali_joined$founder2_grad = ifelse(gali_joined$found_name2_education == "Masters Degree" | 
+                              gali_joined$found_name2_education =="PhD" |
+                              gali_joined$found_name2_education == "Some graduate degree", 1, 0) 
+gali_joined$founder2_grad[is.na(gali_joined$founder2_grad)] <- 0
 
-gali$founder3_grad = ifelse(gali$found_name3_education == "Masters Degree" |
-                              gali$found_name3_education =="PhD" |
-                              gali$found_name3_education == "Some graduate degree", 1, 0)
-gali$founder3_grad[is.na(gali$founder3_grad)] <- 0
+gali_joined$founder3_grad = ifelse(gali_joined$found_name3_education == "Masters Degree" |
+                              gali_joined$found_name3_education =="PhD" |
+                              gali_joined$found_name3_education == "Some graduate degree", 1, 0)
+gali_joined$founder3_grad[is.na(gali_joined$founder3_grad)] <- 0
 
-gali$nb_of_founders <- gali$found_name1_present + gali$found_name2_present + gali$found_name3_present
+gali_joined$nb_of_founders <- gali_joined$found_name1_present + gali_joined$found_name2_present + gali_joined$found_name3_present
 
-gali <- filter(gali, nb_of_founders > 0)
+gali_joined <- filter(gali_joined, nb_of_founders > 0)
 
-gali$grad_pct = ((gali$founder1_grad + gali$founder2_grad + gali$founder3_grad) / gali$nb_of_founders)
+gali_joined$grad_pct = ((gali_joined$founder1_grad + gali_joined$founder2_grad + gali_joined$founder3_grad) / gali_joined$nb_of_founders)
 
@@
 
-gali$founder1_job1_clevel = ifelse(is.na(gali$found_name1_job1_role) | gali$found_name1_job1_role !=  "CEO/Executive Director" , 0, 1)
-gali$founder1_job2_clevel = ifelse(is.na(gali$found_name1_job2_role) | gali$found_name1_job2_role !=  "CEO/Executive Director" , 0, 1)
-gali$founder2_job1_clevel = ifelse(is.na(gali$found_name2_job1_role) | gali$found_name2_job1_role !=  "CEO/Executive Director" , 0, 1)
-gali$founder2_job2_clevel = ifelse(is.na(gali$found_name2_job2_role) | gali$found_name2_job2_role !=  "CEO/Executive Director" , 0, 1)
-gali$founder3_job1_clevel = ifelse(is.na(gali$found_name3_job1_role) | gali$found_name3_job1_role !=  "CEO/Executive Director" , 0, 1)
-gali$founder3_job2_clevel = ifelse(is.na(gali$found_name3_job2_role) | gali$found_name3_job2_role !=  "CEO/Executive Director" , 0, 1)
+gali_joined$founder1_job1_clevel = ifelse(is.na(gali_joined$found_name1_job1_role) | gali_joined$found_name1_job1_role !=  "CEO/Executive Director" , 0, 1)
+gali_joined$founder1_job2_clevel = ifelse(is.na(gali_joined$found_name1_job2_role) | gali_joined$found_name1_job2_role !=  "CEO/Executive Director" , 0, 1)
+gali_joined$founder2_job1_clevel = ifelse(is.na(gali_joined$found_name2_job1_role) | gali_joined$found_name2_job1_role !=  "CEO/Executive Director" , 0, 1)
+gali_joined$founder2_job2_clevel = ifelse(is.na(gali_joined$found_name2_job2_role) | gali_joined$found_name2_job2_role !=  "CEO/Executive Director" , 0, 1)
+gali_joined$founder3_job1_clevel = ifelse(is.na(gali_joined$found_name3_job1_role) | gali_joined$found_name3_job1_role !=  "CEO/Executive Director" , 0, 1)
+gali_joined$founder3_job2_clevel = ifelse(is.na(gali_joined$found_name3_job2_role) | gali_joined$found_name3_job2_role !=  "CEO/Executive Director" , 0, 1)
 
-gali$prior_clevel_pct = ((gali$founder1_job1_clevel + gali$founder1_job2_clevel + gali$founder2_job1_clevel + 
-  gali$founder2_job2_clevel + gali$founder3_job1_clevel + gali$founder3_job2_clevel) / (gali$nb_of_founders*2))
+gali_joined$prior_clevel_pct = ((gali_joined$founder1_job1_clevel + gali_joined$founder1_job2_clevel + gali_joined$founder2_job1_clevel + 
+  gali_joined$founder2_job2_clevel + gali_joined$founder3_job1_clevel + gali_joined$founder3_job2_clevel) / (gali_joined$nb_of_founders*2))
 
@@
 
-gali$avg_teamtenure <- rowMeans(subset(gali, select = c('found_name1_job1_tenure', 'found_name1_job2_tenure', 'found_name2_job1_tenure', 'found_name2_job2_tenure', 'found_name3_job1_tenure', 'found_name3_job2_tenure')), na.rm = TRUE)
+gali_joined$avg_teamtenure <- rowMeans(subset(gali_joined, select = c('found_name1_job1_tenure', 'found_name1_job2_tenure', 'found_name2_job1_tenure', 'found_name2_job2_tenure', 'found_name3_job1_tenure', 'found_name3_job2_tenure')), na.rm = TRUE)
 
-gali$avg_teamtenure[is.nan(gali$avg_teamtenure)] <- 0
+gali_joined$avg_teamtenure[is.nan(gali_joined$avg_teamtenure)] <- 0
 
 #Team Prior Founding
-gali$team_prior_founding <- gali$found_name1_prior_fp + gali$found_name2_prior_fp + gali$found_name3_prior_fp + gali$found_name1_prior_other + gali$found_name2_prior_other + gali$found_name3_prior_other + gali$found_name1_prior_np + gali$found_name2_prior_np + gali$found_name3_prior_np
+gali_joined$team_prior_founding <- gali_joined$found_name1_prior_fp + gali_joined$found_name2_prior_fp + gali_joined$found_name3_prior_fp + gali_joined$found_name1_prior_other + gali_joined$found_name2_prior_other + gali_joined$found_name3_prior_other + gali_joined$found_name1_prior_np + gali_joined$found_name2_prior_np + gali_joined$found_name3_prior_np
 
@@
 
-gali$z_team_prior_founding <- scale(gali$team_prior_founding, center = TRUE, scale = TRUE)
-gali$z_prior_clevel_pct <- scale(gali$prior_clevel_pct, center = TRUE, scale = TRUE)
-gali$z_avg_teamtenure <- scale(gali$avg_teamtenure, center = TRUE, scale = TRUE)
-gali$z_grad_pct <- scale(gali$grad_pct, center = TRUE, scale = TRUE)
+gali_joined$z_team_prior_founding <- scale(gali_joined$team_prior_founding, center = TRUE, scale = TRUE)
+gali_joined$z_prior_clevel_pct <- scale(gali_joined$prior_clevel_pct, center = TRUE, scale = TRUE)
+gali_joined$z_avg_teamtenure <- scale(gali_joined$avg_teamtenure, center = TRUE, scale = TRUE)
+gali_joined$z_grad_pct <- scale(gali_joined$grad_pct, center = TRUE, scale = TRUE)
 
@@
 
-gali$normq_team_prior_founding <- normalize.quantiles(gali$z_team_prior_founding,copy=TRUE)
-gali$normq_prior_clevel_pct <- normalize.quantiles(gali$z_prior_clevel_pct,copy=TRUE)
-gali$normq_avg_teamtenure <- normalize.quantiles(gali$z_avg_teamtenure,copy=TRUE)
-gali$normq_grad_pct <- normalize.quantiles(gali$z_grad_pct,copy=TRUE)
+gali_joined$normq_team_prior_founding <- normalize.quantiles(gali_joined$z_team_prior_founding,copy=TRUE)
+gali_joined$normq_prior_clevel_pct <- normalize.quantiles(gali_joined$z_prior_clevel_pct,copy=TRUE)
+gali_joined$normq_avg_teamtenure <- normalize.quantiles(gali_joined$z_avg_teamtenure,copy=TRUE)
+gali_joined$normq_grad_pct <- normalize.quantiles(gali_joined$z_grad_pct,copy=TRUE)
 
@@
 
-gali$HC_index <- (gali$normq_team_prior_founding + gali$normq_prior_clevel_pct + gali$normq_avg_teamtenure + gali$normq_grad_pct)
+gali_joined$HC_index <- (gali_joined$normq_team_prior_founding + gali_joined$normq_prior_clevel_pct + gali_joined$normq_avg_teamtenure + gali_joined$normq_grad_pct)
 

### 2021-02-25 GALI_2020.Rmd
This is a long due commit after running analysis and moving things to papaja

@@
 knitr::opts_chunk$set(echo = TRUE)
+#install.packages("devtools")
+#devtools::install_github("crsh/papaja")
 ```
@@
 
-#X countries have fewer than 70 firms in the sample.
+#X countries have fewer than 50 firms in the sample.
 Because so few observations may not offer good representation, I excluded firms headquartered in these countries from the analysis, keeping X firms in Y countries and Z industries.
@@
 
-countries_to_keep <- filter(countries_to_keep, Count >6)
+countries_to_keep <- filter(countries_to_keep, Count >9)
 countries_to_keep$`gali$info_venture_country_hq`
@@
 
-#Keep only ventures with 3 years of post acceleration information 
-gali <- filter(gali, fu1report_followup_yes == 1 & fu2report_followup_yes == 1 & fu3report_followup_yes == 1)
+#Keep only for porfit firms 
+gali <- filter(gali, info_legal_status == "For-profit company" )
 
@@
 
-countries_to_keep <- filter(countries_to_keep, Count >6)
+countries_to_keep <- filter(countries_to_keep, Count >9)
 countries_to_keep$`gali$country`
@@
 #Normalize NES data (all data is based on a scale from 1 to 5)
-preproc_nes <- preProcess(gem_nes[,(4:5)], method=c("range"))
+mean_norm_minmax <- function(x){
+                                (x- mean(x)) /(max(x)-min(x))
+                               }
 
-gem_nes <- predict(preproc_nes, gem_nes)
+mean_norm_nes <- as.data.frame(lapply(gem_nes[,(4:5)], mean_norm_minmax))
+
+gem_nes <- cbind(gem_nes[, (1:3)], mean_norm_nes)
 
@@
                    `Series Global ID` == "EOSQ425" |
-                   `Series Global ID` == "EOSQ109")
+                   `Series Global ID` == "EOSQ109" |
+                   `Series Global ID` == "DOMCREDITGDP" |
+                   `Series Global ID` == "EOSQ403")
 gci <- filter(gci, Edition ==2018 )
@@
               values_from = score)
+```
 
-#preproc_gci <- preProcess(gci %>%
-#                           select(starts_with("EOSQ"))
-#                          , method=c("range"))
-#gci <- predict(preproc_gci, gci)
+#Plotting all countries along the 3 dimensions
 
-#gci$inst_fc_gci <- rowMeans(gci[,c('EOSQ425','EOSQ089')], na.rm = TRUE)
+```{r fig.height=10, fig.width=10}
 
-#gci$inst_sc_gci <- gci$EOSQ109
+library(plot3D)
 
-#gci <- select(gci, !starts_with('EOSQ'))
+with(gci, text3D(EOSQ403, EOSQ425, EOSQ109, 
+  labels = gci$country,  
+  col = gg.col(100), theta = 60, phi = 20,
+  xlab = "Human capital", ylab = "Financail capital", zlab = "Social capital", 
+  main = "Institutional level resources", cex = 0.6, 
+  bty = "g", ticktype = "detailed", d = 2,
+  clab = c("Urban","Pop"), adj = 1, font = 1.5))
+
+#Zoom into to the middle for more clarity 
+plotdev(xlim = c(3, 4), ylim = c(3, 5.5), 
+         zlim = c(3, 3.8))
 
@@
 
+#Reverse code attention variable 
 ```{r}
-#Rank 1 shows the most important benefit (highest attention)
+#Reverse code fundtion 
+reverse <- function(x){x*-1- +8}
 
-#Normalize Attention data (all data is based on a scale from 1 to 7)
-preproc_gali <- preProcess(gali %>%
-                            select(starts_with("accel_ben_rank_"))
-                          , method=c("range"))
-gali <- predict(preproc_gali, gali)
+gali_att <- as.data.frame(lapply(gali %>%
+                            select(starts_with("accel_ben_rank_")), reverse))
+
+gali <- cbind(gali %>%
+        select(-starts_with("accel_ben_rank_")), gali_att)
+
+```
+
+```{r}
+mean_norm_att <- as.data.frame(lapply(gali %>%
+                            select(starts_with("accel_ben_rank_")), mean_norm_minmax))
+
+gali <- cbind(gali %>%
+        select(-starts_with("accel_ben_rank_")), mean_norm_att)
+```
+
+```{r}
 
@@
 
-gali$attention_hc <- 1- round(gali$accel_ben_rank_business_skills,2)
+gali$attention_hc <- round(gali$accel_ben_rank_business_skills,2)
 
-gali$attention_signaling <- 1- round((gali$accel_ben_rank_aware_cred),2)
+gali$attention_sc <- round(rowMeans(gali[,
+                                  c('accel_ben_rank_network',
+                                'accel_ben_rank_access_entreprene')],
+                              na.rm=TRUE),2)
 
-gali$attention_sc <- 1- round((rowMeans(gali[,
-                                  c('accel_ben_rank_network',
-                                'accel_ben_rank_access_entreprene',
+gali$attention_fc <-  round(rowMeans(gali[,
+                                  c('accel_ben_rank_direct_funding',
                                 'accel_ben_rank_access_investors')],
-                              na.rm=TRUE)),2)
-
-gali$attention_fc <- 1- round(gali$accel_ben_rank_direct_funding,2)
+                              na.rm=TRUE),2)
 
@@
 ```{r}
-gali_joined <- left_join(gali, gem, by = c("country", "year"))
 
-gali_joined <- left_join(gali_joined, gci, by = "country")
+gali_joined <- left_join(gali, gci, by = "country")
 
@@
 
+#Revenues
+```{r}
+gali_joined <- gali_joined %>% mutate(revenue_tot = gali_joined %>%
+                         select(contains("revenues")) %>% 
+                         rowSums(na.rm = TRUE))
+```
+
 #Human capital acquisition 
@@
 
-#Revenues
+#Mixed model analysis - Human capital
 ```{r}
-gali_joined <- gali_joined %>% mutate(revenue_tot = gali_joined %>%
-                         select(contains("revenues")) %>% 
-                         rowSums(na.rm = TRUE))
-```
+fit0hc <- lmer(participated ~  accel_ben_rank_business_skills + (accel_ben_rank_business_skills|country), data = gali_joined, REML = F)
 
-#Mixed model analysis 
-```{r}
-fit0 <- lmer(capital_raised_tot ~  attention_fc + (attention_fc|country), data = gali_joined, REML = F)
+fit1hc <- lmer(participated ~  accel_ben_rank_business_skills*EOSQ403 + (accel_ben_rank_business_skills|country), data = gali_joined, REML = F)
 
-fit1 <- lmer(capital_raised_tot ~ attention_fc + attention_fc*EOSQ425 + (1 |country), data = gali_joined, REML = F)
+summary(fit0hc)
+summary(fit1hc)
 
-fit2 <- lmer(capital_raised_tot ~ attention_fc + attention_fc*EOSQ089 + (1 |country), data = gali_joined, REML = F)
+fit00hc <- lmer(hr_tot ~  accel_ben_rank_business_skills + (accel_ben_rank_business_skills|country), data = gali_joined, REML = F)
 
-fit3 <- lmer(capital_raised_tot ~ attention_fc + attention_fc*inst_fc_gem + (1 |country), data = gali_joined, REML = F)
+fit11hc <- lmer(hr_tot ~  accel_ben_rank_business_skills*EOSQ403 + (accel_ben_rank_business_skills|country), data = gali_joined, REML = F)
 
-summary(fit2)
+summary(fit00hc)
+summary(fit11hc)
 
@@
 
-#Exploring with plots
+#Mixed model analysis - Financial capital
 ```{r}
-ggplot(gali_joined, aes(inst_hc_gem,inst_fc_gem)) +
-  geom_point()
+fit0fc <- lmer(participated ~   + (accel_ben_rank_direct_funding|country), data = gali_joined, REML = F)
+
+fit1fc <- lmer(participated ~ accel_ben_rank_direct_funding*EOSQ425 + (accel_ben_rank_direct_funding |country ), data = gali_joined, REML = F)
+
+fit2fc <- lmer(participated ~ accel_ben_rank_direct_funding*EOSQ089 + (accel_ben_rank_direct_funding |country ), data = gali_joined, REML = F)
+
+fit3fc <- lmer(participated ~ accel_ben_rank_direct_funding*DOMCREDITGDP + (accel_ben_rank_direct_funding |country), data = gali_joined, REML = F)
+
+summary(fit0fc)
+summary(fit1fc)
+summary(fit2fc)
+summary(fit3fc)
+
+fit00fc <- lmer(capital_raised_tot ~   + (accel_ben_rank_direct_funding|country), data = gali_joined, REML = F)
+
+fit11fc <- lmer(capital_raised_tot ~ accel_ben_rank_direct_funding*EOSQ425 + (accel_ben_rank_direct_funding |country ), data = gali_joined, REML = F)
+
+fit22fc <- lmer(capital_raised_tot ~ accel_ben_rank_direct_funding*EOSQ089 + (accel_ben_rank_direct_funding |country ), data = gali_joined, REML = F)
+
+fit33fc <- lmer(capital_raised_tot ~ accel_ben_rank_direct_funding*DOMCREDITGDP + (accel_ben_rank_direct_funding |country), data = gali_joined, REML = F)
+
+summary(fit00fc)
+summary(fit11fc)
+summary(fit22fc)
+summary(fit33fc)
+
+```
+
+#Mixed model analysis - Social capital
+
+```{r}
+fit0sc <- lmer(participated ~ accel_ben_rank_network + (accel_ben_rank_network |country), data = gali_joined, REML = F)
+
+fit1sc <- lmer(participated ~ accel_ben_rank_network*EOSQ109 + (accel_ben_rank_network | country), data = gali_joined, REML = F)
+
+summary(fit0sc)
+summary(fit1sc)
+
+fit00sc <- lmer(equity_sources_tot ~ accel_ben_rank_network + (accel_ben_rank_network |country), data = gali_joined, REML = F)
+
+fit11sc <- lmer(equity_sources_tot ~ accel_ben_rank_network*EOSQ109 + (accel_ben_rank_network | country), data = gali_joined, REML = F)
+
+summary(fit00sc)
+summary(fit11sc)
 

### 2021-02-25 Manuscript.Rmd
This is a long due commit after running analysis and moving things to papaja

--- 2021-02-25 GALI_2020.Rmd
@@
 ---
-title: "Data Responsive-report"
-author: "Ouafaa Hmaddi"
-date: "January 18, 2021"
-output: html_document 
+title             : "The title"
+shorttitle        : "Title"
+
+author: 
+  - name          : "Ouafaa Hmaddi"
+    affiliation   : "1"
+    corresponding : yes    # Define only one corresponding author
+    address       : "Postal address"
+    email         : "ohmaddi@uoregon.edu"
+    role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
+      - Conceptualization
+      - Writing - Original Draft Preparation
+      - Writing - Review & Editing
+
+affiliation:
+  - id            : "1"
+    institution   : "University of Oregon"
+
+authornote: |
+  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.
+
+  Enter author note here.
+
+abstract: |
+  One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.
+
+  Two to three sentences of **more detailed background**, comprehensible  to scientists in related disciplines.
+
+  One sentence clearly stating the **general problem** being addressed by  this particular study.
+
+  One sentence summarizing the main result (with the words "**here we show**" or their equivalent).
+
+  Two or three sentences explaining what the **main result** reveals in direct comparison to what was thought to be the case previously, or how the  main result adds to previous knowledge.
+
+  One or two sentences to put the results into a more **general context**.
+
+  Two or three sentences to provide a **broader perspective**, readily comprehensible to a scientist in any discipline.
+
+  <!-- https://tinyurl.com/ybremelq -->
+
+keywords          : "keywords"
+wordcount         : "X"
+
+bibliography      : ["r-references.bib"]
+
+floatsintext      : no
+figurelist        : no
+tablelist         : no
+footnotelist      : no
+linenumbers       : yes
+mask              : no
+draft             : no
+
+documentclass     : "apa6"
+classoption       : "man"
+output            : papaja::apa6_pdf
 ---
 
-```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE)
-#install.packages("devtools")
-#devtools::install_github("crsh/papaja")
+```{r setup, include = FALSE}
+library("papaja")
+r_refs("r-references.bib")
 ```
 
-```{r}
+```{r analysis-preferences}
+# Seed for random number generation
+set.seed(42)
+knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
+```
 
-#load libraries
-#if (!requireNamespace("BiocManager", quietly = TRUE))
-#install.packages("caret")
+# Methods
+We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study.
+<!-- 21-word solution (Simmons, Nelson & Simonsohn, 2012; retrieved from http://ssrn.com/abstract=2160588) -->
 
-#BiocManager::install("preprocessCore")
+## Participants
 
+## Material
+
+## Procedure
+
+## Data analysis
+We used `r cite_r("r-references.bib")` for all our analyses.
+```{r message=FALSE, warning=FALSE, include=FALSE}
 library(rio)
 library(tidyverse)
-library(lubridate)
 library(janitor)
 library(ggplot2)
-library(readxl)
-library(reshape2)
-library(readr)
 library(psych)
-library(foreign)
-library(plm)
-library(lme4)
-library(lattice)
-library(lmerTest)
-library(EFAutilities)
-library(haven)
-library(sjPlot)
-library(XLConnect)
-library(preprocessCore)
 library(knitr)
-library(caret)
 
@@
 
-```{r Countries to analyse in main sample}
+```{r Countries to analyse in main sample, message=FALSE, warning=FALSE, include=FALSE}
 gali <- import("Data/GALI_External_DataRelease_2020.xlsx")
@@
 
-#X countries have fewer than 50 firms in the sample.
-Because so few observations may not offer good representation, I excluded firms headquartered in these countries from the analysis, keeping X firms in Y countries and Z industries.
-
 countries_to_keep <- filter(countries_to_keep, `gali$info_venture_country_hq` != 'NA')
@@
 
-#Number of ventures in main sample 
-#kable(countries_to_keep)
-
 ```
 
-```{r}
+```{r message=FALSE, warning=FALSE, include=FALSE}
 gali <- filter(gali, found_name1_age > 14 | is.na(found_name1_age))
@@
 
-```{r Countries to keep in sample with valid data}
+```{r Countries to keep in sample with valid data, message=FALSE, warning=FALSE, include=FALSE}
 
@@
 
-#Number of ventures in main sample 
-#kable(countries_to_keep)
-```
-
-#GEM NES Data
-
-```{r}
-gem_nes <- import("Data/GEM-NES.csv")
-
-#Clean and tidy gem NES
-gem_nes <- clean_names(gem_nes)
-gem_nes <- gem_nes %>%
-  row_to_names(row_number = 2)
-
-gem_nes[,-2] <- gem_nes[,-2] %>% mutate_if(is.character,as.numeric)
-
-gem_nes$inst_hc_nes <- rowMeans(gem_nes[,(5:6)])
-gem_nes <- clean_names(gem_nes)
-gem_nes <- gem_nes %>%
-  rename(country = economy) %>%
-  rename(inst_fc_gem = 	financing_for_entrepreneurs)
-
-gem_nes <- gem_nes [, -(5:6)]
-
-#Normalize NES data (all data is based on a scale from 1 to 5)
-mean_norm_minmax <- function(x){
-                                (x- mean(x)) /(max(x)-min(x))
-                               }
-
-mean_norm_nes <- as.data.frame(lapply(gem_nes[,(4:5)], mean_norm_minmax))
-
-gem_nes <- cbind(gem_nes[, (1:3)], mean_norm_nes)
-
-```
-
-#GEM APS data
-
-```{r}
-#gem_aps <- import("Data/GEM-APS.csv")
-#Clean and tidy gem APS
-#gem_aps <- clean_names(gem_aps)
-#gem_aps <- gem_aps %>%
-  #row_to_names(row_number = 2)
-#gem_aps[,-2] <- gem_aps[,-2] %>% mutate_if(is.character,as.numeric)
-#gem_aps <- clean_names(gem_aps)
-#gem_aps <- gem_aps %>%
-  #rename(country = economy) %>%
-  #rename(inst_signaling_aps = high_status_to_successful_entrepreneurs) #%>%
-  #rename(inst_hc_aps = established_business_ownership) %>%
-  #rename(inst_sc_aps = total_early_stage_entrepreneurial_activity_tea)
-
-#All APS data is a percentage. We devide by 100 to gat [0,1] range
-#gem_aps$inst_signaling_gem <- gem_aps$inst_signaling_aps /100 
-#gem_aps$inst_hc_aps <- gem_aps$inst_hc_aps /100 + 1
-#gem_aps$inst_sc_gem <- gem_aps$inst_sc_aps /100 + 1
-
-```
-
-#Final GEM data
-
-```{r}
-gem <- gem_nes
-#join nes and aps on country and year 
-#gem <- left_join(gem_nes, gem_aps, by=c("country", "year", "code"))
-#gem$inst_hc_gem <- rowMeans(gem[,c("inst_hc_nes", "inst_hc_aps")]) + 1
-#gem$inst_hc_gem <- gem$inst_hc_nes
-
-#gem <- gem %>%
-  #select(code, country, year, ends_with('_gem'))
-
-gem$country[gem$country == "United States"] <-"USA"
-
-gem <- gem %>%
-  group_by(country) %>%
-  mutate(inst_fc_gem = mean(inst_fc_gem, na.rm= TRUE))
-#  inst_hc_gem = mean(inst_hc_gem, na.rm= TRUE),
-  #inst_sc_gem = mean(inst_sc_gem, na.rm= TRUE),
-#  inst_signaling_gem = mean(inst_signaling_gem, na.rm= TRUE))
-
-#gem <- select(gem, -year, -inst_hc_nes)
-
-gem <- gem %>% distinct()
-
 ```
@@
 #CGI data
-```{r}
+```{r message=FALSE, warning=FALSE, include=FALSE}
 gci <- import("Data/GCI_2018.xlsx")
@@
 
-```{r fig.height=10, fig.width=10}
+```{r echo=FALSE, fig.height=10, fig.width=10, message=FALSE, warning=FALSE}
 
@@
 
-```{r Cleaning data of acceleration benefit ranking }
+```{r Cleaning data of acceleration benefit ranking, message=FALSE, warning=FALSE, include=FALSE}
 
@@
 #Reverse code attention variable 
-```{r}
+```{r message=FALSE, warning=FALSE, include=FALSE}
 #Reverse code fundtion 
@@
 
-```{r}
+```{r message=FALSE, warning=FALSE, include=FALSE}
+
+mean_norm_minmax <- function(x){
+                                (x- mean(x)) /(max(x)-min(x))
+                               }
+
 mean_norm_att <- as.data.frame(lapply(gali %>%
@@
 
-```{r}
-
-#Calculating the average of different benifits to group them into one of the 3 categories of capital plus signaling.
-
-gali$attention_hc <- round(gali$accel_ben_rank_business_skills,2)
-
-gali$attention_sc <- round(rowMeans(gali[,
-                                  c('accel_ben_rank_network',
-                                'accel_ben_rank_access_entreprene')],
-                              na.rm=TRUE),2)
-
-gali$attention_fc <-  round(rowMeans(gali[,
-                                  c('accel_ben_rank_direct_funding',
-                                'accel_ben_rank_access_investors')],
-                              na.rm=TRUE),2)
-
-```
-
 #Join all 3 datasets 
-```{r}
+```{r message=FALSE, warning=FALSE, include=FALSE}
 
@@
 #Fiancial Capital acquisiton total
-```{r}
+```{r message=FALSE, warning=FALSE, include=FALSE}
 gali_joined  <- gali_joined %>% mutate(capital_raised0 = gali_joined %>% select(starts_with("inv_") & ends_with("_m1")) %>% 
@@
 #Revenues
-```{r}
+```{r message=FALSE, warning=FALSE, include=FALSE}
 gali_joined <- gali_joined %>% mutate(revenue_tot = gali_joined %>%
@@
 #Human capital acquisition 
-```{r}
+```{r message=FALSE, warning=FALSE, include=FALSE}
 gali_joined  <- gali_joined %>% mutate(hr_tot = gali_joined %>%
@@
 #Social capital acquisition 
-```{r}
+```{r message=FALSE, warning=FALSE, include=FALSE}
 gali_joined <- gali_joined %>% mutate(equity_sources_tot = gali_joined %>%
@@
 
+# Results
+
+```{r message=FALSE, warning=FALSE, include=FALSE}
+#Function to extract coefficients of summary table
+
+summary_table <- function(x){ x$coefficients %>%
+  as.data.frame %>%
+    rename(
+      "$b$" = "Estimate"
+    , "SE" = "Std. Error"
+    , "$t$" = "t value"
+  ) %>%
+  mutate(
+    Effect = papaja:::prettify_terms(rownames(.))
+  ) %>%
+  printnum(
+    digits = c(2, 2, 2, 3)
+    , gt1 = c(TRUE, TRUE, TRUE, TRUE, FALSE, FALSE)
+    , zero = c(TRUE, TRUE, TRUE, TRUE, FALSE, FALSE)
+  ) %>%
+  select(Effect, `$b$`, `SE`, `$t$`)}
+
+#for glmer
+
+summary_table_z <- function(x){ x$coefficients %>%
+  as.data.frame %>%
+    rename(
+      "$b$" = "Estimate"
+    , "SE" = "Std. Error"
+    , "$z$" = "z value"
+  ) %>%
+  mutate(
+    Effect = papaja:::prettify_terms(rownames(.))
+  ) %>%
+  printnum(
+    digits = c(2, 2, 2, 3)
+    , gt1 = c(TRUE, TRUE, TRUE, TRUE, FALSE, FALSE)
+    , zero = c(TRUE, TRUE, TRUE, TRUE, FALSE, FALSE)
+  ) %>%
+  select(Effect, `$b$`, `SE`, `$z$`)}
+
+```
+
 #Mixed model analysis - Human capital
-```{r}
-fit0hc <- lmer(participated ~  accel_ben_rank_business_skills + (accel_ben_rank_business_skills|country), data = gali_joined, REML = F)
+```{r echo=FALSE, message=FALSE, warning=FALSE}
+library(lme4)
+fit0hc <- glmer(participated ~  accel_ben_rank_business_skills + (accel_ben_rank_business_skills|country), data = gali_joined, family=binomial)
 
-fit1hc <- lmer(participated ~  accel_ben_rank_business_skills*EOSQ403 + (accel_ben_rank_business_skills|country), data = gali_joined, REML = F)
-
-summary(fit0hc)
-summary(fit1hc)
+fit1hc <- glmer(participated ~  accel_ben_rank_business_skills*EOSQ403 + (accel_ben_rank_business_skills|country), data = gali_joined, family=binomial)
 
@@
 fit11hc <- lmer(hr_tot ~  accel_ben_rank_business_skills*EOSQ403 + (accel_ben_rank_business_skills|country), data = gali_joined, REML = F)
+hc0 <- summary_table_z(summary(fit0hc))
+hc1 <- summary_table_z(summary(fit1hc))
+hc00 <- summary_table(summary(fit00hc))
+hc11 <- summary_table(summary(fit11hc))
 
-summary(fit00hc)
-summary(fit11hc)
+rownames(hc0) <- c("Intercept","Attention to Human capital(AHC)")
+rownames(hc1) <- c("Intercept","AHC", "Ease of finding skilled employees", "AHCxEase of finding skilled employees")
+rownames(hc00) <- c("Intercept","Attention to Human capital")
+rownames(hc11) <- c("Intercept","AHC", "Ease of finding skilled employees", "AHCxEase of finding skilled employees")
+
+kable(hc0[,-1]) 
+kable(hc1[,-1])
+kable(hc00[,-1])
+kable(hc11[,-1])
 
@@
 #Mixed model analysis - Financial capital
-```{r}
-fit0fc <- lmer(participated ~   + (accel_ben_rank_direct_funding|country), data = gali_joined, REML = F)
+```{r echo=FALSE, message=FALSE, warning=FALSE}
+library(lme4)
+fit0fc <- glmer(participated ~  accel_ben_rank_direct_funding + (accel_ben_rank_direct_funding|country), data = gali_joined, family=binomial)
 
-fit1fc <- lmer(participated ~ accel_ben_rank_direct_funding*EOSQ425 + (accel_ben_rank_direct_funding |country ), data = gali_joined, REML = F)
+fit1fc <- glmer(participated ~ accel_ben_rank_direct_funding*EOSQ425 + (accel_ben_rank_direct_funding |country ), data = gali_joined, family=binomial)
 
-fit2fc <- lmer(participated ~ accel_ben_rank_direct_funding*EOSQ089 + (accel_ben_rank_direct_funding |country ), data = gali_joined, REML = F)
+fit2fc <- glmer(participated ~ accel_ben_rank_direct_funding*EOSQ089 + (accel_ben_rank_direct_funding |country ), data = gali_joined, family=binomial)
 
-fit3fc <- lmer(participated ~ accel_ben_rank_direct_funding*DOMCREDITGDP + (accel_ben_rank_direct_funding |country), data = gali_joined, REML = F)
+fit3fc <- glmer(participated ~ accel_ben_rank_direct_funding*DOMCREDITGDP + (accel_ben_rank_direct_funding |country), data = gali_joined, family=binomial)
 
@@
 
-```{r}
+```{r echo=FALSE, message=FALSE, warning=FALSE}
 fit0sc <- lmer(participated ~ accel_ben_rank_network + (accel_ben_rank_network |country), data = gali_joined, REML = F)
@@
 
-summary(fit0sc)
-summary(fit1sc)
+coef(summary(fit0sc))
+coef(summary(fit1sc))
 
@@
 
-summary(fit00sc)
-summary(fit11sc)
+coef(summary(fit00sc))
+coef(summary(fit11sc))
 
@@
 
-##Constrcuting human capital index (control variable)
-###Graduate percentage, Prior C-level Executive Percentage, Average Team Tenure , Team Prior Founding
+# Discussion
 
-```{r Human capital index}
-#Graduate percentage
+\newpage
 
-gali_joined$founder1_grad = ifelse(gali_joined$found_name1_education == "Masters Degree" | 
-                              gali_joined$found_name1_education =="PhD" |
-                              gali_joined$found_name1_education == "Some graduate degree", 1, 0) 
-gali_joined$founder1_grad[is.na(gali_joined$founder1_grad)] <- 0
+# References
 
-gali_joined$founder2_grad = ifelse(gali_joined$found_name2_education == "Masters Degree" | 
-                              gali_joined$found_name2_education =="PhD" |
-                              gali_joined$found_name2_education == "Some graduate degree", 1, 0) 
-gali_joined$founder2_grad[is.na(gali_joined$founder2_grad)] <- 0
+\begingroup
+\setlength{\parindent}{-0.5in}
+\setlength{\leftskip}{0.5in}
 
-gali_joined$founder3_grad = ifelse(gali_joined$found_name3_education == "Masters Degree" |
-                              gali_joined$found_name3_education =="PhD" |
-                              gali_joined$found_name3_education == "Some graduate degree", 1, 0)
-gali_joined$founder3_grad[is.na(gali_joined$founder3_grad)] <- 0
-
-gali_joined$nb_of_founders <- gali_joined$found_name1_present + gali_joined$found_name2_present + gali_joined$found_name3_present
-
-gali_joined <- filter(gali_joined, nb_of_founders > 0)
-
-gali_joined$grad_pct = ((gali_joined$founder1_grad + gali_joined$founder2_grad + gali_joined$founder3_grad) / gali_joined$nb_of_founders)
-
-#Prior C-level Executive Percentage
-
-gali_joined$founder1_job1_clevel = ifelse(is.na(gali_joined$found_name1_job1_role) | gali_joined$found_name1_job1_role !=  "CEO/Executive Director" , 0, 1)
-gali_joined$founder1_job2_clevel = ifelse(is.na(gali_joined$found_name1_job2_role) | gali_joined$found_name1_job2_role !=  "CEO/Executive Director" , 0, 1)
-gali_joined$founder2_job1_clevel = ifelse(is.na(gali_joined$found_name2_job1_role) | gali_joined$found_name2_job1_role !=  "CEO/Executive Director" , 0, 1)
-gali_joined$founder2_job2_clevel = ifelse(is.na(gali_joined$found_name2_job2_role) | gali_joined$found_name2_job2_role !=  "CEO/Executive Director" , 0, 1)
-gali_joined$founder3_job1_clevel = ifelse(is.na(gali_joined$found_name3_job1_role) | gali_joined$found_name3_job1_role !=  "CEO/Executive Director" , 0, 1)
-gali_joined$founder3_job2_clevel = ifelse(is.na(gali_joined$found_name3_job2_role) | gali_joined$found_name3_job2_role !=  "CEO/Executive Director" , 0, 1)
-
-gali_joined$prior_clevel_pct = ((gali_joined$founder1_job1_clevel + gali_joined$founder1_job2_clevel + gali_joined$founder2_job1_clevel + 
-  gali_joined$founder2_job2_clevel + gali_joined$founder3_job1_clevel + gali_joined$founder3_job2_clevel) / (gali_joined$nb_of_founders*2))
-
-#Average Team Tenure
-
-gali_joined$avg_teamtenure <- rowMeans(subset(gali_joined, select = c('found_name1_job1_tenure', 'found_name1_job2_tenure', 'found_name2_job1_tenure', 'found_name2_job2_tenure', 'found_name3_job1_tenure', 'found_name3_job2_tenure')), na.rm = TRUE)
-
-gali_joined$avg_teamtenure[is.nan(gali_joined$avg_teamtenure)] <- 0
-
-#Team Prior Founding
-gali_joined$team_prior_founding <- gali_joined$found_name1_prior_fp + gali_joined$found_name2_prior_fp + gali_joined$found_name3_prior_fp + gali_joined$found_name1_prior_other + gali_joined$found_name2_prior_other + gali_joined$found_name3_prior_other + gali_joined$found_name1_prior_np + gali_joined$found_name2_prior_np + gali_joined$found_name3_prior_np
-
-#Final Human Capital Index
-
-gali_joined$z_team_prior_founding <- scale(gali_joined$team_prior_founding, center = TRUE, scale = TRUE)
-gali_joined$z_prior_clevel_pct <- scale(gali_joined$prior_clevel_pct, center = TRUE, scale = TRUE)
-gali_joined$z_avg_teamtenure <- scale(gali_joined$avg_teamtenure, center = TRUE, scale = TRUE)
-gali_joined$z_grad_pct <- scale(gali_joined$grad_pct, center = TRUE, scale = TRUE)
-
-#Cite Bolstad et al, Bioinformatics (2003)
-
-gali_joined$normq_team_prior_founding <- normalize.quantiles(gali_joined$z_team_prior_founding,copy=TRUE)
-gali_joined$normq_prior_clevel_pct <- normalize.quantiles(gali_joined$z_prior_clevel_pct,copy=TRUE)
-gali_joined$normq_avg_teamtenure <- normalize.quantiles(gali_joined$z_avg_teamtenure,copy=TRUE)
-gali_joined$normq_grad_pct <- normalize.quantiles(gali_joined$z_grad_pct,copy=TRUE)
-
-#group all into an index
-
-gali_joined$HC_index <- (gali_joined$normq_team_prior_founding + gali_joined$normq_prior_clevel_pct + gali_joined$normq_avg_teamtenure + gali_joined$normq_grad_pct)
-
-```
-
-##Constrcuting social capital index (control variable)
-
-```{r}
-
-```
-
-##Constrcuting financial capital index (control variable)
-
-```{r}
-
-```
-
-##Gender decomposition variable
-
-```{r Gender decomposition variable}
-gali <- gali %>% drop_na(found_name1_gender)
-
-gali$found_name2_gender[is.na(gali$found_name2_gender)] <- 0
-gali$found_name3_gender[is.na(gali$found_name3_gender)] <- 0
-
-gali$founder1_f <- ifelse(gali$found_name1_gender == "F", 1,0)
-gali$founder2_f <- ifelse(gali$found_name2_gender == "F", 1,0)
-gali$founder3_f <- ifelse(gali$found_name3_gender == "F", 1,0)
-
-gali$female_pct <- round(((gali$founder1_f + gali$founder2_f + gali$founder3_f) / gali$nb_of_founders ), 2)
-
-```
-
-```{r Capital structure study variables}
-
-##Total invesmtment
-gali_0$tot_cap_m1 <- rowSums(gali_0[ , c('inv_ownmoney_m1', 'inv_outequity_m1', 'inv_totaldebt_m1', 'inv_philan_m1')],na.rm = TRUE)
-
-gali_0$tot_cap_sincefound <- rowSums(gali_0[ , c('inv_ownmoney_sincefound', 'inv_outequity_sincefound', 'inv_totaldebt_sincefound', 'inv_philan_sincefound')],na.rm = TRUE)
-
-gali_0$fu1_tot_cap_m1 <- rowSums(gali_0[ , c('fu1-inv_ownmoney_m1', 'fu1-inv_outequity_m1', 'fu1-inv_totaldebt_m1', 'fu1-inv_philan_m1')],na.rm = TRUE)
-
-##Percentage of each capital type 
-###Equity
-gali_0$pctequity_m1 <- gali_0$inv_outequity_m1 / gali_0$tot_cap_m1
-gali_0$pctequity_sincefound <- gali_0$inv_outequity_sincefound / gali_0$tot_cap_sincefound
-gali_0$fu1_pctequity_m1 <- gali_0$`fu1-inv_outequity_m` / gali_0$fu1_tot_cap_m1
-
-###Debt
-gali_0$pctdebt_m1 <- gali_0$inv_totaldebt_m1 / gali_0$tot_cap_m1
-gali_0$pctdebt_sincefound <- gali_0$inv_totaldebt_sincefound / gali_0$tot_cap_sincefound
-gali_0$fu1_pctdebt_m1 <- gali_0$`fu1-inv_totaldebt_m` / gali_0$fu1_tot_cap_m1
-
-###Own Money
-gali_0$pctownmoney_m1 <- gali_0$inv_ownmoney_m1 / gali_0$tot_cap_m1
-gali_0$pctownmoney_sincefound <- gali_0$inv_ownmoney_sincefound / gali_0$tot_cap_sincefound
-gali_0$fu1_pctownmoney_m1 <- gali_0$`fu1-inv_ownmoney_m` / gali_0$fu1_tot_cap_m1
-
-###Phillantropy
-gali_0$pctphilan_m1 <- gali_0$inv_philan_m1 / gali_0$tot_cap_m1
-gali_0$pctphilan_sincefound <- gali_0$inv_philan_sincefound / gali_0$tot_cap_sincefound
-gali_0$fu1_pctphilan_m1 <- gali_0$`fu1-inv_philan_m` / gali_0$fu1_tot_cap_m1
-
-##Single source vs dominant source (> 90%)
-###Single source
-gali_0$single_source_m1 <- ifelse(gali_0$pctequity_m1 == 1 | 
-                                  gali_0$pctdebt_m1 == 1|
-                                  gali_0$pctownmoney_m1 == 1 |
-                                  gali_0$pctphilan_m1 ==1 , 1, 0)
-
-gali_0$single_source_sincefound <- ifelse(gali_0$pctequity_sincefound == 1 | 
-                                  gali_0$pctdebt_sincefound == 1|
-                                  gali_0$pctownmoney_sincefound == 1 |
-                                  gali_0$pctphilan_sincefound ==1 , 1, 0)
-
-gali_0$single_fu1_source_m1 <- ifelse(gali_0$fu1_pctequity_m1 == 1 | 
-                                  gali_0$fu1_pctdebt_m1 == 1|
-                                  gali_0$fu1_pctownmoney_m1 == 1 |
-                                  gali_0$fu1_pctphilan_m1 ==1 , 1, 0)
-
-###Dominant source
-gali_0$dominant_source_m1 <- ifelse((gali_0$pctequity_m1 >= .9 | 
-                                  gali_0$pctdebt_m1 >= .9 |
-                                  gali_0$pctownmoney_m1 >= .9 |
-                                  gali_0$pctphilan_m1 >= .9) &
-                                    gali_0$single_source_m1 == 0, 1, 0)
-
-gali_0$dominant_source_sincefound <- ifelse((gali_0$pctequity_sincefound >= .9 | 
-                                  gali_0$pctdebt_sincefound >= .9 |
-                                  gali_0$pctownmoney_sincefound >= .9 |
-                                  gali_0$pctphilan_sincefound >= .9) &
-                                  gali_0$single_source_m1 == 0, 1, 0)
-
-gali_0$dominant_fu1_source_m1 <- ifelse((gali_0$fu1_pctequity_m1 >= .9 | 
-                                  gali_0$fu1_pctdebt_m1 >= .9 |
-                                  gali_0$fu1_pctownmoney_m1 >= .9 |
-                                  gali_0$fu1_pctphilan_m1 >= .9) &
-                                  gali_0$single_source_m1 == 0, 1, 0)
-```
-
-```{r Apirations for capital structure in 12 months and 3 years }
-##Total aspired  invesmtment Pre-acceleration 
-gali_0$tot_plans_cap_12m <- rowSums(gali_0[ , c('inv_plans_outequity_12months', 'inv_plans_debt_12months', 'inv_plans_philan_12months')],na.rm = TRUE)
-
-gali_0$tot_plans_cap_3y <- rowSums(gali_0[ , c('inv_plans_outequity_3years', 'inv_plans_debt_3years', 'inv_plans_philan_3years')], na.rm = TRUE)
-
-##Total aspired  invesmtment Post-acceleration 
-gali_0$fu1_tot_plans_cap_12m <- rowSums(gali_0[ , c('fu1-inv_plans_outequity_12months', 'fu1-inv_plans_debt_12months', 'fu1-inv_plans_philan_12months')], na.rm = TRUE)
-
-gali_0$fu1_tot_plans_cap_3y <- rowSums(gali_0[ , c('fu1-inv_plans_outequity_3years', 'fu1-inv_plans_debt_3years', 'fu1-inv_plans_philan_3years')], na.rm = TRUE)
-
-##Aspired percentage of each capital type pre-acceleration 
-###Equity
-gali_0$pctequity_plan12m <- gali_0$inv_plans_outequity_12months / gali_0$tot_plans_cap_12m
-gali_0$pctequity_plan3y <- gali_0$inv_plans_outequity_3years / gali_0$tot_plans_cap_3y
-
-###Debt
-gali_0$pctdebt_m1 <- gali_0$inv_plans_debt_12months / gali_0$tot_plans_cap_12m
-gali_0$pctdebt_sincefound <- gali_0$inv_plans_debt_3years / gali_0$tot_plans_cap_3y
-
-###Phillantropy
-gali_0$pctphilan_m1 <- gali_0$inv_plans_philan_12months / gali_0$tot_plans_cap_12m
-gali_0$pctphilan_sincefound <- gali_0$inv_plans_philan_3years / gali_0$tot_plans_cap_3y
-
-##Aspired percentage of each capital type post-acceleration 
-###Equity
-gali_0$fu1_pctequity_plan12m <- gali_0$`fu1-inv_plans_outequity_12months` / gali_0$fu1_tot_plans_cap_12m
-gali_0$fu1_pctequity_plan3y <- gali_0$`fu1-inv_plans_outequity_3years` / gali_0$fu1_tot_plans_cap_3y
-
-###Debt
-gali_0$fu1_pctdebt_plan12m <- gali_0$`fu1-inv_plans_debt_12months` / gali_0$fu1_tot_plans_cap_12m
-gali_0$fu1_pctdebt_plan3y <- gali_0$`fu1-inv_plans_debt_3years` / gali_0$fu1_tot_plans_cap_3y
-
-###Phillantropy
-gali_0$fu1_pctphilan_plan12m <- gali_0$`fu1-inv_plans_philan_12months` / gali_0$fu1_tot_plans_cap_12m
-gali_0$fu1_pctphilan_plan3y <- gali_0$`fu1-inv_plans_philan_3years` / gali_0$fu1_tot_plans_cap_3y
-
-```
+<div id="refs" custom-style="Bibliography"></div>
+\endgroup

### 2021-02-25 Manuscript.tex
This is a long due commit after running analysis and moving things to papaja

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  english,
  man]{apa6}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={The title},
  pdfauthor={Ouafaa Hmaddi1},
  pdfkeywords={keywords},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

% Table formatting
\usepackage{longtable}
\usepackage{lscape}
% \usepackage[counterclockwise]{rotating}   % Landscape page setup for large tables
\usepackage{multirow}		% Table styling
\usepackage{tabularx}		% Control Column width
\usepackage[flushleft]{threeparttable}	% Allows for three part tables with a specified notes section
\usepackage{threeparttablex}            % Lets threeparttable work with longtable

% Create new environments so endfloat can handle them
% \newenvironment{ltable}
%   {\begin{landscape}\begin{center}\begin{threeparttable}}
%   {\end{threeparttable}\end{center}\end{landscape}}
\newenvironment{lltable}{\begin{landscape}\begin{center}\begin{ThreePartTable}}{\end{ThreePartTable}\end{center}\end{landscape}}

% Enables adjusting longtable caption width to table width
% Solution found at http://golatex.de/longtable-mit-caption-so-breit-wie-die-tabelle-t15767.html
\makeatletter
\newcommand\LastLTentrywidth{1em}
\newlength\longtablewidth
\setlength{\longtablewidth}{1in}
\newcommand{\getlongtablewidth}{\begingroup \ifcsname LT@\roman{LT@tables}\endcsname \global\longtablewidth=0pt \renewcommand{\LT@entry}[2]{\global\advance\longtablewidth by ##2\relax\gdef\LastLTentrywidth{##2}}\@nameuse{LT@\roman{LT@tables}} \fi \endgroup}

% \setlength{\parindent}{0.5in}
% \setlength{\parskip}{0pt plus 0pt minus 0pt}

% \usepackage{etoolbox}
\makeatletter
\patchcmd{\HyOrg@maketitle}
  {\section{\normalfont\normalsize\abstractname}}
  {\section*{\normalfont\normalsize\abstractname}}
  {}{\typeout{Failed to patch abstract.}}
\patchcmd{\HyOrg@maketitle}
  {\section{\protect\normalfont{\@title}}}
  {\section*{\protect\normalfont{\@title}}}
  {}{\typeout{Failed to patch title.}}
\makeatother
\shorttitle{Title}
\keywords{keywords\newline\indent Word count: X}
\DeclareDelayedFloatFlavor{ThreePartTable}{table}
\DeclareDelayedFloatFlavor{lltable}{table}
\DeclareDelayedFloatFlavor*{longtable}{table}
\makeatletter
\renewcommand{\efloat@iwrite}[1]{\immediate\expandafter\protected@write\csname efloat@post#1\endcsname{}}
\makeatother
\usepackage{lineno}

\linenumbers
\usepackage{csquotes}
\ifxetex
  % Load polyglossia as late as possible: uses bidi with RTL langages (e.g. Hebrew, Arabic)
  \usepackage{polyglossia}
  \setmainlanguage[]{english}
\else
  \usepackage[shorthands=off,main=english]{babel}
\fi

\title{The title}
\author{Ouafaa Hmaddi\textsuperscript{1}}
\date{}

\authornote{

Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.

Enter author note here.

The authors made the following contributions. Ouafaa Hmaddi: Conceptualization, Writing - Original Draft Preparation, Writing - Review \& Editing.

Correspondence concerning this article should be addressed to Ouafaa Hmaddi, Postal address. E-mail: \href{mailto:ohmaddi@uoregon.edu}{\nolinkurl{ohmaddi@uoregon.edu}}

}

\affiliation{\vspace{0.5cm}\textsuperscript{1} University of Oregon}

\abstract{
One or two sentences providing a \textbf{basic introduction} to the field, comprehensible to a scientist in any discipline.

Two to three sentences of \textbf{more detailed background}, comprehensible to scientists in related disciplines.

One sentence clearly stating the \textbf{general problem} being addressed by this particular study.

One sentence summarizing the main result (with the words ``\textbf{here we show}'' or their equivalent).

Two or three sentences explaining what the \textbf{main result} reveals in direct comparison to what was thought to be the case previously, or how the main result adds to previous knowledge.

One or two sentences to put the results into a more \textbf{general context}.

Two or three sentences to provide a \textbf{broader perspective}, readily comprehensible to a scientist in any discipline.
}

\begin{document}
\maketitle

\hypertarget{methods}{%
\section{Methods}\label{methods}}

We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study.

\hypertarget{participants}{%
\subsection{Participants}\label{participants}}

\hypertarget{material}{%
\subsection{Material}\label{material}}

\hypertarget{procedure}{%
\subsection{Procedure}\label{procedure}}

\hypertarget{data-analysis}{%
\subsection{Data analysis}\label{data-analysis}}

We used R (Version 4.0.2; R Core Team, 2020) and the R-packages \emph{lme4} (Version 1.1.23; Bates, Mächler, Bolker, \& Walker, 2015), \emph{Matrix} (Version 1.2.18; Bates \& Maechler, 2019), and \emph{papaja} (Version 0.1.0.9997; Aust \& Barth, 2020) for all our analyses.

\#CGI data

\#Plotting all countries along the 3 dimensions

\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-4-1.pdf} \includegraphics{Manuscript_files/figure-latex/unnamed-chunk-4-2.pdf}

\#Attention to capital - venture data

\#Reverse code attention variable

\#Join all 3 datasets

\#Fiancial Capital acquisiton total

\#Revenues

\#Human capital acquisition

\#Social capital acquisition

\hypertarget{results}{%
\section{Results}\label{results}}

\#Mixed model analysis - Human capital

\begin{tabular}{l|l|l|l}
\hline
  & \$b\$ & SE & \$z\$\\
\hline
Intercept & -1.47 & 0.08 & -19.16\\
\hline
Attention to Human capital(AHC) & 0.10 & 0.08 & 1.24\\
\hline
\end{tabular}

\begin{tabular}{l|l|l|l}
\hline
  & \$b\$ & SE & \$z\$\\
\hline
Intercept & -0.94 & 0.53 & -1.77\\
\hline
AHC & 0.86 & 0.44 & 1.97\\
\hline
Ease of finding skilled employees & -0.12 & 0.12 & -0.96\\
\hline
AHCxEase of finding skilled employees & -0.16 & 0.09 & -1.69\\
\hline
\end{tabular}

\begin{tabular}{l|l|l|l}
\hline
  & \$b\$ & SE & \$t\$\\
\hline
Intercept & 738.20 & 485.65 & 1.52\\
\hline
Attention to Human capital & 2,841.44 & 2,153.75 & 1.32\\
\hline
\end{tabular}

\begin{tabular}{l|l|l|l}
\hline
  & \$b\$ & SE & \$t\$\\
\hline
Intercept & -1,882.79 & 3,470.12 & -0.54\\
\hline
AHC & -9,744.87 & 16,027.75 & -0.61\\
\hline
Ease of finding skilled employees & 618.05 & 783.89 & 0.79\\
\hline
AHCxEase of finding skilled employees & 2,989.85 & 3,687.09 & 0.81\\
\hline
\end{tabular}

\#Mixed model analysis - Financial capital

\begin{verbatim}
## Linear mixed model fit by maximum likelihood  ['lmerMod']
## Formula: participated ~ +(accel_ben_rank_direct_funding | country)
##    Data: gali_joined
## 
##      AIC      BIC   logLik deviance df.resid 
##  14831.2  14869.8  -7410.6  14821.2    16439 
## 
## Scaled residuals: 
##     Min      1Q  Median      3Q     Max 
## -1.3463 -0.5096 -0.4046 -0.2890  2.4564 
## 
## Random effects:
##  Groups   Name                          Variance Std.Dev. Corr 
##  country  (Intercept)                   0.008936 0.09453       
##           accel_ben_rank_direct_funding 0.001665 0.04080  -0.49
##  Residual                               0.142950 0.37809       
## Number of obs: 16444, groups:  country, 83
## 
## Fixed effects:
##             Estimate Std. Error t value
## (Intercept)  0.19651    0.01228   16.01
\end{verbatim}

\begin{verbatim}
## Linear mixed model fit by maximum likelihood  ['lmerMod']
## Formula: 
## participated ~ accel_ben_rank_direct_funding * EOSQ425 + (accel_ben_rank_direct_funding |  
##     country)
##    Data: gali_joined
## 
##      AIC      BIC   logLik deviance df.resid 
##  14620.0  14681.5  -7302.0  14604.0    16177 
## 
## Scaled residuals: 
##     Min      1Q  Median      3Q     Max 
## -1.4017 -0.5138 -0.3955 -0.2813  2.4249 
## 
## Random effects:
##  Groups   Name                          Variance  Std.Dev. Corr 
##  country  (Intercept)                   0.0085583 0.09251       
##           accel_ben_rank_direct_funding 0.0009436 0.03072  -1.00
##  Residual                               0.1432556 0.37849       
## Number of obs: 16185, groups:  country, 74
## 
## Fixed effects:
##                                         Estimate Std. Error t value
## (Intercept)                            0.2004428  0.0710787   2.820
## accel_ben_rank_direct_funding         -0.0255510  0.0455072  -0.561
## EOSQ425                                0.0008104  0.0184340   0.044
## accel_ben_rank_direct_funding:EOSQ425 -0.0023544  0.0107909  -0.218
## 
## Correlation of Fixed Effects:
##             (Intr) ac____ EOSQ42
## accl_bn_r__ -0.490              
## EOSQ425     -0.984  0.485       
## a____:EOSQ4  0.533 -0.975 -0.545
## convergence code: 0
## boundary (singular) fit: see ?isSingular
\end{verbatim}

\begin{verbatim}
## Linear mixed model fit by maximum likelihood  ['lmerMod']
## Formula: 
## participated ~ accel_ben_rank_direct_funding * EOSQ089 + (accel_ben_rank_direct_funding |  
##     country)
##    Data: gali_joined
## 
##      AIC      BIC   logLik deviance df.resid 
##  14619.7  14681.2  -7301.8  14603.7    16177 
## 
## Scaled residuals: 
##     Min      1Q  Median      3Q     Max 
## -1.4020 -0.5136 -0.3962 -0.2810  2.4270 
## 
## Random effects:
##  Groups   Name                          Variance  Std.Dev. Corr 
##  country  (Intercept)                   0.0084870 0.09212       
##           accel_ben_rank_direct_funding 0.0009291 0.03048  -1.00
##  Residual                               0.1432565 0.37849       
## Number of obs: 16185, groups:  country, 74
## 
## Fixed effects:
##                                        Estimate Std. Error t value
## (Intercept)                            0.229561   0.046331   4.955
## accel_ben_rank_direct_funding         -0.037525   0.030596  -1.226
## EOSQ089                               -0.008695   0.014873  -0.585
## accel_ben_rank_direct_funding:EOSQ089  0.001088   0.008465   0.129
## 
## Correlation of Fixed Effects:
##             (Intr) ac____ EOSQ08
## accl_bn_r__ -0.477              
## EOSQ089     -0.961  0.464       
## a____:EOSQ0  0.539 -0.944 -0.566
## convergence code: 0
## boundary (singular) fit: see ?isSingular
\end{verbatim}

\begin{verbatim}
## Linear mixed model fit by maximum likelihood  ['lmerMod']
## Formula: participated ~ accel_ben_rank_direct_funding * DOMCREDITGDP +  
##     (accel_ben_rank_direct_funding | country)
##    Data: gali_joined
## 
##      AIC      BIC   logLik deviance df.resid 
##  14619.7  14681.2  -7301.8  14603.7    16177 
## 
## Scaled residuals: 
##     Min      1Q  Median      3Q     Max 
## -1.3992 -0.5115 -0.3980 -0.2807  2.4272 
## 
## Random effects:
##  Groups   Name                          Variance  Std.Dev. Corr 
##  country  (Intercept)                   0.0085682 0.09256       
##           accel_ben_rank_direct_funding 0.0009053 0.03009  -1.00
##  Residual                               0.1432523 0.37849       
## Number of obs: 16185, groups:  country, 74
## 
## Fixed effects:
##                                              Estimate Std. Error t value
## (Intercept)                                 2.113e-01  2.084e-02  10.137
## accel_ben_rank_direct_funding              -3.313e-02  1.549e-02  -2.139
## DOMCREDITGDP                               -1.339e-04  2.829e-04  -0.473
## accel_ben_rank_direct_funding:DOMCREDITGDP -1.288e-05  1.590e-04  -0.081
## 
## Correlation of Fixed Effects:
##             (Intr) ac____ DOMCRE
## accl_bn_r__ -0.414              
## DOMCREDITGD -0.788  0.334       
## a____:DOMCR  0.441 -0.768 -0.567
## convergence code: 0
## boundary (singular) fit: see ?isSingular
\end{verbatim}

\begin{verbatim}
## Linear mixed model fit by maximum likelihood  ['lmerMod']
## Formula: capital_raised_tot ~ +(accel_ben_rank_direct_funding | country)
##    Data: gali_joined
## 
##       AIC       BIC    logLik  deviance  df.resid 
##  628881.3  628919.9 -314435.7  628871.3     16439 
## 
## Scaled residuals: 
##     Min      1Q  Median      3Q     Max 
##  -0.756  -0.010  -0.008  -0.004 126.757 
## 
## Random effects:
##  Groups   Name                          Variance  Std.Dev. Corr 
##  country  (Intercept)                   1.168e+13  3417674      
##           accel_ben_rank_direct_funding 4.366e+13  6607224 -1.00
##  Residual                               2.373e+15 48709324      
## Number of obs: 16444, groups:  country, 83
## 
## Fixed effects:
##             Estimate Std. Error t value
## (Intercept)   607877     562167   1.081
## convergence code: 0
## boundary (singular) fit: see ?isSingular
\end{verbatim}

\begin{verbatim}
## Linear mixed model fit by maximum likelihood  ['lmerMod']
## Formula: capital_raised_tot ~ accel_ben_rank_direct_funding * EOSQ425 +  
##     (accel_ben_rank_direct_funding | country)
##    Data: gali_joined
## 
##       AIC       BIC    logLik  deviance  df.resid 
##  619237.1  619298.6 -309610.6  619221.1     16177 
## 
## Scaled residuals: 
##     Min      1Q  Median      3Q     Max 
##  -0.770  -0.009  -0.006  -0.004 125.749 
## 
## Random effects:
##  Groups   Name                          Variance  Std.Dev. Corr 
##  country  (Intercept)                   1.205e+13  3471900      
##           accel_ben_rank_direct_funding 4.540e+13  6737688 -1.00
##  Residual                               2.410e+15 49094901      
## Number of obs: 16185, groups:  country, 74
## 
## Fixed effects:
##                                       Estimate Std. Error t value
## (Intercept)                            3278060    3931054   0.834
## accel_ben_rank_direct_funding         -5097275    8516455  -0.599
## EOSQ425                                -589495    1003353  -0.588
## accel_ben_rank_direct_funding:EOSQ425   972897    2131244   0.456
## 
## Correlation of Fixed Effects:
##             (Intr) ac____ EOSQ42
## accl_bn_r__ -0.717              
## EOSQ425     -0.982  0.725       
## a____:EOSQ4  0.740 -0.980 -0.771
## convergence code: 0
## boundary (singular) fit: see ?isSingular
\end{verbatim}

\begin{verbatim}
## Linear mixed model fit by maximum likelihood  ['lmerMod']
## Formula: capital_raised_tot ~ accel_ben_rank_direct_funding * EOSQ089 +  
##     (accel_ben_rank_direct_funding | country)
##    Data: gali_joined
## 
##       AIC       BIC    logLik  deviance  df.resid 
##  619236.9  619298.5 -309610.5  619220.9     16177 
## 
## Scaled residuals: 
##     Min      1Q  Median      3Q     Max 
##  -0.771  -0.009  -0.006  -0.004 125.749 
## 
## Random effects:
##  Groups   Name                          Variance  Std.Dev. Corr 
##  country  (Intercept)                   1.196e+13  3458659      
##           accel_ben_rank_direct_funding 4.502e+13  6709707 -1.00
##  Residual                               2.410e+15 49094926      
## Number of obs: 16185, groups:  country, 74
## 
## Fixed effects:
##                                       Estimate Std. Error t value
## (Intercept)                            2758748    2542379   1.085
## accel_ben_rank_direct_funding         -4463383    5575404  -0.801
## EOSQ089                                -575121     797830  -0.721
## accel_ben_rank_direct_funding:EOSQ089  1016469    1690294   0.601
## 
## Correlation of Fixed Effects:
##             (Intr) ac____ EOSQ08
## accl_bn_r__ -0.700              
## EOSQ089     -0.957  0.703       
## a____:EOSQ0  0.729 -0.952 -0.787
## convergence code: 0
## boundary (singular) fit: see ?isSingular
\end{verbatim}

\begin{verbatim}
## Linear mixed model fit by maximum likelihood  ['lmerMod']
## Formula: capital_raised_tot ~ accel_ben_rank_direct_funding * DOMCREDITGDP +  
##     (accel_ben_rank_direct_funding | country)
##    Data: gali_joined
## 
##       AIC       BIC    logLik  deviance  df.resid 
##  619237.2  619298.7 -309610.6  619221.2     16177 
## 
## Scaled residuals: 
##     Min      1Q  Median      3Q     Max 
##  -0.770  -0.007  -0.006  -0.004 125.749 
## 
## Random effects:
##  Groups   Name                          Variance  Std.Dev. Corr 
##  country  (Intercept)                   1.208e+13  3475044      
##           accel_ben_rank_direct_funding 4.521e+13  6724103 -1.00
##  Residual                               2.410e+15 49095018      
## Number of obs: 16185, groups:  country, 74
## 
## Fixed effects:
##                                            Estimate Std. Error t value
## (Intercept)                                 1451825    1141899   1.271
## accel_ben_rank_direct_funding              -2232392    2605340  -0.857
## DOMCREDITGDP                                  -7480      14628  -0.511
## accel_ben_rank_direct_funding:DOMCREDITGDP    13756      31129   0.442
## 
## Correlation of Fixed Effects:
##             (Intr) ac____ DOMCRE
## accl_bn_r__ -0.615              
## DOMCREDITGD -0.764  0.519       
## a____:DOMCR  0.555 -0.760 -0.779
## convergence code: 0
## boundary (singular) fit: see ?isSingular
\end{verbatim}

\#Mixed model analysis - Social capital

\begin{verbatim}
##                          Estimate Std. Error   t value
## (Intercept)            0.20204321 0.01250494 16.157077
## accel_ben_rank_network 0.01914256 0.00950974  2.012943
\end{verbatim}

\begin{verbatim}
##                                    Estimate Std. Error    t value
## (Intercept)                     0.295903338 0.06852242  4.3183434
## accel_ben_rank_network          0.023874383 0.05035733  0.4740994
## EOSQ109                        -0.023521692 0.01733603 -1.3568099
## accel_ben_rank_network:EOSQ109 -0.001363126 0.01125294 -0.1211352
\end{verbatim}

\begin{verbatim}
##                          Estimate Std. Error   t value
## (Intercept)            0.57431349 0.04229280 13.579463
## accel_ben_rank_network 0.06431639 0.04574601  1.405945
\end{verbatim}

\begin{verbatim}
##                                  Estimate Std. Error   t value
## (Intercept)                    -0.2693634 0.20697678 -1.301419
## accel_ben_rank_network         -0.5635796 0.23434531 -2.404911
## EOSQ109                         0.2155408 0.05213442  4.134328
## accel_ben_rank_network:EOSQ109  0.1600702 0.05499693  2.910531
\end{verbatim}

\hypertarget{discussion}{%
\section{Discussion}\label{discussion}}

\newpage

\hypertarget{references}{%
\section{References}\label{references}}

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

\hypertarget{refs}{}
\leavevmode\hypertarget{ref-R-papaja}{}%
Aust, F., \& Barth, M. (2020). \emph{papaja: Create APA manuscripts with R Markdown}. Retrieved from \url{https://github.com/crsh/papaja}

\leavevmode\hypertarget{ref-R-Matrix}{}%
Bates, D., \& Maechler, M. (2019). \emph{Matrix: Sparse and dense matrix classes and methods}. Retrieved from \url{https://CRAN.R-project.org/package=Matrix}

\leavevmode\hypertarget{ref-R-lme4}{}%
Bates, D., Mächler, M., Bolker, B., \& Walker, S. (2015). Fitting linear mixed-effects models using lme4. \emph{Journal of Statistical Software}, \emph{67}(1), 1--48. \url{https://doi.org/10.18637/jss.v067.i01}

\leavevmode\hypertarget{ref-R-base}{}%
R Core Team. (2020). \emph{R: A language and environment for statistical computing}. Vienna, Austria: R Foundation for Statistical Computing. Retrieved from \url{https://www.R-project.org/}

\endgroup

\end{document}

### 2021-03-06 Manuscript.Rmd
manuscript development

@@
 ---
-title             : "The title"
-shorttitle        : "Title"
+title             : "An institutional approach to attention allocation and venture resource mobilization and acquisition"
+shorttitle        : "An institutional approach to venture attention allocation"
 
@@
     corresponding : yes    # Define only one corresponding author
-    address       : "Postal address"
+    address       : "292A Anstett"
     email         : "ohmaddi@uoregon.edu"
@@
 authornote: |
-  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.
+  Lundquist College of Business
 
-  Enter author note here.
+  Department of Management
 
@@
 
-  Two to three sentences of **more detailed background**, comprehensible  to scientists in related disciplines.
-
-  One sentence clearly stating the **general problem** being addressed by  this particular study.
-
-  One sentence summarizing the main result (with the words "**here we show**" or their equivalent).
-
-  Two or three sentences explaining what the **main result** reveals in direct comparison to what was thought to be the case previously, or how the  main result adds to previous knowledge.
-
-  One or two sentences to put the results into a more **general context**.
-
-  Two or three sentences to provide a **broader perspective**, readily comprehensible to a scientist in any discipline.
-
   <!-- https://tinyurl.com/ybremelq -->
 
-keywords          : "keywords"
-wordcount         : "X"
+keywords          : "attention, resources, institutional capital, accelerators"
 
@@
 
-# Methods
-We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study.
-<!-- 21-word solution (Simmons, Nelson & Simonsohn, 2012; retrieved from http://ssrn.com/abstract=2160588) -->
+# Introduction 
+Early stage entrepreneurs are faced with a range of resource choices to seek, and must decide what should garner their attention.
+The literature on entrepreneurial resources argues the resources entrepreneurs possess shape their resource acquisition and once they raise one resource others follow.
+Thus, one might theorize that founders should focus their attention on the resource they can leverage based on their existing resource endowment.
+However, resource acquisition depends on both entrepreneurs’ resource endowment and the institutional-level capital.
+Both are indispensable antecedents that affect the mobilization and acquisition of additional capital.
 
-## Participants
+The value of a resource varies with its institutional context [@holburn2010political].
+On the one hand, strong institutions can increase the value of a resource by streamlining access to complementary external resources [@khanna2001estimating; @north1990institutions].
+For example, in countries with strong financing infrastructure, acquiring financing can streamline accessing other resources and thus it would make sense to focus on raising capital at venture’s earliest stages.
+On the other hand, resources such as legitimation or social capital can substitute for the weak institutions and capital infrastructure, thereby increasing in value when institutions are weak [@khanna1997focused; @kock2001strategy].
+Therefore, the broader environment can enhance or inhibit the optimal use of the endowed resource capital.
+I posit that an examination of both the venture and its broader institutional environment would give us more insights about where founders attention should be allocated.
+Specifically, I hypothesize that the institutional-level capital positively moderates the relationship between a founder’s attention and its subsequent resource mobilization and acquisition.
+For example, attention to human capital is more positively related to a higher number of employees in contexts in which it has higher intuitional-level human capital.
+This similarly applies to social capital, and financial capital as the types of resources sought by entrepreneurs.
+Thus, in this paper I seek to examine the following research question: How does the alignment of the institutional context and the allocation of entrepreneurial attention toward specific resources influence the venture’s resource mobilization and acquisition?
 
-## Material
+# Hypotheses Development 
+At the heart of the intersection between resource acquisition and the institutional context is entrepreneurial attention, that is, founders’ attention allocation to resources.
+Bounded by their limited attentional capacities, entrepreneurs cannot attend to all the resources; rather, they focus on some resources but must ignore others.
+Where they focus their attention determines the propensity of mobilizing and acquiring resources.
+A venture could miss the chance to exploit an opportunity of resources acquisition if that opportunity never appears on the entrepreneur’s radar screens because they are too focused on an alternative resource.
+For example, a voluntary work with potential partners who are well connected to other investors might be missed because the founder is too focused on raising capital by honing their business plan over and over and even paying accounting boutique firms to develop that business plan for them.
 
-## Procedure
+Thus, selective attention plays a crucial role in both individual and organizational behavior because it bounds individual rationality and determines the menu of available actions [@simon1947comment].
+The debate over which resource should garner the entrepreneur’s attention concludes that the founding team resource endowment is the key factor that influences resource acquisition.
+For instance, scholars argue that founding teams with a more ties to potential investors are more likely to gain funding [@shane2002organizational].
+Furthermore, if we focus on the findings of the stream of research examining the performance implications of acquiring financial capital [@hochberg2007whom] we would expect that early-stage financing should be most likely to garner founders’ attention.
+However, the role of the institutional context has been ignored and neglected in this debate.
+I argue that selective attention allocation depends on both entrepreneur’s resource endowment and institutional capital.
+
+Therefore, I state the following hypotheses about the relationship between the congruence level of the entrepreneurs' attention to resources and the institutional level capital, and the venture's resource mobilization, acquisition, and performance.
+
+**Hypothesis 1** *The higher the level of congruency of venture’s attention to a resource and its institutional level capital, the higher the odds of mobilization that resource*
+
+**Hypothesis 2** *The higher the level of congruency of venture’s attention to a resource and its institutional level capital, the higher the level of the accumulated resource*
+
+**Hypothesis 3** *The higher the level of congruency of venture’s attention to a resource and its institutional level capital, the higher the venture performance*
+
+# Analysis
+
+## Measures
+
+*Predictors*
+*Outcomes*
+*Control Variables*
+**Human Capital Index** consists of educational attainment, prior career experience in executive positions (C-level positions), team tenure, and prior founding experience [@colombo2005founders; @dimov2005human; @estrin2016human].
+I measure the educational attainment of a founding team by calculating the percentage of founders with a graduate degree in the founding team (Graduate Percentage).
+Prior career experience in C-level executive positions (Prior C-level Executive Percentage) is measured by the percentage of founders in the founding teams holding C-level executive positions prior to the current venture.
+Average Team Tenure measures the average working years of the founding team members.
+Team Prior Founding measures the number of organizations founded by the founding team before the current venture.
+
+To create an index, I use the quantile normalization technique to reduce the effect of extreme values while preserving the sequence of an observation in each variable [@hansen2012removing].
+Quantile normalization makes two or more distributions identical in statistical properties, such as maximum, minimum, and mean, without a reference distribution.
+It maintains the order, namely quantile, of observations in each variable treated but the values are normalized with respect to values from other variables at the same quantile.
+After doing so, the extreme values observed in some variables are smoothed out while the order is preserved, allowing us to explore the effect of each variable more accurately.
+I first z-standardize the above-mentioned variables.
+Then, I use the {preprocessCore} package to conduct quantile normalization by sets of variables.
+I then rescale the index to a range between 0 and 1.
+
+**Gender Decomposition**
+
+## Data
+The dataset from the Global Accelerator Learning Initiative (GALI) covers entrepreneurs who applied to scores of accelerators that began accepting applications between 2013 and 2020.
+Our data include information – collected during program applications – about ventures, founding teams, and pre-program performance.
+They also identify which applicants went on to participate in each program.
+Finally, these data include follow-up information collected from selected and rejected applicants in the years following each application window.
+The anonymized dataset containing both application and follow-up data can be accessed at [GALI Data](www.galidata.org/data-request).
+
+This is multi-country dataset. It typically contain hundreds of ventures per country.
+
+When entrepreneurs apply to a GALI-participating accelerator, they are asked to complete a standardized survey which asks basic questions about their venture’s business model, financial performance, and founding team.
+Then, after one year, they are asked to complete a follow-up survey, whether or not they were accepted into the program to which they applied.
+
+All financial statistics are in United States Dollars (USD).
+
+Table 1: Ventures in sample, by country of operation and survey responses
+
+## Methods
+Mixed-effects logit and probit
+
+Given the structure of the data I used a model that incorporates both fixed- and random-effects terms.
+This helps me take into account the institutional (i.e.
+country) effect on venture outcomes and quantify the extent to which differences in outcomes reflect differences in the effects of country-specific features, specifically institutional level capital.
+
+yic=Xicβ+Zcγ+uc+εic,  withi=1,…,Nc;c=1,…,C.
+
+Outcome y ic for each person i in country c is assumed to depend on observed predictors and unobserved factors.
+Xic contains variables that summarize individual-level characteristics such as age, education, or marital status; Zc contains variables summarizing country-level features such as socio-economic institutions or labour markets.
+There are also unobserved individual effects ( ε ic ) and country effects ( u c ), each assumed to be normally distributed and uncorrelated with Xic and Zc .
+We suppose the researcher has available a data set with a large number of individuals for each country ( N c is typically in the thousands) sampled from each of a small number of countries ( C is typically less than 30).
+The parameters associated with the observed predictors β and γ are sometimes called ‘fixed’ regression parameters to distinguish them from the parameters characterizing the joint distribution of the random terms ε ic and u c (their variances σ2ε and σ2u ).
+These variances are often referred to as ‘random effect’ parameters or ‘variance components’.
 
 ## Data analysis
-We used `r cite_r("r-references.bib")` for all our analyses.
+I used `r cite_r("r-references.bib")` for all our analyses.
 ```{r message=FALSE, warning=FALSE, include=FALSE}
@@
 library(knitr)
+library(preprocessCore)
 
@@
 gali <- import("Data/GALI_External_DataRelease_2020.xlsx") 
-
+wb <- import("Data/CLASS.xls")
 count(gali,info_venture_country_hq)
@@
 
+##Control variables
+
+##Constrcuting human capital index (control variable)
+###Graduate percentage, Prior C-level Executive Percentage, Average Team Tenure , Team Prior Founding
+
+```{r Human capital index}
+#Graduate percentage
+
+gali$founder1_grad = ifelse(gali$found_name1_education == "Masters Degree" | 
+                              gali$found_name1_education =="PhD" |
+                              gali$found_name1_education == "Some graduate degree", 1, 0) 
+gali$founder1_grad[is.na(gali$founder1_grad)] <- 0
+
+gali$founder2_grad = ifelse(gali$found_name2_education == "Masters Degree" | 
+                              gali$found_name2_education =="PhD" |
+                              gali$found_name2_education == "Some graduate degree", 1, 0) 
+gali$founder2_grad[is.na(gali$founder2_grad)] <- 0
+
+gali$founder3_grad = ifelse(gali$found_name3_education == "Masters Degree" |
+                              gali$found_name3_education =="PhD" |
+                              gali$found_name3_education == "Some graduate degree", 1, 0)
+gali$founder3_grad[is.na(gali$founder3_grad)] <- 0
+
+gali$nb_of_founders <- gali$found_name1_present + gali$found_name2_present + gali$found_name3_present
+
+gali <- filter(gali, nb_of_founders > 0)
+
+gali$grad_pct = ((gali$founder1_grad + gali$founder2_grad + gali$founder3_grad) / gali$nb_of_founders)
+
+#Prior C-level Executive Percentage
+
+gali$founder1_job1_clevel = ifelse(is.na(gali$found_name1_job1_role) | gali$found_name1_job1_role !=  "CEO/Executive Director" , 0, 1)
+gali$founder1_job2_clevel = ifelse(is.na(gali$found_name1_job2_role) | gali$found_name1_job2_role !=  "CEO/Executive Director" , 0, 1)
+gali$founder2_job1_clevel = ifelse(is.na(gali$found_name2_job1_role) | gali$found_name2_job1_role !=  "CEO/Executive Director" , 0, 1)
+gali$founder2_job2_clevel = ifelse(is.na(gali$found_name2_job2_role) | gali$found_name2_job2_role !=  "CEO/Executive Director" , 0, 1)
+gali$founder3_job1_clevel = ifelse(is.na(gali$found_name3_job1_role) | gali$found_name3_job1_role !=  "CEO/Executive Director" , 0, 1)
+gali$founder3_job2_clevel = ifelse(is.na(gali$found_name3_job2_role) | gali$found_name3_job2_role !=  "CEO/Executive Director" , 0, 1)
+
+gali$prior_clevel_pct = ((gali$founder1_job1_clevel + gali$founder1_job2_clevel + gali$founder2_job1_clevel + 
+  gali$founder2_job2_clevel + gali$founder3_job1_clevel + gali$founder3_job2_clevel) / (gali$nb_of_founders*2))
+
+#Average Team Tenure
+
+gali$avg_teamtenure <- rowMeans(subset(gali, select = c('found_name1_job1_tenure', 'found_name1_job2_tenure', 'found_name2_job1_tenure', 'found_name2_job2_tenure', 'found_name3_job1_tenure', 'found_name3_job2_tenure')), na.rm = TRUE)
+
+gali$avg_teamtenure[is.nan(gali$avg_teamtenure)] <- 0
+
+#Team Prior Founding
+gali$team_prior_founding <- gali$found_name1_prior_fp + gali$found_name2_prior_fp + gali$found_name3_prior_fp + gali$found_name1_prior_other + gali$found_name2_prior_other + gali$found_name3_prior_other + gali$found_name1_prior_np + gali$found_name2_prior_np + gali$found_name3_prior_np
+
+#Final Human Capital Index
+
+gali$z_team_prior_founding <- scale(gali$team_prior_founding, center = TRUE, scale = TRUE)
+gali$z_prior_clevel_pct <- scale(gali$prior_clevel_pct, center = TRUE, scale = TRUE)
+gali$z_avg_teamtenure <- scale(gali$avg_teamtenure, center = TRUE, scale = TRUE)
+gali$z_grad_pct <- scale(gali$grad_pct, center = TRUE, scale = TRUE)
+
+#Cite Bolstad et al, Bioinformatics (2003)
+
+gali$normq_team_prior_founding <- normalize.quantiles(gali$z_team_prior_founding,copy=TRUE)
+gali$normq_prior_clevel_pct <- normalize.quantiles(gali$z_prior_clevel_pct,copy=TRUE)
+gali$normq_avg_teamtenure <- normalize.quantiles(gali$z_avg_teamtenure,copy=TRUE)
+gali$normq_grad_pct <- normalize.quantiles(gali$z_grad_pct,copy=TRUE)
+
+#group all into an index
+
+gali$HC_index <- (gali$normq_team_prior_founding + gali$normq_prior_clevel_pct + gali$normq_avg_teamtenure + gali$normq_grad_pct)
+
+```
+
+##Gender decomposition variable
+
+```{r Gender decomposition variable}
+gali <- gali %>% drop_na(found_name1_gender)
+
+gali$found_name2_gender[is.na(gali$found_name2_gender)] <- 0
+gali$found_name3_gender[is.na(gali$found_name3_gender)] <- 0
+
+gali$founder1_f <- ifelse(gali$found_name1_gender == "F", 1,0)
+gali$founder2_f <- ifelse(gali$found_name2_gender == "F", 1,0)
+gali$founder3_f <- ifelse(gali$found_name3_gender == "F", 1,0)
+
+gali$female_pct <- round(((gali$founder1_f + gali$founder2_f + gali$founder3_f) / gali$nb_of_founders ), 2)
+
+```
+
 #Reverse code attention variable 
@@
 #Reverse code fundtion 
-reverse <- function(x){x*-1- +8}
+reverse <- function(x){x*-1 +8}
 
@@
         select(-starts_with("accel_ben_rank_")), gali_att)
+
+```
+
+#Distribution of attention
+
+```{r fig.height=5, fig.width=8}
+a <- gali %>%
+  select(country, starts_with("accel_ben_rank_"))
+
+colnames(a) <- c( "Country", "Network", "Business Skills", "Mentorship", "Investors", "Direct Funding", "Peers", "Credibility")
+
+a <- left_join(a, wb, by = "Country" )
+
+a <- a %>%
+  pivot_longer(!c("Country", "Region","Income group"), names_to = "Attention", values_to = "Score")
+
+a[is.na(a)] <- "High Income"  #The two countries with NA values are USA and UK because of naming issues. They are both classified high income
+
+a  %>%
+  ggplot(aes(Score)) +
+  geom_bar() +
+  facet_grid(~Attention) +
+  theme_bw()
+
+#Some countries are classified as "High income" while other are "High Income". I will capitilize all first letter to solve this issue
+
+simpleCap <- function(x) {
+  s <- strsplit(x, " ")[[1]]
+  paste(toupper(substring(s, 1,1)), substring(s, 2),
+      sep="", collapse=" ")
+}
+
+a$`Income group` <- gsub("(^|[[:space:]])([[:alpha:]])", "\\1\\U\\2", a$`Income group`, perl=TRUE)
+
+a  %>%
+  ggplot(aes(Score)) +
+  geom_bar() +
+  facet_grid(vars(`Income group`), vars(Attention)) +
+  theme_bw()
+
+```
+
+##Outcomes
+
+#Revenues
+```{r message=FALSE, warning=FALSE, include=FALSE}
+gali <- gali %>% mutate(revenue_tot = gali %>%
+                         select(contains("revenues")) %>% 
+                         rowSums(na.rm = TRUE))
+```
+
+#Human capital acquisition 
+```{r message=FALSE, warning=FALSE, include=FALSE}
+gali  <- gali %>% mutate(hr_tot = gali %>%
+                         select(contains("_employees")) %>% 
+                         rowSums(na.rm = TRUE))
+```
+
+#Social capital acquisition 
+```{r message=FALSE, warning=FALSE, include=FALSE}
+gali <- gali %>% mutate(equity_sources_tot = gali %>%
+                         select(contains("equityfrom")) %>% 
+                         rowSums(na.rm = TRUE))
+```
+
+#Fiancial Capital acquisiton total
+```{r message=FALSE, warning=FALSE, include=FALSE}
+gali  <- gali %>% mutate(capital_raised0 = gali %>% select(starts_with("inv_") & ends_with("_m1")) %>% 
+                         rowSums(na.rm = TRUE))
+
+gali  <- gali %>% mutate(capital_raised1 = gali %>% select(starts_with("fu1inv_") & ends_with("_m1")) %>% 
+                         rowSums(na.rm = TRUE))
+
+gali  <- gali %>% mutate(capital_raised2 = gali %>% select(starts_with("fu2inv_") & ends_with("_m1")) %>% 
+                         rowSums(na.rm = TRUE))
+
+gali  <- gali %>% mutate(capital_raised3 = gali %>% select(starts_with("fu3inv_") & ends_with("_m1")) %>% 
+                         rowSums(na.rm = TRUE))
+
+gali  <- gali %>% mutate(capital_raised4 = gali %>% select(starts_with("fu4inv_") & ends_with("_m1")) %>% 
+                         rowSums(na.rm = TRUE))
+
+gali  <- gali %>% mutate(capital_raised_tot = gali %>% select(starts_with("capital_raised")) %>% 
+                         rowSums(na.rm = TRUE))
+
+```
+
+#Predictor and outcome plots 
+```{r}
+
+b <- gali %>%
+  select(country, equity_sources_tot, revenue_tot, capital_raised_tot, starts_with("accel_ben_rank_"))
+
+colnames(b) <- c( "Country", "Total Equity Sources", "Revenue", "Capital Raised", "Network", "Business Skills", "Mentorship", "Investors", "Direct Funding", "Peers", "Credibility")
+
+b <- left_join(b, wb, by = "Country" )
+
+b <- b %>%
+  pivot_longer(!c("Country", "Total Equity Sources", "Income group", "Region", "Revenue", "Capital Raised"), names_to = "Attention", values_to = "Score")
+
+b[is.na(b)] <- "High Income"  #The two countries with NA values are USA and UK because of naming issues. They are both classified high income
+
+#Some countries are classified as "High income" while other are "High Income". I will capitilize all first letter to solve this issue
+
+b$`Income group` <- gsub("(^|[[:space:]])([[:alpha:]])", "\\1\\U\\2", b$`Income group`, perl=TRUE)
+
+filter(b, Attention == "Network")  %>%
+  ggplot(aes(Score, `Total Equity Sources`)) +
+  geom_point()  +
+  facet_grid(~`Income group`)+
+  theme_bw()
+
+filter(b, Attention == "Direct Funding")  %>%
+  ggplot(aes(Score, `Capital Raised`)) +
+  geom_point()  +
+  facet_grid(~`Income group`)+
+  theme_bw()
 
@@
 
-```
-
-#Fiancial Capital acquisiton total
-```{r message=FALSE, warning=FALSE, include=FALSE}
-gali_joined  <- gali_joined %>% mutate(capital_raised0 = gali_joined %>% select(starts_with("inv_") & ends_with("_m1")) %>% 
-                         rowSums(na.rm = TRUE))
-
-gali_joined  <- gali_joined %>% mutate(capital_raised1 = gali_joined %>% select(starts_with("fu1inv_") & ends_with("_m1")) %>% 
-                         rowSums(na.rm = TRUE))
-
-gali_joined  <- gali_joined %>% mutate(capital_raised2 = gali_joined %>% select(starts_with("fu2inv_") & ends_with("_m1")) %>% 
-                         rowSums(na.rm = TRUE))
-
-gali_joined  <- gali_joined %>% mutate(capital_raised3 = gali_joined %>% select(starts_with("fu3inv_") & ends_with("_m1")) %>% 
-                         rowSums(na.rm = TRUE))
-
-gali_joined  <- gali_joined %>% mutate(capital_raised4 = gali_joined %>% select(starts_with("fu4inv_") & ends_with("_m1")) %>% 
-                         rowSums(na.rm = TRUE))
-
-gali_joined  <- gali_joined %>% mutate(capital_raised_tot = gali_joined %>% select(starts_with("capital_raised")) %>% 
-                         rowSums(na.rm = TRUE))
-
-```
-
-#Revenues
-```{r message=FALSE, warning=FALSE, include=FALSE}
-gali_joined <- gali_joined %>% mutate(revenue_tot = gali_joined %>%
-                         select(contains("revenues")) %>% 
-                         rowSums(na.rm = TRUE))
-```
-
-#Human capital acquisition 
-```{r message=FALSE, warning=FALSE, include=FALSE}
-gali_joined  <- gali_joined %>% mutate(hr_tot = gali_joined %>%
-                         select(contains("_employees")) %>% 
-                         rowSums(na.rm = TRUE))
-```
-
-#Social capital acquisition 
-```{r message=FALSE, warning=FALSE, include=FALSE}
-gali_joined <- gali_joined %>% mutate(equity_sources_tot = gali_joined %>%
-                         select(contains("equityfrom")) %>% 
-                         rowSums(na.rm = TRUE))
 ```
@@
 fit11hc <- lmer(hr_tot ~  accel_ben_rank_business_skills*EOSQ403 + (accel_ben_rank_business_skills|country), data = gali_joined, REML = F)
+
 hc0 <- summary_table_z(summary(fit0hc))
@@
 
-kable(hc0[,-1]) 
-kable(hc1[,-1])
-kable(hc00[,-1])
-kable(hc11[,-1])
+kable(hc0[,-1], escape = FALSE) 
+kable(hc1[,-1], escape = FALSE)
+kable(hc00[,-1], escape = FALSE)
+kable(hc11[,-1], escape = FALSE)
 
@@
 
+# Data and Methods
+
 # Discussion

### 2021-03-06 Manuscript.tex
manuscript development

@@
 \hypersetup{
-  pdftitle={The title},
+  pdftitle={An institutional approach to attention allocation and venture resource mobilization and acquisition},
   pdfauthor={Ouafaa Hmaddi1},
-  pdfkeywords={keywords},
+  pdfkeywords={attention, resources, institutional capital, accelerators},
   hidelinks,
@@
 \makeatother
-\shorttitle{Title}
-\keywords{keywords\newline\indent Word count: X}
+\shorttitle{An institutional approach to venture attention allocation}
+\keywords{attention, resources, institutional capital, accelerators}
 \DeclareDelayedFloatFlavor{ThreePartTable}{table}
@@
 
-\title{The title}
+\title{An institutional approach to attention allocation and venture resource mobilization and acquisition}
 \author{Ouafaa Hmaddi\textsuperscript{1}}
@@
 
-Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.
+Lundquist College of Business
 
-Enter author note here.
+Department of Management
 
@@
 
-Correspondence concerning this article should be addressed to Ouafaa Hmaddi, Postal address. E-mail: \href{mailto:ohmaddi@uoregon.edu}{\nolinkurl{ohmaddi@uoregon.edu}}
+Correspondence concerning this article should be addressed to Ouafaa Hmaddi, 292A Anstett. E-mail: \href{mailto:ohmaddi@uoregon.edu}{\nolinkurl{ohmaddi@uoregon.edu}}
 
@@
 One or two sentences providing a \textbf{basic introduction} to the field, comprehensible to a scientist in any discipline.
-
-Two to three sentences of \textbf{more detailed background}, comprehensible to scientists in related disciplines.
-
-One sentence clearly stating the \textbf{general problem} being addressed by this particular study.
-
-One sentence summarizing the main result (with the words ``\textbf{here we show}'' or their equivalent).
-
-Two or three sentences explaining what the \textbf{main result} reveals in direct comparison to what was thought to be the case previously, or how the main result adds to previous knowledge.
-
-One or two sentences to put the results into a more \textbf{general context}.
-
-Two or three sentences to provide a \textbf{broader perspective}, readily comprehensible to a scientist in any discipline.
 }
@@
 
+\hypertarget{introduction}{%
+\section{Introduction}\label{introduction}}
+
+Early stage entrepreneurs are faced with a range of resource choices to seek, and must decide what should garner their attention.
+The literature on entrepreneurial resources argues the resources entrepreneurs possess shape their resource acquisition and once they raise one resource others follow.
+Thus, one might theorize that founders should focus their attention on the resource they can leverage based on their existing resource endowment.
+However, resource acquisition depends on both entrepreneurs' resource endowment and the institutional-level capital.
+Both are indispensable antecedents that affect the mobilization and acquisition of additional capital.
+
+The value of a resource varies with its institutional context (Holburn \& Zelner, 2010).
+On the one hand, strong institutions can increase the value of a resource by streamlining access to complementary external resources (Khanna \& Rivkin, 2001; North \& others, 1990).
+For example, in countries with strong financing infrastructure, acquiring financing can streamline accessing other resources and thus it would make sense to focus on raising capital at venture's earliest stages.
+On the other hand, resources such as legitimation or social capital can substitute for the weak institutions and capital infrastructure, thereby increasing in value when institutions are weak (Khanna \& Palepu, 1997; Kock \& Guillén, 2001).
+Therefore, the broader environment can enhance or inhibit the optimal use of the endowed resource capital.
+I posit that an examination of both the venture and its broader institutional environment would give us more insights about where founders attention should be allocated.
+Specifically, I hypothesize that the institutional-level capital positively moderates the relationship between a founder's attention and its subsequent resource mobilization and acquisition.
+For example, attention to human capital is more positively related to a higher number of employees in contexts in which it has higher intuitional-level human capital.
+This similarly applies to social capital, and financial capital as the types of resources sought by entrepreneurs.
+Thus, in this paper I seek to examine the following research question: How does the alignment of the institutional context and the allocation of entrepreneurial attention toward specific resources influence the venture's resource mobilization and acquisition?
+
+\hypertarget{hypotheses-development}{%
+\section{Hypotheses Development}\label{hypotheses-development}}
+
+At the heart of the intersection between resource acquisition and the institutional context is entrepreneurial attention, that is, founders' attention allocation to resources.
+Bounded by their limited attentional capacities, entrepreneurs cannot attend to all the resources; rather, they focus on some resources but must ignore others.
+Where they focus their attention determines the propensity of mobilizing and acquiring resources.
+A venture could miss the chance to exploit an opportunity of resources acquisition if that opportunity never appears on the entrepreneur's radar screens because they are too focused on an alternative resource.
+For example, a voluntary work with potential partners who are well connected to other investors might be missed because the founder is too focused on raising capital by honing their business plan over and over and even paying accounting boutique firms to develop that business plan for them.
+
+Thus, selective attention plays a crucial role in both individual and organizational behavior because it bounds individual rationality and determines the menu of available actions (Simon, 1947).
+The debate over which resource should garner the entrepreneur's attention concludes that the founding team resource endowment is the key factor that influences resource acquisition.
+For instance, scholars argue that founding teams with a more ties to potential investors are more likely to gain funding (Shane \& Stuart, 2002).
+Furthermore, if we focus on the findings of the stream of research examining the performance implications of acquiring financial capital (e.g.; (Hochberg, Ljungqvist, \& Lu, 2007)) we would expect that early-stage financing should be most likely to garner founders' attention.
+However, the role of the institutional context has been ignored and neglected in this debate.
+I argue that selective attention allocation depends on both entrepreneur's resource endowment and institutional capital.
+
+Therefore, I state the following hypotheses about the relationship between the congruence level of the entrepreneurs' attention to resources and the institutional level capital, and the venture's resource mobilization, acquisition, and performance.
+
+\textbf{Hypothesis 1} \emph{The higher the level of congruency of venture's attention to a resource and its institutional level capital, the higher the odds of mobilization that resource}
+
+\textbf{Hypothesis 2} \emph{The higher the level of congruency of venture's attention to a resource and its institutional level capital, the higher the level of the accumulated resource}
+
+\textbf{Hypothesis 3} \emph{The higher the level of congruency of venture's attention to a resource and its institutional level capital, the higher the venture performance}
+
+\hypertarget{analysis}{%
+\section{Analysis}\label{analysis}}
+
+\hypertarget{measures}{%
+\subsection{Measures}\label{measures}}
+
+\hypertarget{data}{%
+\subsection{Data}\label{data}}
+
 \hypertarget{methods}{%
-\section{Methods}\label{methods}}
+\subsection{Methods}\label{methods}}
 
 We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study.
-
-\hypertarget{participants}{%
-\subsection{Participants}\label{participants}}
-
-\hypertarget{material}{%
-\subsection{Material}\label{material}}
-
-\hypertarget{procedure}{%
-\subsection{Procedure}\label{procedure}}
 
@@
 
-We used R (Version 4.0.2; R Core Team, 2020) and the R-packages \emph{lme4} (Version 1.1.23; Bates, Mächler, Bolker, \& Walker, 2015), \emph{Matrix} (Version 1.2.18; Bates \& Maechler, 2019), and \emph{papaja} (Version 0.1.0.9997; Aust \& Barth, 2020) for all our analyses.
+I used R (Version 4.0.2; R Core Team, 2020b) and the R-packages \emph{caret} (Version 6.0.86; Kuhn, 2020), \emph{dplyr} (Version 1.0.0; Wickham et al., 2020), \emph{EFAutilities} (Version 2.0.0; Zhang, Jiang, Hattori, \& Trichtinger, 2019), \emph{forcats} (Version 0.5.0; Wickham, 2020), \emph{foreign} (Version 0.8.80; R Core Team, 2020a), \emph{ggplot2} (Version 3.3.2; Wickham, 2016), \emph{haven} (Version 2.3.1; Wickham \& Miller, 2020), \emph{janitor} (Version 2.0.1; Firke, 2020), \emph{knitr} (Version 1.29; Xie, 2015), \emph{lattice} (Version 0.20.41; Sarkar, 2008), \emph{lme4} (Version 1.1.23; Bates, Mächler, Bolker, \& Walker, 2015), \emph{lmerTest} (Version 3.1.2; Kuznetsova, Brockhoff, \& Christensen, 2017), \emph{lubridate} (Version 1.7.9; Grolemund \& Wickham, 2011), \emph{Matrix} (Version 1.2.18; Bates \& Maechler, 2019), \emph{papaja} (Version 0.1.0.9997; Aust \& Barth, 2020), \emph{plm} (Version 2.2.3; Croissant \& Millo, 2008; Millo, 2017), \emph{plot3D} (Version 1.3; Soetaert, 2019), \emph{preprocessCore} (Version 1.50.0; Bolstad, 2020), \emph{psych} (Version 1.9.12.31; Revelle, 2019), \emph{purrr} (Version 0.3.4; Henry \& Wickham, 2020), \emph{readr} (Version 1.3.1; Wickham, Hester, \& Francois, 2018), \emph{readxl} (Version 1.3.1; Wickham \& Bryan, 2019), \emph{reshape2} (Version 1.4.4; Wickham, 2007), \emph{rio} (Version 0.5.16; Chan, Chan, Leeper, \& Becker, 2018), \emph{sjPlot} (Version 2.8.4; Lüdecke, 2020), \emph{stringr} (Version 1.4.0; Wickham, 2019), \emph{tibble} (Version 3.0.3; Müller \& Wickham, 2020), \emph{tidyr} (Version 1.1.0; Wickham \& Henry, 2020), \emph{tidyverse} (Version 1.3.0; Wickham, Averick, et al., 2019), and \emph{XLConnect} (Version 1.0.1; Mirai Solutions GmbH, 2020) for all our analyses.
 
@@
 
+\#\#Control variables
+
+\#\#Constrcuting human capital index (control variable)
+\#\#\#Graduate percentage, Prior C-level Executive Percentage, Average Team Tenure , Team Prior Founding
+
+\#\#Gender decomposition variable
+
 \#Reverse code attention variable
 
-\#Join all 3 datasets
+\#Distribution of attention
 
-\#Fiancial Capital acquisiton total
+\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-6-1.pdf} \includegraphics{Manuscript_files/figure-latex/unnamed-chunk-6-2.pdf}
+
+\#\#Outcomes
 
@@
 \#Social capital acquisition
+
+\#Fiancial Capital acquisiton total
+
+\#Predictor and outcome plots
+\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-11-1.pdf} \includegraphics{Manuscript_files/figure-latex/unnamed-chunk-11-2.pdf}
+
+\#Join all 3 datasets
 
@@
 \hline
-  & \$b\$ & SE & \$z\$\\
+  & $b$ & SE & $z$\\
 \hline
-Intercept & -1.47 & 0.08 & -19.16\\
+Intercept & -1.46 & 0.08 & -19.18\\
 \hline
-Attention to Human capital(AHC) & 0.10 & 0.08 & 1.24\\
+Attention to Human capital(AHC) & 0.11 & 0.07 & 1.54\\
 \hline
@@
 \hline
-  & \$b\$ & SE & \$z\$\\
+  & $b$ & SE & $z$\\
 \hline
-Intercept & -0.94 & 0.53 & -1.77\\
+Intercept & -0.85 & 0.53 & -1.61\\
 \hline
-AHC & 0.86 & 0.44 & 1.97\\
+AHC & 0.92 & 0.45 & 2.05\\
 \hline
-Ease of finding skilled employees & -0.12 & 0.12 & -0.96\\
+Ease of finding skilled employees & -0.14 & 0.12 & -1.14\\
 \hline
-AHCxEase of finding skilled employees & -0.16 & 0.09 & -1.69\\
+AHCxEase of finding skilled employees & -0.17 & 0.10 & -1.79\\
 \hline
@@
 \hline
-  & \$b\$ & SE & \$t\$\\
+  & $b$ & SE & $t$\\
 \hline
-Intercept & 738.20 & 485.65 & 1.52\\
+Intercept & 762.25 & 502.25 & 1.52\\
 \hline
-Attention to Human capital & 2,841.44 & 2,153.75 & 1.32\\
+Attention to Human capital & 2,955.97 & 2,238.11 & 1.32\\
 \hline
@@
 \hline
-  & \$b\$ & SE & \$t\$\\
+  & $b$ & SE & $t$\\
 \hline
-Intercept & -1,882.79 & 3,470.12 & -0.54\\
+Intercept & -1,955.91 & 3,599.05 & -0.54\\
 \hline
-AHC & -9,744.87 & 16,027.75 & -0.61\\
+AHC & -10,174.65 & 16,704.03 & -0.61\\
 \hline
-Ease of finding skilled employees & 618.05 & 783.89 & 0.79\\
+Ease of finding skilled employees & 641.03 & 813.08 & 0.79\\
 \hline
-AHCxEase of finding skilled employees & 2,989.85 & 3,687.09 & 0.81\\
+AHCxEase of finding skilled employees & 3,118.93 & 3,842.90 & 0.81\\
 \hline
@@
 \begin{verbatim}
-## Linear mixed model fit by maximum likelihood  ['lmerMod']
-## Formula: participated ~ +(accel_ben_rank_direct_funding | country)
+## Generalized linear mixed model fit by maximum likelihood (Laplace
+##   Approximation) [glmerMod]
+##  Family: binomial  ( logit )
+## Formula: 
+## participated ~ accel_ben_rank_direct_funding + (accel_ben_rank_direct_funding |  
+##     country)
 ##    Data: gali_joined
@@
 ##      AIC      BIC   logLik deviance df.resid 
-##  14831.2  14869.8  -7410.6  14821.2    16439 
+##  14773.7  14812.1  -7381.8  14763.7    15976 
 ## 
@@
 ##     Min      1Q  Median      3Q     Max 
-## -1.3463 -0.5096 -0.4046 -0.2890  2.4564 
+## -1.0388 -0.4890 -0.4207 -0.3515  3.0479 
 ## 
@@
 ##  Groups  Name                          Variance Std.Dev. Corr 
-##  country  (Intercept)                   0.008936 0.09453       
-##           accel_ben_rank_direct_funding 0.001665 0.04080  -0.49
-##  Residual                               0.142950 0.37809       
-## Number of obs: 16444, groups:  country, 83
+##  country (Intercept)                   0.300861 0.54851       
+##          accel_ben_rank_direct_funding 0.007982 0.08934  -1.00
+## Number of obs: 15981, groups:  country, 82
 ## 
 ## Fixed effects:
-##             Estimate Std. Error t value
-## (Intercept)  0.19651    0.01228   16.01
+##                               Estimate Std. Error z value Pr(>|z|)    
+## (Intercept)                   -1.45326    0.07722 -18.821  < 2e-16 ***
+## accel_ben_rank_direct_funding -0.19333    0.06321  -3.059  0.00222 ** 
+## ---
+## Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
+## 
+## Correlation of Fixed Effects:
+##             (Intr)
+## accl_bn_r__ -0.171
+## convergence code: 0
+## boundary (singular) fit: see ?isSingular
 \end{verbatim}
@@
 \begin{verbatim}
-## Linear mixed model fit by maximum likelihood  ['lmerMod']
+## Generalized linear mixed model fit by maximum likelihood (Laplace
+##   Approximation) [glmerMod]
+##  Family: binomial  ( logit )
 ## Formula: 
@@
 ##      AIC      BIC   logLik deviance df.resid 
-##  14620.0  14681.5  -7302.0  14604.0    16177 
+##  14562.1  14615.8  -7274.1  14548.1    15720 
 ## 
@@
 ##     Min      1Q  Median      3Q     Max 
-## -1.4017 -0.5138 -0.3955 -0.2813  2.4249 
+## -1.0463 -0.4908 -0.4210 -0.3513  3.0165 
 ## 
@@
 ##  Groups  Name                          Variance Std.Dev. Corr 
-##  country  (Intercept)                   0.0085583 0.09251       
-##           accel_ben_rank_direct_funding 0.0009436 0.03072  -1.00
-##  Residual                               0.1432556 0.37849       
-## Number of obs: 16185, groups:  country, 74
+##  country (Intercept)                   0.287438 0.53613       
+##          accel_ben_rank_direct_funding 0.009936 0.09968  -1.00
+## Number of obs: 15727, groups:  country, 73
 ## 
 ## Fixed effects:
-##                                         Estimate Std. Error t value
-## (Intercept)                            0.2004428  0.0710787   2.820
-## accel_ben_rank_direct_funding         -0.0255510  0.0455072  -0.561
-## EOSQ425                                0.0008104  0.0184340   0.044
-## accel_ben_rank_direct_funding:EOSQ425 -0.0023544  0.0107909  -0.218
+##                                        Estimate Std. Error z value Pr(>|z|)   
+## (Intercept)                           -1.349694   0.434021  -3.110  0.00187 **
+## accel_ben_rank_direct_funding         -0.210801   0.285396  -0.739  0.46013   
+## EOSQ425                               -0.021755   0.112408  -0.194  0.84654   
+## accel_ben_rank_direct_funding:EOSQ425  0.003382   0.065751   0.051  0.95898   
+## ---
+## Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
 ## 
@@
 ##             (Intr) ac____ EOSQ42
-## accl_bn_r__ -0.490              
-## EOSQ425     -0.984  0.485       
-## a____:EOSQ4  0.533 -0.975 -0.545
+## accl_bn_r__ -0.246              
+## EOSQ425     -0.983  0.246       
+## a____:EOSQ4  0.280 -0.974 -0.289
 ## convergence code: 0
@@
 ##      AIC      BIC   logLik deviance df.resid 
-##  14619.7  14681.2  -7301.8  14603.7    16177 
+##  14561.6  14615.2  -7273.8  14547.6    15720 
 ## 
@@
 ##     Min      1Q  Median      3Q     Max 
-## -1.4020 -0.5136 -0.3962 -0.2810  2.4270 
+## -1.0482 -0.4904 -0.4209 -0.3510  3.0323 
 ## 
@@
 ##  Groups  Name                          Variance Std.Dev. Corr 
-##  country  (Intercept)                   0.0084870 0.09212       
-##           accel_ben_rank_direct_funding 0.0009291 0.03048  -1.00
-##  Residual                               0.1432565 0.37849       
-## Number of obs: 16185, groups:  country, 74
+##  country (Intercept)                   0.284084 0.53299       
+##          accel_ben_rank_direct_funding 0.009676 0.09837  -1.00
+## Number of obs: 15727, groups:  country, 73
 ## 
 ## Fixed effects:
-##                                        Estimate Std. Error t value
-## (Intercept)                            0.229561   0.046331   4.955
-## accel_ben_rank_direct_funding         -0.037525   0.030596  -1.226
-## EOSQ089                               -0.008695   0.014873  -0.585
-## accel_ben_rank_direct_funding:EOSQ089  0.001088   0.008465   0.129
+##                                       Estimate Std. Error z value Pr(>|z|)    
+## (Intercept)                           -1.21998    0.28033  -4.352 1.35e-05 ***
+## accel_ben_rank_direct_funding         -0.24283    0.19650  -1.236    0.217    
+## EOSQ089                               -0.07084    0.09006  -0.787    0.432    
+## accel_ben_rank_direct_funding:EOSQ089  0.01463    0.05184   0.282    0.778    
+## ---
+## Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
 ## 
@@
 ##             (Intr) ac____ EOSQ08
-## accl_bn_r__ -0.477              
-## EOSQ089     -0.961  0.464       
-## a____:EOSQ0  0.539 -0.944 -0.566
+## accl_bn_r__ -0.232              
+## EOSQ089     -0.960  0.230       
+## a____:EOSQ0  0.281 -0.944 -0.300
 ## convergence code: 0
@@
 \begin{verbatim}
-## Linear mixed model fit by maximum likelihood  ['lmerMod']
+## Generalized linear mixed model fit by maximum likelihood (Laplace
+##   Approximation) [glmerMod]
+##  Family: binomial  ( logit )
 ## Formula: participated ~ accel_ben_rank_direct_funding * DOMCREDITGDP +  
@@
 ##      AIC      BIC   logLik deviance df.resid 
-##  14619.7  14681.2  -7301.8  14603.7    16177 
+##  14561.8  14615.5  -7273.9  14547.8    15720 
 ## 
@@
 ##     Min      1Q  Median      3Q     Max 
-## -1.3992 -0.5115 -0.3980 -0.2807  2.4272 
+## -1.0466 -0.4909 -0.4213 -0.3514  3.0629 
 ## 
@@
 ##  Groups  Name                          Variance Std.Dev. Corr 
-##  country  (Intercept)                   0.0085682 0.09256       
-##           accel_ben_rank_direct_funding 0.0009053 0.03009  -1.00
-##  Residual                               0.1432523 0.37849       
-## Number of obs: 16185, groups:  country, 74
+##  country (Intercept)                   0.289392 0.53795       
+##          accel_ben_rank_direct_funding 0.009926 0.09963  -1.00
+## Number of obs: 15727, groups:  country, 73
 ## 
 ## Fixed effects:
-##                                              Estimate Std. Error t value
-## (Intercept)                                 2.113e-01  2.084e-02  10.137
-## accel_ben_rank_direct_funding              -3.313e-02  1.549e-02  -2.139
-## DOMCREDITGDP                               -1.339e-04  2.829e-04  -0.473
-## accel_ben_rank_direct_funding:DOMCREDITGDP -1.288e-05  1.590e-04  -0.081
+##                                              Estimate Std. Error z value
+## (Intercept)                                -1.3735020  0.1256629 -10.930
+## accel_ben_rank_direct_funding              -0.2051438  0.1031016  -1.990
+## DOMCREDITGDP                               -0.0010317  0.0017273  -0.597
+## accel_ben_rank_direct_funding:DOMCREDITGDP  0.0001439  0.0009667   0.149
+##                                            Pr(>|z|)    
+## (Intercept)                                  <2e-16 ***
+## accel_ben_rank_direct_funding                0.0466 *  
+## DOMCREDITGDP                                 0.5503    
+## accel_ben_rank_direct_funding:DOMCREDITGDP   0.8817    
+## ---
+## Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
 ## 
@@
 ##             (Intr) ac____ DOMCRE
-## accl_bn_r__ -0.414              
-## DOMCREDITGD -0.788  0.334       
-## a____:DOMCR  0.441 -0.768 -0.567
+## accl_bn_r__ -0.193              
+## DOMCREDITGD -0.778  0.159       
+## a____:DOMCR  0.233 -0.779 -0.313
 ## convergence code: 0
@@
 ##       AIC       BIC    logLik  deviance  df.resid 
-##  628881.3  628919.9 -314435.7  628871.3     16439 
+##  541645.1  541683.5 -270817.5  541635.1     15976 
 ## 
@@
 ##     Min      1Q  Median      3Q     Max 
-##  -0.756  -0.010  -0.008  -0.004 126.757 
+##  -0.316  -0.040  -0.029  -0.018 120.803 
 ## 
@@
 ##  Groups   Name                          Variance  Std.Dev. Corr
-##  country  (Intercept)                   1.168e+13  3417674      
-##           accel_ben_rank_direct_funding 4.366e+13  6607224 -1.00
-##  Residual                               2.373e+15 48709324      
-## Number of obs: 16444, groups:  country, 83
+##  country  (Intercept)                   1.187e+11  344600      
+##           accel_ben_rank_direct_funding 2.332e+09   48286  1.00
+##  Residual                               3.062e+13 5533830      
+## Number of obs: 15981, groups:  country, 82
 ## 
@@
 ##             Estimate Std. Error t value
-## (Intercept)   607877     562167   1.081
+## (Intercept)   226024      79869    2.83
 ## convergence code: 0
@@
 ##       AIC       BIC    logLik  deviance  df.resid 
-##  619237.1  619298.6 -309610.6  619221.1     16177 
+##  533280.8  533342.1 -266632.4  533264.8     15719 
 ## 
@@
 ##     Min      1Q  Median      3Q     Max 
-##  -0.770  -0.009  -0.006  -0.004 125.749 
+##  -0.311  -0.041  -0.028  -0.016 119.888 
 ## 
@@
 ##  Groups   Name                          Variance  Std.Dev. Corr
-##  country  (Intercept)                   1.205e+13  3471900      
-##           accel_ben_rank_direct_funding 4.540e+13  6737688 -1.00
-##  Residual                               2.410e+15 49094901      
-## Number of obs: 16185, groups:  country, 74
+##  country  (Intercept)                   1.247e+11  353102      
+##           accel_ben_rank_direct_funding 2.606e+09   51053  1.00
+##  Residual                               3.109e+13 5575911      
+## Number of obs: 15727, groups:  country, 73
 ## 
@@
 ##                                       Estimate Std. Error t value
-## (Intercept)                            3278060    3931054   0.834
-## accel_ben_rank_direct_funding         -5097275    8516455  -0.599
-## EOSQ425                                -589495    1003353  -0.588
-## accel_ben_rank_direct_funding:EOSQ425   972897    2131244   0.456
+## (Intercept)                              -4885     444377  -0.011
+## accel_ben_rank_direct_funding          -191024     590675  -0.323
+## EOSQ425                                  59478     112868   0.527
+## accel_ben_rank_direct_funding:EOSQ425    31388     134942   0.233
 ## 
@@
 ##             (Intr) ac____ EOSQ42
-## accl_bn_r__ -0.717              
-## EOSQ425     -0.982  0.725       
-## a____:EOSQ4  0.740 -0.980 -0.771
+## accl_bn_r__  0.106              
+## EOSQ425     -0.982 -0.103       
+## a____:EOSQ4 -0.111 -0.975  0.111
 ## convergence code: 0
@@
 ##       AIC       BIC    logLik  deviance  df.resid 
-##  619236.9  619298.5 -309610.5  619220.9     16177 
+##  533280.7  533342.0 -266632.3  533264.7     15719 
 ## 
@@
 ##     Min      1Q  Median      3Q     Max 
-##  -0.771  -0.009  -0.006  -0.004 125.749 
+##  -0.310  -0.041  -0.028  -0.015 119.888 
 ## 
@@
 ##  Groups   Name                          Variance  Std.Dev. Corr
-##  country  (Intercept)                   1.196e+13  3458659      
-##           accel_ben_rank_direct_funding 4.502e+13  6709707 -1.00
-##  Residual                               2.410e+15 49094926      
-## Number of obs: 16185, groups:  country, 74
+##  country  (Intercept)                   1.245e+11  352894      
+##           accel_ben_rank_direct_funding 2.412e+09   49109  1.00
+##  Residual                               3.109e+13 5575889      
+## Number of obs: 15727, groups:  country, 73
 ## 
@@
 ##                                       Estimate Std. Error t value
-## (Intercept)                            2758748    2542379   1.085
-## accel_ben_rank_direct_funding         -4463383    5575404  -0.801
-## EOSQ089                                -575121     797830  -0.721
-## accel_ben_rank_direct_funding:EOSQ089  1016469    1690294   0.601
+## (Intercept)                              66014     285162   0.231
+## accel_ben_rank_direct_funding          -205433     401458  -0.512
+## EOSQ089                                  51858      88843   0.584
+## accel_ben_rank_direct_funding:EOSQ089    41162     104375   0.394
 ## 
@@
 ##             (Intr) ac____ EOSQ08
-## accl_bn_r__ -0.700              
-## EOSQ089     -0.957  0.703       
-## a____:EOSQ0  0.729 -0.952 -0.787
+## accl_bn_r__  0.083              
+## EOSQ089     -0.957 -0.080       
+## a____:EOSQ0 -0.094 -0.944  0.098
 ## convergence code: 0
@@
 ##       AIC       BIC    logLik  deviance  df.resid 
-##  619237.2  619298.7 -309610.6  619221.2     16177 
+##  533280.9  533342.2 -266632.4  533264.9     15719 
 ## 
@@
 ##     Min      1Q  Median      3Q     Max 
-##  -0.770  -0.007  -0.006  -0.004 125.749 
+##  -0.310  -0.041  -0.028  -0.016 119.887 
 ## 
@@
 ##  Groups   Name                          Variance  Std.Dev. Corr
-##  country  (Intercept)                   1.208e+13  3475044      
-##           accel_ben_rank_direct_funding 4.521e+13  6724103 -1.00
-##  Residual                               2.410e+15 49095018      
-## Number of obs: 16185, groups:  country, 74
+##  country  (Intercept)                   1.245e+11  352820      
+##           accel_ben_rank_direct_funding 2.381e+09   48795  1.00
+##  Residual                               3.109e+13 5575926      
+## Number of obs: 15727, groups:  country, 73
 ## 
@@
 ##                                             Estimate Std. Error t value
-## (Intercept)                                 1451825    1141899   1.271
-## accel_ben_rank_direct_funding              -2232392    2605340  -0.857
-## DOMCREDITGDP                                  -7480      14628  -0.511
-## accel_ben_rank_direct_funding:DOMCREDITGDP    13756      31129   0.442
+## (Intercept)                                 190993.0   128015.3   1.492
+## accel_ben_rank_direct_funding              -121351.9   210078.0  -0.578
+## DOMCREDITGDP                                   572.9     1620.3   0.354
+## accel_ben_rank_direct_funding:DOMCREDITGDP     768.4     1952.7   0.393
 ## 
@@
 ##             (Intr) ac____ DOMCRE
-## accl_bn_r__ -0.615              
-## DOMCREDITGD -0.764  0.519       
-## a____:DOMCR  0.555 -0.760 -0.779
+## accl_bn_r__  0.058              
+## DOMCREDITGD -0.761 -0.043       
+## a____:DOMCR -0.062 -0.776  0.085
 ## convergence code: 0
@@
 ##                          Estimate  Std. Error   t value
-## (Intercept)            0.20204321 0.01250494 16.157077
-## accel_ben_rank_network 0.01914256 0.00950974  2.012943
+## (Intercept)            0.20316446 0.012552069 16.185735
+## accel_ben_rank_network 0.01831386 0.009581619  1.911353
 \end{verbatim}
@@
 ##                                     Estimate Std. Error      t value
-## (Intercept)                     0.295903338 0.06852242  4.3183434
-## accel_ben_rank_network          0.023874383 0.05035733  0.4740994
-## EOSQ109                        -0.023521692 0.01733603 -1.3568099
-## accel_ben_rank_network:EOSQ109 -0.001363126 0.01125294 -0.1211352
+## (Intercept)                     3.133837e-01 0.06847055  4.576912615
+## accel_ben_rank_network          1.746818e-02 0.05079577  0.343890367
+## EOSQ109                        -2.763492e-02 0.01732516 -1.595074599
+## accel_ben_rank_network:EOSQ109 -4.430267e-05 0.01131854 -0.003914168
 \end{verbatim}
@@
 ##                          Estimate Std. Error   t value
-## (Intercept)            0.57431349 0.04229280 13.579463
-## accel_ben_rank_network 0.06431639 0.04574601  1.405945
+## (Intercept)            0.57925930 0.04337800 13.353759
+## accel_ben_rank_network 0.06485941 0.04797524  1.351935
 \end{verbatim}
@@
 ##                                  Estimate Std. Error   t value
-## (Intercept)                    -0.2693634 0.20697678 -1.301419
-## accel_ben_rank_network         -0.5635796 0.23434531 -2.404911
-## EOSQ109                         0.2155408 0.05213442  4.134328
-## accel_ben_rank_network:EOSQ109  0.1600702 0.05499693  2.910531
+## (Intercept)                    -0.2751093 0.21194630 -1.298014
+## accel_ben_rank_network         -0.6038282 0.24619417 -2.452650
+## EOSQ109                         0.2185398 0.05339006  4.093266
+## accel_ben_rank_network:EOSQ109  0.1708510 0.05804559  2.943393
 \end{verbatim}
+
+\hypertarget{data-and-methods}{%
+\section{Data and Methods}\label{data-and-methods}}
+
+Our dataset, the Global Accelerator Learning Initiative (GALI), covers entrepreneurs who applied to scores of accelerators that began accepting applications between 2013 and 2020.
+Our data include information -- collected during program applications -- about ventures, founding teams, and pre-program performance.
+They also identify which applicants went on to participate in each program.
+Finally, these data include follow-up information collected from selected and rejected applicants in the years following each application window.
+The anonymized dataset containing both application and follow-up data can be accessed at \href{www.galidata.org/data-request}{GALI Data}.
+
+When entrepreneurs apply to a GALI-participating accelerator, they are asked to complete a standardized survey which asks basic questions about their venture's business model, financial performance, and founding team.
+Then, after one year, they are asked to complete a follow-up survey, whether or not they were accepted into the program to which they applied.
+
+All financial statistics are in United States Dollars (USD).
+
+Table 1: Ventures in sample, by country of operation and survey responses
 
@@
 
+\leavevmode\hypertarget{ref-R-preprocessCore}{}%
+Bolstad, B. (2020). \emph{PreprocessCore: A collection of pre-processing functions}. Retrieved from \url{https://github.com/bmbolstad/preprocessCore}
+
+\leavevmode\hypertarget{ref-R-rio}{}%
+Chan, C.-h., Chan, G. C., Leeper, T. J., \& Becker, J. (2018). \emph{Rio: A swiss-army knife for data file i/o}.
+
+\leavevmode\hypertarget{ref-R-plm_a}{}%
+Croissant, Y., \& Millo, G. (2008). Panel data econometrics in R: The plm package. \emph{Journal of Statistical Software}, \emph{27}(2), 1--43. \url{https://doi.org/10.18637/jss.v027.i02}
+
+\leavevmode\hypertarget{ref-R-janitor}{}%
+Firke, S. (2020). \emph{Janitor: Simple tools for examining and cleaning dirty data}. Retrieved from \url{https://CRAN.R-project.org/package=janitor}
+
+\leavevmode\hypertarget{ref-R-lubridate}{}%
+Grolemund, G., \& Wickham, H. (2011). Dates and times made easy with lubridate. \emph{Journal of Statistical Software}, \emph{40}(3), 1--25. Retrieved from \url{http://www.jstatsoft.org/v40/i03/}
+
+\leavevmode\hypertarget{ref-R-purrr}{}%
+Henry, L., \& Wickham, H. (2020). \emph{Purrr: Functional programming tools}. Retrieved from \url{https://CRAN.R-project.org/package=purrr}
+
+\leavevmode\hypertarget{ref-hochberg2007whom}{}%
+Hochberg, Y. V., Ljungqvist, A., \& Lu, Y. (2007). Whom you know matters: Venture capital networks and investment performance. \emph{The Journal of Finance}, \emph{62}(1), 251--301.
+
+\leavevmode\hypertarget{ref-holburn2010political}{}%
+Holburn, G.
+L., \& Zelner, B.
+A.
+(2010).
+Political capabilities, policy risk, and international investment strategy: Evidence from the global electric power generation industry.
+\emph{Strategic Management Journal}, \emph{31}(12), 1290--1315.
+
+\leavevmode\hypertarget{ref-khanna1997focused}{}%
+Khanna, T., \& Palepu, K. (1997). Why focused strategies may be wrong for emerging markets. \emph{Harvard Business Review}, \emph{75}, 41--54.
+
+\leavevmode\hypertarget{ref-khanna2001estimating}{}%
+Khanna, T., \& Rivkin, J. W. (2001). Estimating the performance effects of business groups in emerging markets. \emph{Strategic Management Journal}, \emph{22}(1), 45--74.
+
+\leavevmode\hypertarget{ref-kock2001strategy}{}%
+Kock, C.
+J., \& Guillén, M.
+F.
+(2001).
+Strategy and structure in developing countries: Business groups as an evolutionary response to opportunities for unrelated diversification.
+\emph{Industrial and Corporate Change}, \emph{10}(1), 77--113.
+
+\leavevmode\hypertarget{ref-R-caret}{}%
+Kuhn, M. (2020). \emph{Caret: Classification and regression training}. Retrieved from \url{https://CRAN.R-project.org/package=caret}
+
+\leavevmode\hypertarget{ref-R-lmerTest}{}%
+Kuznetsova, A., Brockhoff, P.
+B., \& Christensen, R.
+H.
+B.
+(2017).
+lmerTest package: Tests in linear mixed effects models.
+\emph{Journal of Statistical Software}, \emph{82}(13), 1--26.
+\url{https://doi.org/10.18637/jss.v082.i13}
+
+\leavevmode\hypertarget{ref-R-sjPlot}{}%
+Lüdecke, D. (2020). \emph{SjPlot: Data visualization for statistics in social science}. Retrieved from \url{https://CRAN.R-project.org/package=sjPlot}
+
+\leavevmode\hypertarget{ref-R-plm_b}{}%
+Millo, G. (2017). Robust standard error estimators for panel models: A unifying approach. \emph{Journal of Statistical Software}, \emph{82}(3), 1--27. \url{https://doi.org/10.18637/jss.v082.i03}
+
+\leavevmode\hypertarget{ref-R-XLConnect}{}%
+Mirai Solutions GmbH. (2020). \emph{XLConnect: Excel connector for r}. Retrieved from \url{https://CRAN.R-project.org/package=XLConnect}
+
+\leavevmode\hypertarget{ref-R-tibble}{}%
+Müller, K., \& Wickham, H. (2020). \emph{Tibble: Simple data frames}. Retrieved from \url{https://CRAN.R-project.org/package=tibble}
+
+\leavevmode\hypertarget{ref-north1990institutions}{}%
+North, D. C., \& others. (1990). \emph{Institutions, institutional change and economic performance}. Cambridge university press.
+
+\leavevmode\hypertarget{ref-R-foreign}{}%
+R Core Team. (2020a). \emph{Foreign: Read data stored by 'minitab', 's', 'sas', 'spss', 'stata', 'systat', 'weka', 'dBase', ...} Retrieved from \url{https://CRAN.R-project.org/package=foreign}
+
 \leavevmode\hypertarget{ref-R-base}{}%
-R Core Team. (2020). \emph{R: A language and environment for statistical computing}. Vienna, Austria: R Foundation for Statistical Computing. Retrieved from \url{https://www.R-project.org/}
+R Core Team. (2020b). \emph{R: A language and environment for statistical computing}. Vienna, Austria: R Foundation for Statistical Computing. Retrieved from \url{https://www.R-project.org/}
+
+\leavevmode\hypertarget{ref-R-psych}{}%
+Revelle, W.
+(2019).
+\emph{Psych: Procedures for psychological, psychometric, and personality research}.
+Evanston, Illinois: Northwestern University.
+Retrieved from \url{https://CRAN.R-project.org/package=psych}
+
+\leavevmode\hypertarget{ref-R-lattice}{}%
+Sarkar, D. (2008). \emph{Lattice: Multivariate data visualization with r}. New York: Springer. Retrieved from \url{http://lmdvr.r-forge.r-project.org}
+
+\leavevmode\hypertarget{ref-shane2002organizational}{}%
+Shane, S., \& Stuart, T. (2002). Organizational endowments and the performance of university start-ups. \emph{Management Science}, \emph{48}(1), 154--170.
+
+\leavevmode\hypertarget{ref-simon1947comment}{}%
+Simon, H. A. (1947). A comment on" the science of public administration". \emph{Public Administration Review}, \emph{7}(3), 200--203.
+
+\leavevmode\hypertarget{ref-R-plot3D}{}%
+Soetaert, K. (2019). \emph{Plot3D: Plotting multi-dimensional data}. Retrieved from \url{https://CRAN.R-project.org/package=plot3D}
+
+\leavevmode\hypertarget{ref-R-reshape2}{}%
+Wickham, H. (2007). Reshaping data with the reshape package. \emph{Journal of Statistical Software}, \emph{21}(12), 1--20. Retrieved from \url{http://www.jstatsoft.org/v21/i12/}
+
+\leavevmode\hypertarget{ref-R-ggplot2}{}%
+Wickham, H. (2016). \emph{Ggplot2: Elegant graphics for data analysis}. Springer-Verlag New York. Retrieved from \url{https://ggplot2.tidyverse.org}
+
+\leavevmode\hypertarget{ref-R-stringr}{}%
+Wickham, H. (2019). \emph{Stringr: Simple, consistent wrappers for common string operations}. Retrieved from \url{https://CRAN.R-project.org/package=stringr}
+
+\leavevmode\hypertarget{ref-R-forcats}{}%
+Wickham, H. (2020). \emph{Forcats: Tools for working with categorical variables (factors)}. Retrieved from \url{https://CRAN.R-project.org/package=forcats}
+
+\leavevmode\hypertarget{ref-R-tidyverse}{}%
+Wickham, H., Averick, M., Bryan, J., Chang, W., McGowan, L.
+D., François, R., \ldots{} Yutani, H.
+(2019).
+Welcome to the tidyverse.
+\emph{Journal of Open Source Software}, \emph{4}(43), 1686.
+\url{https://doi.org/10.21105/joss.01686}
+
+\leavevmode\hypertarget{ref-R-readxl}{}%
+Wickham, H., \& Bryan, J. (2019). \emph{Readxl: Read excel files}. Retrieved from \url{https://CRAN.R-project.org/package=readxl}
+
+\leavevmode\hypertarget{ref-R-dplyr}{}%
+Wickham, H., François, R., Henry, L., \& Müller, K. (2020). \emph{Dplyr: A grammar of data manipulation}. Retrieved from \url{https://CRAN.R-project.org/package=dplyr}
+
+\leavevmode\hypertarget{ref-R-tidyr}{}%
+Wickham, H., \& Henry, L. (2020). \emph{Tidyr: Tidy messy data}. Retrieved from \url{https://CRAN.R-project.org/package=tidyr}
+
+\leavevmode\hypertarget{ref-R-readr}{}%
+Wickham, H., Hester, J., \& Francois, R. (2018). \emph{Readr: Read rectangular text data}. Retrieved from \url{https://CRAN.R-project.org/package=readr}
+
+\leavevmode\hypertarget{ref-R-haven}{}%
+Wickham, H., \& Miller, E. (2020). \emph{Haven: Import and export 'spss', 'stata' and 'sas' files}. Retrieved from \url{https://CRAN.R-project.org/package=haven}
+
+\leavevmode\hypertarget{ref-R-knitr}{}%
+Xie, Y. (2015). \emph{Dynamic documents with R and knitr} (2nd ed.). Boca Raton, Florida: Chapman; Hall/CRC. Retrieved from \url{https://yihui.org/knitr/}
+
+\leavevmode\hypertarget{ref-R-EFAutilities}{}%
+Zhang, G., Jiang, G., Hattori, M., \& Trichtinger, L.
+(2019).
+\emph{EFAutilities: Utility functions for exploratory factor analysis}.
+Retrieved from \url{https://CRAN.R-project.org/package=EFAutilities}
 

### 2021-03-10 Manuscript.Rmd
manuscript development

@@
 library("papaja")
+#install.packages("tinytex")
+#tinytex::install_tinytex()
 r_refs("r-references.bib")
@@
 *Predictors*
+**Venture attention to a resource** A common approach to measure attention allocation is to use the revealed preference of individuals to evaluate the attention structure [@gebauer2009attention].
+I use the entrepreneurs’ ranked preference of the desired benefits from accelerator programs as a proxy for the attention allocation of the early-stage ventures to various resources.
+The GALI questionnaire asks applying entrepreneurs to rank seven acceleration benefits by perceived importance to their ventures.
+The seven benefits are network development (Network), e.g.
+with potential partners and customers, business skill development (Business Skills), mentorship from business experts (Mentorship), indirect funding through access to potential investors/funders (Access to Investors), securing direct venture funding (Direct Funding), gaining access to a group of like-minded entrepreneurs (Access to Like-minded Entrepreneurs), and awareness and credibility (Awareness and Credibility).
+Setting aside Awareness and Credibility and Access to Like-minded Entrepreneurs, the remaining five benefits can be categorized into three types of resources.
+Mentorship and Business Skills represent the development of human capital.
+Network help develop social capital.
+Direct Funding and Access to Investors improve the financial capital of early-stage ventures directly or indirectly.
+
+Respondents are asked to rank the seven benefits on a scale from one to seven, with one being the most important and seven being the least important.
+These rankings were reverse-coded to facilitate interpretation of the effects in order of increased importance, with 1 being the least important and 7 the most important.
+The benefits that accelerators provide consistently ranked in the top three were network development, business skills development, and securing direct venture funding.
+I assume that the early-stage ventures’ attention allocation reflects the rankings given in their questionnaires.
+The questionnaire enforces a rule that respondents need to enter a ranking for all seven benefits and no tie is allowed.
+I exclude observations that do not have complete ranking of the seven items or because they have ties in the rankings.
+
+**Institutional level capital** To measure the level of capital of a certain resource at the country level, I used data from the World Economic Forum Global Competitiveness Index (GCI).
+Specificaly, I used the variable State of cluster development as a measure for institutional level social capital; Ease of finding skilled employees as a measure for institutional level human capital; and Venture capital availability, Financing of Small and Medium Enterprises, Domestic Credit Gaps as different measures of institutional level financial capital.
+While former measures of fiancial capital are self-explanatory, the latter variable is defined loans, purchases of non-equity securities, and trade credits and other accounts receivable provided to the private sector by financial corporations as a percentage of gross domestic products (GDP).
+
 *Outcomes*
+**Resource mobilization** is coded as a dichotomous measure *Participated* equal to one
+if an applicant participate to an accelerator program of choice, and zero otherwise.
+I assume that pariticipating to an acceleration program is the first step to mobiliza all types of resources provided by the accelerator.
+
+**Resource acquisition** once participants mobilize resources through participation to an accelerator, they engage in acquiring resources that garner their attention.
+These resources can translate into (a) raising capital from one source or many sources depending on (b) the entrepreneurs social capital (i.e.
+Network) or (c) hiring employees.
+(a), (b), and (c) are all resource acquisition outcomes.
+
+**Performance** finaly to measure the impact on venture performance, I use the variable *Revenue* as a proxy for this outcome.
+This is the most commonly used performance indicator in the management in strategy litrature.
+
 *Control Variables*
@@
 
-**Gender Decomposition**
+**Gender composition** the proportion female co-founders in each venture team.
 
@@
 The anonymized dataset containing both application and follow-up data can be accessed at [GALI Data](www.galidata.org/data-request).
-
-This is multi-country dataset. It typically contain hundreds of ventures per country.
+This is multi-country dataset.
+It typically contains hundreds of ventures per country.
 
@@
 
+I set aside XXX nonprofit organizations and XXX observations that are missing relevant venture information or preference ranking, resulting in xxx observations in the final sample.
 All financial statistics are in United States Dollars (USD).
-
-Table 1: Ventures in sample, by country of operation and survey responses
+********
 
@@
 country) effect on venture outcomes and quantify the extent to which differences in outcomes reflect differences in the effects of country-specific features, specifically institutional level capital.
-
-yic=Xicβ+Zcγ+uc+εic,  withi=1,…,Nc;c=1,…,C.
-
-Outcome y ic for each person i in country c is assumed to depend on observed predictors and unobserved factors.
-Xic contains variables that summarize individual-level characteristics such as age, education, or marital status; Zc contains variables summarizing country-level features such as socio-economic institutions or labour markets.
-There are also unobserved individual effects ( ε ic ) and country effects ( u c ), each assumed to be normally distributed and uncorrelated with Xic and Zc .
-We suppose the researcher has available a data set with a large number of individuals for each country ( N c is typically in the thousands) sampled from each of a small number of countries ( C is typically less than 30).
-The parameters associated with the observed predictors β and γ are sometimes called ‘fixed’ regression parameters to distinguish them from the parameters characterizing the joint distribution of the random terms ε ic and u c (their variances σ2ε and σ2u ).
-These variances are often referred to as ‘random effect’ parameters or ‘variance components’.
 

### 2021-03-10 Manuscript.tex
manuscript development

@@
 For instance, scholars argue that founding teams with a more ties to potential investors are more likely to gain funding (Shane \& Stuart, 2002).
-Furthermore, if we focus on the findings of the stream of research examining the performance implications of acquiring financial capital (e.g.; (Hochberg, Ljungqvist, \& Lu, 2007)) we would expect that early-stage financing should be most likely to garner founders' attention.
+Furthermore, if we focus on the findings of the stream of research examining the performance implications of acquiring financial capital (Hochberg, Ljungqvist, \& Lu, 2007) we would expect that early-stage financing should be most likely to garner founders' attention.
 However, the role of the institutional context has been ignored and neglected in this debate.
@@
 
+\emph{Predictors}
+\textbf{Venture attention to a resource} A common approach to measure attention allocation is to use the revealed preference of individuals to evaluate the attention structure (Gebauer, 2009).
+I use the entrepreneurs' ranked preference of the desired benefits from accelerator programs as a proxy for the attention allocation of the early-stage ventures to various resources.
+The GALI questionnaire asks applying entrepreneurs to rank seven acceleration benefits by perceived importance to their ventures.
+The seven benefits are network development (Network), e.g.~with potential partners and customers, business skill development (Business Skills), mentorship from business experts (Mentorship), indirect funding through access to potential investors/funders (Access to Investors), securing direct venture funding (Direct Funding), gaining access to a group of like-minded entrepreneurs (Access to Like-minded Entrepreneurs), and awareness and credibility (Awareness and Credibility).
+Setting aside Awareness and Credibility and Access to Like-minded Entrepreneurs, the remaining five benefits can be categorized into three types of resources.
+Mentorship and Business Skills represent the development of human capital.
+Network help develop social capital.
+Direct Funding and Access to Investors improve the financial capital of early-stage ventures directly or indirectly.
+
+Respondents are asked to rank the seven benefits on a scale from one to seven, with one being the most important and seven being the least important.
+These rankings were reverse-coded to facilitate interpretation of the effects in order of increased importance, with 1 being the least important and 7 the most important.
+The benefits that accelerators provide consistently ranked in the top three were network development, business skills development, and securing direct venture funding.
+I assume that the early-stage ventures' attention allocation reflects the rankings given in their questionnaires.
+The questionnaire enforces a rule that respondents need to enter a ranking for all seven benefits and no tie is allowed.
+I exclude observations that do not have complete ranking of the seven items or because they have ties in the rankings.
+
+\textbf{Institutional level capital} To measure the level of capital of a certain resource at the country level, I used data from the World Economic Forum Global Competitiveness Index (GCI).
+Specificaly, I used the variable State of cluster development as a measure for institutional level social capital; Ease of finding skilled employees as a measure for institutional level human capital; and Venture capital availability, Financing of Small and Medium Enterprises, Domestic Credit Gaps as different measures of institutional level financial capital.
+While former measures of fiancial capital are self-explanatory, the latter variable is defined loans, purchases of non-equity securities, and trade credits and other accounts receivable provided to the private sector by financial corporations as a percentage of gross domestic products (GDP).
+
+\emph{Outcomes}
+\textbf{Resource mobilization} is coded as a dichotomous measure \emph{Participated} equal to one
+if an applicant participate to an accelerator program of choice, and zero otherwise.
+I assume that pariticipating to an acceleration program is the first step to mobiliza all types of resources provided by the accelerator.
+
+\textbf{Resource acquisition} once participants mobilize resources through participation to an accelerator, they engage in acquiring resources that garner their attention.
+These resources can translate into (a) raising capital from one source or many sources depending on (b) the entrepreneurs social capital (i.e.~Network) or (c) hiring employees.
+(a), (b), and (c) are all resource acquisition outcomes.
+
+\textbf{Performance} finaly to measure the impact on venture performance, I use the variable \emph{Revenue} as a proxy for this outcome.
+This is the most commonly used performance indicator in the management in strategy litrature.
+
+\emph{Control Variables}
+\textbf{Human Capital Index} consists of educational attainment, prior career experience in executive positions (C-level positions), team tenure, and prior founding experience (Colombo \& Grilli, 2005; Dimov \& Shepherd, 2005; Estrin, Mickiewicz, \& Stephan, 2016).
+I measure the educational attainment of a founding team by calculating the percentage of founders with a graduate degree in the founding team (Graduate Percentage).
+Prior career experience in C-level executive positions (Prior C-level Executive Percentage) is measured by the percentage of founders in the founding teams holding C-level executive positions prior to the current venture.
+Average Team Tenure measures the average working years of the founding team members.
+Team Prior Founding measures the number of organizations founded by the founding team before the current venture.
+
+To create an index, I use the quantile normalization technique to reduce the effect of extreme values while preserving the sequence of an observation in each variable (Hansen, Irizarry, \& Wu, 2012).
+Quantile normalization makes two or more distributions identical in statistical properties, such as maximum, minimum, and mean, without a reference distribution.
+It maintains the order, namely quantile, of observations in each variable treated but the values are normalized with respect to values from other variables at the same quantile.
+After doing so, the extreme values observed in some variables are smoothed out while the order is preserved, allowing us to explore the effect of each variable more accurately.
+I first z-standardize the above-mentioned variables.
+Then, I use the \{preprocessCore\} package to conduct quantile normalization by sets of variables.
+I then rescale the index to a range between 0 and 1.
+
+\textbf{Gender composition} the proportion female co-founders in each venture team.
+
 \hypertarget{data}{%
 \subsection{Data}\label{data}}
+
+The dataset from the Global Accelerator Learning Initiative (GALI) covers entrepreneurs who applied to scores of accelerators that began accepting applications between 2013 and 2020.
+Our data include information -- collected during program applications -- about ventures, founding teams, and pre-program performance.
+They also identify which applicants went on to participate in each program.
+Finally, these data include follow-up information collected from selected and rejected applicants in the years following each application window.
+The anonymized dataset containing both application and follow-up data can be accessed at \href{www.galidata.org/data-request}{GALI Data}.
+This is multi-country dataset.
+It typically contains hundreds of ventures per country.
+
+When entrepreneurs apply to a GALI-participating accelerator, they are asked to complete a standardized survey which asks basic questions about their venture's business model, financial performance, and founding team.
+Then, after one year, they are asked to complete a follow-up survey, whether or not they were accepted into the program to which they applied.
+
+I set aside XXX nonprofit organizations and XXX observations that are missing relevant venture information or preference ranking, resulting in xxx observations in the final sample.
+All financial statistics are in United States Dollars (USD).
+********
 
@@
 
-We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study.
+Mixed-effects logit and probit
+
+Given the structure of the data I used a model that incorporates both fixed- and random-effects terms.
+This helps me take into account the institutional (i.e.~country) effect on venture outcomes and quantify the extent to which differences in outcomes reflect differences in the effects of country-specific features, specifically institutional level capital.
 
@@
 
-Our dataset, the Global Accelerator Learning Initiative (GALI), covers entrepreneurs who applied to scores of accelerators that began accepting applications between 2013 and 2020.
-Our data include information -- collected during program applications -- about ventures, founding teams, and pre-program performance.
-They also identify which applicants went on to participate in each program.
-Finally, these data include follow-up information collected from selected and rejected applicants in the years following each application window.
-The anonymized dataset containing both application and follow-up data can be accessed at \href{www.galidata.org/data-request}{GALI Data}.
-
-When entrepreneurs apply to a GALI-participating accelerator, they are asked to complete a standardized survey which asks basic questions about their venture's business model, financial performance, and founding team.
-Then, after one year, they are asked to complete a follow-up survey, whether or not they were accepted into the program to which they applied.
-
-All financial statistics are in United States Dollars (USD).
-
-Table 1: Ventures in sample, by country of operation and survey responses
-
 \hypertarget{discussion}{%
@@
 
+\leavevmode\hypertarget{ref-colombo2005founders}{}%
+Colombo, M. G., \& Grilli, L. (2005). Founders' human capital and the growth of new technology-based firms: A competence-based view. \emph{Research Policy}, \emph{34}(6), 795--816.
+
 \leavevmode\hypertarget{ref-R-plm_a}{}%
 Croissant, Y., \& Millo, G. (2008). Panel data econometrics in R: The plm package. \emph{Journal of Statistical Software}, \emph{27}(2), 1--43. \url{https://doi.org/10.18637/jss.v027.i02}
+
+\leavevmode\hypertarget{ref-dimov2005human}{}%
+Dimov, D. P., \& Shepherd, D. A. (2005). Human capital theory and venture capital firms: Exploring ``home runs'' and ``strike outs''. \emph{Journal of Business Venturing}, \emph{20}(1), 1--21.
+
+\leavevmode\hypertarget{ref-estrin2016human}{}%
+Estrin, S., Mickiewicz, T., \& Stephan, U. (2016). Human capital in social and commercial entrepreneurship. \emph{Journal of Business Venturing}, \emph{31}(4), 449--467.
 
@@
 
+\leavevmode\hypertarget{ref-gebauer2009attention}{}%
+Gebauer, H. (2009). An attention-based view on service orientation in the business strategy of manufacturing companies. \emph{Journal of Managerial Psychology}.
+
 \leavevmode\hypertarget{ref-R-lubridate}{}%
 Grolemund, G., \& Wickham, H. (2011). Dates and times made easy with lubridate. \emph{Journal of Statistical Software}, \emph{40}(3), 1--25. Retrieved from \url{http://www.jstatsoft.org/v40/i03/}
+
+\leavevmode\hypertarget{ref-hansen2012removing}{}%
+Hansen, K. D., Irizarry, R. A., \& Wu, Z. (2012). Removing technical variability in rna-seq data using conditional quantile normalization. \emph{Biostatistics}, \emph{13}(2), 204--216.
 

### 2021-03-11 Manuscript.Rmd
kable extra is driving me crazy

@@
 library("papaja")
-#install.packages("tinytex")
-#tinytex::install_tinytex()
 r_refs("r-references.bib")
@@
 knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
+#options(knitr.table.format = "latex")
+```
+
+```{r message=FALSE, warning=FALSE, include=FALSE}
+#This is not my code. It is from https://rdrr.io/cran/gdata/src/R/cbindX.R to help me me bind cols of dfs with different number of rows
+
+cbindX <- function(...)
+{
+  ## --- Setup ---
+
+  x <- list(...)
+
+  ## Are all objects matrices or data.frames?
+  test <- sapply(x, function(z) is.matrix(z) | is.data.frame(z))
+  if(any(!test)) stop("only matrices and data.frames can be used")
+
+  ## Get maximum number of rows
+  tmp <- sapply(x, nrow)
+  maxi <- which.max(tmp)
+  test <- tmp < tmp[maxi]
+
+  ## --- Core ---
+
+  ## Adding additional "empty" rows so that all objects have the same number of rows
+  for(i in 1:length(tmp)) {
+    if(test[i]) {
+      add <- matrix(nrow=tmp[maxi] - tmp[i], ncol=ncol(x[[i]]))
+      if(is.data.frame(x[[i]])) {
+        add <- as.data.frame(add)
+      }
+      colnames(add) <- colnames(x[[i]])
+      x[[i]] <- rbind(x[[i]], add)
+    }
+  }
+
+  ## Column-bind all objects
+  ret <- x[[1]]
+  for(i in 2:length(tmp)) {
+    ret <- cbind(ret, x[[i]])
+  }
+
+  ## --- Return ---
+  ret
+}
 ```
@@
 
-*Predictors*
-**Venture attention to a resource** A common approach to measure attention allocation is to use the revealed preference of individuals to evaluate the attention structure [@gebauer2009attention].
+**Predictors**
+
+*Venture attention to a resource* A common approach to measure attention allocation is to use the revealed preference of individuals to evaluate the attention structure [@gebauer2009attention].
 I use the entrepreneurs’ ranked preference of the desired benefits from accelerator programs as a proxy for the attention allocation of the early-stage ventures to various resources.
@@
 
-**Institutional level capital** To measure the level of capital of a certain resource at the country level, I used data from the World Economic Forum Global Competitiveness Index (GCI).
-Specificaly, I used the variable State of cluster development as a measure for institutional level social capital; Ease of finding skilled employees as a measure for institutional level human capital; and Venture capital availability, Financing of Small and Medium Enterprises, Domestic Credit Gaps as different measures of institutional level financial capital.
+*Institutional level capital* To measure the level of capital of a certain resource at the country level, I used data from the World Economic Forum Global Competitiveness Index (GCI).
+Specificaly, I used the variable State of cluster development as a measure for institutional level social capital; Ease of finding skilled employees as a measure for institutional level human capital; and Venture capital (VC) availability, Financing of Small and Medium Enterprises (SMEs), Domestic Credit Gaps as different measures of institutional level financial capital.
 While former measures of fiancial capital are self-explanatory, the latter variable is defined loans, purchases of non-equity securities, and trade credits and other accounts receivable provided to the private sector by financial corporations as a percentage of gross domestic products (GDP).
 
-*Outcomes*
-**Resource mobilization** is coded as a dichotomous measure *Participated* equal to one
+**Outcomes**
+
+*Resource mobilization* is coded as a dichotomous measure *Participated* equal to one
 if an applicant participate to an accelerator program of choice, and zero otherwise.
@@
 
-**Resource acquisition** once participants mobilize resources through participation to an accelerator, they engage in acquiring resources that garner their attention.
+*Resource acquisition* once participants mobilize resources through participation to an accelerator, they engage in acquiring resources that garner their attention.
 These resources can translate into (a) raising capital from one source or many sources depending on (b) the entrepreneurs social capital (i.e.
@@
 
-**Performance** finaly to measure the impact on venture performance, I use the variable *Revenue* as a proxy for this outcome.
+*Performance* finaly to measure the impact on venture performance, I use the variable *Revenue* as a proxy for this outcome.
 This is the most commonly used performance indicator in the management in strategy litrature.
 
-*Control Variables*
-**Human Capital Index** consists of educational attainment, prior career experience in executive positions (C-level positions), team tenure, and prior founding experience [@colombo2005founders; @dimov2005human; @estrin2016human].
+**Control Variables**
+
+*Human Capital Index* consists of educational attainment, prior career experience in executive positions (C-level positions), team tenure, and prior founding experience [@colombo2005founders; @dimov2005human; @estrin2016human].
 I measure the educational attainment of a founding team by calculating the percentage of founders with a graduate degree in the founding team (Graduate Percentage).
@@
 
-**Gender composition** the proportion female co-founders in each venture team.
+*Gender composition* the proportion female co-founders in each venture team.
 
@@
 ## Methods
-Mixed-effects logit and probit
+The ventures in our sample are nested within countries.
+To account for such nested (or hierarchical) structure of the data, I opt for a linear mixed effects model to estimate the effects of each resource alone and when it interacts with institutional level of the resource.
+This helps us account for fixed effects and random effects associated with non-nested grouping factors.
+Namely, it allows us to take into account the institutional (i.e.
+country) effect on venture outcomes and quantify the extent to which differences in outcomes reflect differences in the effects of country-specific features, specifically institutional level capital.
 
-Given the structure of the data I used a model that incorporates both fixed- and random-effects terms.
-This helps me take into account the institutional (i.e.
-country) effect on venture outcomes and quantify the extent to which differences in outcomes reflect differences in the effects of country-specific features, specifically institutional level capital.
+The following equation (formulas) show all the models by outcome category.
+Of note, I run all the following models with conrols and without controls as robustness check.
+Control vriables are HCI refering to Human Capital Index and GC refering to Gender composition (i.e.
+female percentage in a team).
+
+**Resource mobilization**
+
+(1)	*Participated ~  AHC + (AHC | Country)    ; AHC = Attention to Human Capital* 
+(2)	*Participated ~  AHC + (AHC x Ease of finding skilled employees | Country)*
+(3)	*Participated ~  AFC + (AFC | Country)   ; AHC = Attention to Financial Capital*
+(4)	*Participated ~  AFC + (AFC x Financing of SMEs| Country)*   
+(5)	*Participated ~  AFC + (AFC x VC availability | Country)*   
+(6)	*Participated ~  AFC + (AFC x Domestic Credit Gaps | Country)*   
+(7)	*Participated ~  ASC + (ASC | Country) ; ASC = Attention to Social Capital*   
+(8)	*Participated ~  ASC + (ASC x State of cluster development | Country)*
+
+**Resource acquisition**
+
+(9) *Total employees ~ AHC + (AHC | Country)*
+(10) *Total employees ~ AHC + (AHC x Ease of finding skilled employees | Country)*
+(11) *Capital Raised ~ AFC + (AFC | Country)* 
+(12) *Capital Raised ~ AFC + (AFC x Financing of SMEs| Country)*
+(13) *Capital Raised ~ AFC + (AFC x VC availability | Country)*
+(14) *Capital Raised ~ AFC + (AFC x VC availability | Country)*
+(15) *Capital sources ~ ASC + (ASC | Country)*   
+(16) *Capital sources ~  ASC + (ASC x State of cluster development | Country)*
+
+**Performance**
+
+(17)	*Revenue ~  AHC + (AHC | Country)* 
+(18)	*Revenue ~  AHC + (AHC x Ease of finding skilled employees | Country)*
+(19)	*Revenue ~  AFC + (AFC | Country)*
+(20)	*Revenue ~  AFC + (AFC x Financing of SMEs| Country)*   
+(21)	*Revenue ~  AFC + (AFC x VC availability | Country)*   
+(22)	*Revenue ~  AFC + (AFC x Domestic Credit Gaps | Country)*   
+(23)	*Revenue ~  ASC + (ASC | Country)*   
+(24)	*Revenue ~  ASC + (ASC x State of cluster development | Country)*
 
@@
 library(preprocessCore)
+library(kableExtra)
 
@@
   col = gg.col(100), theta = 60, phi = 20,
-  xlab = "Human capital", ylab = "Financail capital", zlab = "Social capital", 
+  xlab = "Human capital", ylab = "Financial capital", zlab = "Social capital", 
   main = "Institutional level resources", cex = 0.6, 
@@
 
-#Attention to capital - venture data
+```{r Cleaning data of acceleration benefit ranking, message=FALSE, warning=FALSE, include=FALSE}
 
-```{r Cleaning data of acceleration benefit ranking, message=FALSE, warning=FALSE, include=FALSE}
+## Attention to capital - venture data
 
@@
 
+```{r Human capital index}
 ##Control variables
@@
 
-```{r Human capital index}
 #Graduate percentage
@@
 
-##Gender decomposition variable
+```{r Gender decomposition variable}
+##Gender composition variable
 
-```{r Gender decomposition variable}
 gali <- gali %>% drop_na(found_name1_gender)
@@
 
+```{r message=FALSE, warning=FALSE, include=FALSE}
 #Reverse code attention variable
-```{r message=FALSE, warning=FALSE, include=FALSE}
+
 #Reverse code fundtion 
@@
 
+```{r fig.height=5, fig.width=8}
 #Distribution of attention
 
-```{r fig.height=5, fig.width=8}
 a <- gali %>%
@@
 
-##Outcomes
+```{r message=FALSE, warning=FALSE, include=FALSE}
+#Revenues
 
-#Revenues
-```{r message=FALSE, warning=FALSE, include=FALSE}
 gali <- gali %>% mutate(revenue_tot = gali %>%
@@
 
+```{r message=FALSE, warning=FALSE, include=FALSE}
 #Human capital acquisition
-```{r message=FALSE, warning=FALSE, include=FALSE}
+
 gali  <- gali %>% mutate(hr_tot = gali %>%
@@
 
+```{r message=FALSE, warning=FALSE, include=FALSE}
 #Social capital acquisition
-```{r message=FALSE, warning=FALSE, include=FALSE}
 gali <- gali %>% mutate(equity_sources_tot = gali %>%
@@
 
+```{r message=FALSE, warning=FALSE, include=FALSE}
 #Fiancial Capital acquisiton total
-```{r message=FALSE, warning=FALSE, include=FALSE}
 gali  <- gali %>% mutate(capital_raised0 = gali %>% select(starts_with("inv_") & ends_with("_m1")) %>% 
@@
 
+```{r}
 #Predictor and outcome plots
-```{r}
 
@@
 
+```{r message=FALSE, warning=FALSE, include=FALSE}
 #Join all 3 datasets 
-```{r message=FALSE, warning=FALSE, include=FALSE}
-
 gali_joined <- left_join(gali, gci, by = "country")
-
 ```
 
+```{r message=FALSE, warning=FALSE}
 # Results
 
-```{r message=FALSE, warning=FALSE, include=FALSE}
 #Function to extract coefficients of summary table
@@
     , "$t$" = "t value"
+    , "$p$" = "Pr(>|t|)"
   ) %>%
@@
   ) %>%
-  select(Effect, `$b$`, `SE`, `$t$`)}
+  select(Effect, `$b$`, `SE`, `$t$`, `$p$`)}
 
@@
     , "$z$" = "z value"
+    , "$p$" = "Pr(>|z|)"
   ) %>%
@@
   ) %>%
-  select(Effect, `$b$`, `SE`, `$z$`)}
+  select(Effect, `$b$`, `SE`, `$z$`, `$p$`)}
 
@@
 
-#Mixed model analysis - Human capital
 ```{r echo=FALSE, message=FALSE, warning=FALSE}
+#Outcome: resource mobilization 
+#Models
 library(lme4)
@@
 
+fit0hc_c <- glmer(participated ~  accel_ben_rank_business_skills + (accel_ben_rank_business_skills|country) + HC_index + female_pct, data = gali_joined, family=binomial)
+
 fit1hc <- glmer(participated ~  accel_ben_rank_business_skills*EOSQ403 + (accel_ben_rank_business_skills|country), data = gali_joined, family=binomial)
+
+fit1hc_c <- glmer(participated ~  accel_ben_rank_business_skills*EOSQ403 + (accel_ben_rank_business_skills|country)+ HC_index + female_pct, data = gali_joined, family=binomial)
+
+fit0fc <- glmer(participated ~  accel_ben_rank_direct_funding + (accel_ben_rank_direct_funding|country), data = gali_joined, family=binomial)
+
+fit0fc_c <- glmer(participated ~  accel_ben_rank_direct_funding + (accel_ben_rank_direct_funding|country)+ HC_index + female_pct, data = gali_joined, family=binomial)
+
+fit1fc <- glmer(participated ~ accel_ben_rank_direct_funding*EOSQ425 + (accel_ben_rank_direct_funding |country ), data = gali_joined, family=binomial)
+
+fit1fc_c <- glmer(participated ~ accel_ben_rank_direct_funding*EOSQ425 + (accel_ben_rank_direct_funding |country )+ HC_index + female_pct, data = gali_joined, family=binomial)
+
+fit2fc <- glmer(participated ~ accel_ben_rank_direct_funding*EOSQ089 + (accel_ben_rank_direct_funding |country ), data = gali_joined, family=binomial)
+
+fit2fc_c <- glmer(participated ~ accel_ben_rank_direct_funding*EOSQ089 + (accel_ben_rank_direct_funding |country )+ HC_index + female_pct, data = gali_joined, family=binomial)
+
+fit3fc <- glmer(participated ~ accel_ben_rank_direct_funding*DOMCREDITGDP + (accel_ben_rank_direct_funding |country), data = gali_joined, family=binomial)
+
+fit3fc_c <- glmer(participated ~ accel_ben_rank_direct_funding*DOMCREDITGDP + (accel_ben_rank_direct_funding |country)+ HC_index + female_pct, data = gali_joined, family=binomial)
+
+fit0sc <- glmer(participated ~ accel_ben_rank_network + (accel_ben_rank_network |country), data = gali_joined, family=binomial)
+
+fit0sc_c <- glmer(participated ~ accel_ben_rank_network + (accel_ben_rank_network |country)+ HC_index + female_pct, data = gali_joined, family=binomial)
+
+fit1sc <- glmer(participated ~ accel_ben_rank_network*EOSQ109 + (accel_ben_rank_network | country), data = gali_joined, family=binomial)
+
+fit1sc_c <- glmer(participated ~ accel_ben_rank_network*EOSQ109 + (accel_ben_rank_network | country)+ HC_index + female_pct, data = gali_joined, family=binomial)
+
+```
+
+```{r message=FALSE, warning=FALSE}
+#Summary tables
+
+hc0 <- summary_table_z(summary(fit0hc))
+hc0_c <- summary_table_z(summary(fit0hc_c))
+hc1 <- summary_table_z(summary(fit1hc))
+hc1_c <- summary_table_z(summary(fit1hc_c))
+fc0 <- summary_table_z(summary(fit0fc))
+fc0_c <- summary_table_z(summary(fit0fc_c))
+fc1 <- summary_table_z(summary(fit1fc))
+fc1_c <- summary_table_z(summary(fit1fc_c))
+fc2 <- summary_table_z(summary(fit2fc))
+fc2_c <- summary_table_z(summary(fit2fc_c))
+fc3 <- summary_table_z(summary(fit3fc))
+fc3_c <- summary_table_z(summary(fit3fc_c))
+sc0 <- summary_table_z(summary(fit0sc))
+sc0_c <- summary_table_z(summary(fit0sc_c))
+sc1 <- summary_table_z(summary(fit1sc))
+sc1_c <- summary_table_z(summary(fit1sc_c))
+
+rownames(hc0) <- c("Intercept","Attention to Human capital(AHC)")
+rownames(hc0_c) <- c("Intercept","Attention to Human capital(AHC)", "HCI", "GC")
+#rownames(hc1) <- c("Intercept","AHC", "Ease of finding skilled employees", "AHCxEase of finding skilled employees")
+rownames(hc1_c) <- c("Intercept","AHC", "Ease of finding skilled employees", "AHCxEase of finding skilled employees", "HCI", "GC")
+#rownames(fc0) <- c("Intercept","Attention to Financial capital")
+rownames(fc0_c) <- c("Intercept","Attention to Financial capital", "HCI", "GC")
+#rownames(fc1) <- c("Intercept","AFC", "Financing of SMEs", "AFCxFinancing of SMEs")
+rownames(fc1_c) <- c("Intercept","AFC", "Financing of SMEs", "AFCxFinancing of SMEs", "HCI", "GC")
+#rownames(fc2) <- c("Intercept","AFC", "VC Availability", "AFCxVC Availability")
+rownames(fc2_c) <- c("Intercept","AFC", "VC Availability", "AFCxVC Availability", "HCI", "GC")
+#rownames(fc3) <- c("Intercept","AFC", "Domestic Credit Gaps", "AFCxDomestic Credit Gaps")
+rownames(fc3_c) <- c("Intercept","AFC", "Domestic Credit Gaps", "AFCxDomestic Credit Gaps", "HCI", "GC")
+#rownames(sc0) <- c("Intercept","Attention to Social capital")
+rownames(sc0_c) <- c("Intercept","Attention to Social capital", "HCI", "GC")
+#rownames(sc1) <- c("Intercept","ASC", "State of cluster development","ASCxState of cluster development")
+rownames(sc1_c) <- c("Intercept","ASC", "State of cluster development","ASCxState of cluster development", "HCI", "GC")
+
+hc_zero <- cbindX(hc0_c[,-1], hc0[,-1]) 
+hc_one <- cbindX(hc1_c[,-1], hc1[,-1]) 
+fc_zero <- cbindX(fc0_c[,-1], fc0[,-1]) 
+fc_one <- cbindX(fc1_c[,-1], fc1[,-1])
+fc_two <- cbindX(fc2_c[,-1], fc2[,-1]) 
+fc_three <- cbindX(fc3_c[,-1], fc3[,-1]) 
+sc_zero <- cbindX(sc0_c[,-1], sc0[,-1]) 
+sc_one <- cbindX(sc1_c[,-1], sc1[,-1])
+
+```
+
+```{r }
+#Print summaries
+
+kable(hc_zero, booktabs = T, caption = "Table 1: Effect of attention to human capital", escape = F) %>%
+  add_header_above(c(" ", "Model w/ controls" = 4, "Model w/o controls" = 4), italic = T) %>%
+  kable_styling(latex_options = c("repeat_header")) %>%
+  pack_rows("Control variables", 3, 4, latex_gap_space = "2em")
+
+kable(hc_one, caption = "Table 2: Effect of congruency of venture attention and institutional level of human capital", format = "latex") %>%
+  add_header_above(c(" ", "Model w/ controls" = 4, "Model w/o controls" = 4), italic = T) %>%
+  kable_styling(latex_options = c("repeat_header")) %>%
+  pack_rows("Control variables", 3, 4, latex_gap_space = "2em")
+
+kbl(fc_zero, caption = "Table 3: Effect of attention to financial capital") %>%
+  add_header_above(c(" ", "Model w/ controls" = 4, "Model w/o controls" = 4), italic = T) %>%
+  kable_styling(latex_options = c("repeat_header")) %>%
+  pack_rows("Control variables", 3, 4, latex_gap_space = "2em")
+
+kbl(fc_one, caption = "Table 4: Effect of congruency of venture attention and institutional level (SME financing) of financial capital") %>%
+  add_header_above(c(" ", "Model w/ controls" = 4, "Model w/o controls" = 4), italic = T) %>%
+  kable_styling(latex_options = c("repeat_header")) %>%
+  pack_rows("Control variables", 3, 4, latex_gap_space = "2em")
+
+kbl(fc_two, caption = "Table 5: Effect of congruency of venture attention and institutional level (VC) of financial capital") %>%
+  add_header_above(c(" ", "Model w/ controls" = 4, "Model w/o controls" = 4), italic = T) %>%
+  kable_styling(latex_options = c("repeat_header")) %>%
+  pack_rows("Control variables", 3, 4, latex_gap_space = "2em")
+
+kbl(fc_three, caption = "Table 6: Effect of congruency of venture attention and institutional level (Credit gaps) of financial capital") %>%
+  add_header_above(c(" ", "Model w/ controls" = 4, "Model w/o controls" = 4), italic = T) %>%
+  kable_styling(latex_options = c("repeat_header")) %>%
+  pack_rows("Control variables", 3, 4, latex_gap_space = "2em")
+
+kbl(sc_zero, caption = "Table 7: Effect of attention to social capital") %>%
+  add_header_above(c(" ", "Model w/ controls" = 4, "Model w/o controls" = 4), italic = T) %>%
+  kable_styling(latex_options = c("repeat_header")) %>%
+  pack_rows("Control variables", 3, 4, latex_gap_space = "2em")
+
+kbl(sc_one, caption = "Table 8: Effect of congruency of venture attention and institutional level of social capital") %>%
+  add_header_above(c(" ", "Model w/ controls" = 4, "Model w/o controls" = 4), italic = T) %>%
+  kable_styling(latex_options = c("repeat_header")) %>%
+  pack_rows("Control variables", 3, 4, latex_gap_space = "2em")
+
+#kable(sc1_c[,-1], escape = FALSE, caption = "Table 16: Effect of congruency of venture attention and institutional level of social capital - Model with controls")
+
+```
+
+```{r eval=FALSE, message=FALSE, warning=FALSE, include=FALSE}
+#Outcome: Resource acquistion 
+library(lme4)
 
@@
 
-hc0 <- summary_table_z(summary(fit0hc))
-hc1 <- summary_table_z(summary(fit1hc))
-hc00 <- summary_table(summary(fit00hc))
-hc11 <- summary_table(summary(fit11hc))
-
-rownames(hc0) <- c("Intercept","Attention to Human capital(AHC)")
-rownames(hc1) <- c("Intercept","AHC", "Ease of finding skilled employees", "AHCxEase of finding skilled employees")
-rownames(hc00) <- c("Intercept","Attention to Human capital")
-rownames(hc11) <- c("Intercept","AHC", "Ease of finding skilled employees", "AHCxEase of finding skilled employees")
-
-kable(hc0[,-1], escape = FALSE) 
-kable(hc1[,-1], escape = FALSE)
-kable(hc00[,-1], escape = FALSE)
-kable(hc11[,-1], escape = FALSE)
-
-```
-
-#Mixed model analysis - Financial capital
-```{r echo=FALSE, message=FALSE, warning=FALSE}
-library(lme4)
-fit0fc <- glmer(participated ~  accel_ben_rank_direct_funding + (accel_ben_rank_direct_funding|country), data = gali_joined, family=binomial)
-
-fit1fc <- glmer(participated ~ accel_ben_rank_direct_funding*EOSQ425 + (accel_ben_rank_direct_funding |country ), data = gali_joined, family=binomial)
-
-fit2fc <- glmer(participated ~ accel_ben_rank_direct_funding*EOSQ089 + (accel_ben_rank_direct_funding |country ), data = gali_joined, family=binomial)
-
-fit3fc <- glmer(participated ~ accel_ben_rank_direct_funding*DOMCREDITGDP + (accel_ben_rank_direct_funding |country), data = gali_joined, family=binomial)
-
-summary(fit0fc)
-summary(fit1fc)
-summary(fit2fc)
-summary(fit3fc)
-
-fit00fc <- lmer(capital_raised_tot ~   + (accel_ben_rank_direct_funding|country), data = gali_joined, REML = F)
+fit00fc <- lmer(capital_raised_tot ~ + accel_ben_rank_direct_funding+ (accel_ben_rank_direct_funding|country), data = gali_joined, REML = F)
 
@@
 
-summary(fit00fc)
-summary(fit11fc)
-summary(fit22fc)
-summary(fit33fc)
-
-```
-
-#Mixed model analysis - Social capital
-
-```{r echo=FALSE, message=FALSE, warning=FALSE}
-fit0sc <- lmer(participated ~ accel_ben_rank_network + (accel_ben_rank_network |country), data = gali_joined, REML = F)
-
-fit1sc <- lmer(participated ~ accel_ben_rank_network*EOSQ109 + (accel_ben_rank_network | country), data = gali_joined, REML = F)
-
-coef(summary(fit0sc))
-coef(summary(fit1sc))
-
 fit00sc <- lmer(equity_sources_tot ~ accel_ben_rank_network + (accel_ben_rank_network |country), data = gali_joined, REML = F)
@@
 
-coef(summary(fit00sc))
-coef(summary(fit11sc))
+hc00 <- summary_table(summary(fit00hc))
+hc11 <- summary_table(summary(fit11hc))
+fc00 <- summary_table(summary(fit00fc))
+fc11 <- summary_table(summary(fit11fc))
+fc22 <- summary_table(summary(fit22fc))
+fc33 <- summary_table(summary(fit33fc))
+sc00 <- summary_table(summary(fit00sc))
+sc11 <- summary_table(summary(fit11sc))
+
+rownames(hc00) <- c("Intercept","Attention to Human capital")
+rownames(hc11) <- c("Intercept","AHC", "Ease of finding skilled employees", "AHCxEase of finding skilled employees")
+rownames(fc00) <- c("Intercept","Attention to Financial capital")
+rownames(fc11) <- c("Intercept","AFC", "Financing of SMEs", "AFCxFinancing of SMEs")
+rownames(fc22) <- c("Intercept","AFC", "VC Availability", "AFCxVC Availability")
+rownames(fc33) <- c("Intercept","AFC", "Domestic Credit Gaps", "AFCxDomestic Credit Gaps")
+rownames(sc00) <- c("Intercept","Attention to Social capital")
+rownames(sc11) <- c("Intercept","ASC", "State of cluster development","ASCxState of cluster development")
+
+#kable(hc00[,-1], escape = FALSE)
+#kable(hc11[,-1], escape = FALSE)
+#kable(fc00[,-1], escape = FALSE)
+#kable(fc11[,-1], escape = FALSE)
+#kable(fc22[,-1], escape = FALSE)
+#kable(fc33[,-1], escape = FALSE)
+#kable(sc00[,-1], escape = FALSE)
+#kable(sc11[,-1], escape = FALSE, caption = "This is the table caption")
 
 ```
-
-# Data and Methods
 

### 2021-03-11 Manuscript.tex
kable extra is driving me crazy

@@
 
-\emph{Predictors}
-\textbf{Venture attention to a resource} A common approach to measure attention allocation is to use the revealed preference of individuals to evaluate the attention structure (Gebauer, 2009).
+\textbf{Predictors}
+
+\emph{Venture attention to a resource} A common approach to measure attention allocation is to use the revealed preference of individuals to evaluate the attention structure (Gebauer, 2009).
 I use the entrepreneurs' ranked preference of the desired benefits from accelerator programs as a proxy for the attention allocation of the early-stage ventures to various resources.
@@
 
-\textbf{Institutional level capital} To measure the level of capital of a certain resource at the country level, I used data from the World Economic Forum Global Competitiveness Index (GCI).
-Specificaly, I used the variable State of cluster development as a measure for institutional level social capital; Ease of finding skilled employees as a measure for institutional level human capital; and Venture capital availability, Financing of Small and Medium Enterprises, Domestic Credit Gaps as different measures of institutional level financial capital.
+\emph{Institutional level capital} To measure the level of capital of a certain resource at the country level, I used data from the World Economic Forum Global Competitiveness Index (GCI).
+Specificaly, I used the variable State of cluster development as a measure for institutional level social capital; Ease of finding skilled employees as a measure for institutional level human capital; and Venture capital (VC) availability, Financing of Small and Medium Enterprises (SMEs), Domestic Credit Gaps as different measures of institutional level financial capital.
 While former measures of fiancial capital are self-explanatory, the latter variable is defined loans, purchases of non-equity securities, and trade credits and other accounts receivable provided to the private sector by financial corporations as a percentage of gross domestic products (GDP).
 
-\emph{Outcomes}
-\textbf{Resource mobilization} is coded as a dichotomous measure \emph{Participated} equal to one
+\textbf{Outcomes}
+
+\emph{Resource mobilization} is coded as a dichotomous measure \emph{Participated} equal to one
 if an applicant participate to an accelerator program of choice, and zero otherwise.
@@
 
-\textbf{Resource acquisition} once participants mobilize resources through participation to an accelerator, they engage in acquiring resources that garner their attention.
+\emph{Resource acquisition} once participants mobilize resources through participation to an accelerator, they engage in acquiring resources that garner their attention.
 These resources can translate into (a) raising capital from one source or many sources depending on (b) the entrepreneurs social capital (i.e.~Network) or (c) hiring employees.
@@
 
-\textbf{Performance} finaly to measure the impact on venture performance, I use the variable \emph{Revenue} as a proxy for this outcome.
+\emph{Performance} finaly to measure the impact on venture performance, I use the variable \emph{Revenue} as a proxy for this outcome.
 This is the most commonly used performance indicator in the management in strategy litrature.
 
-\emph{Control Variables}
-\textbf{Human Capital Index} consists of educational attainment, prior career experience in executive positions (C-level positions), team tenure, and prior founding experience (Colombo \& Grilli, 2005; Dimov \& Shepherd, 2005; Estrin, Mickiewicz, \& Stephan, 2016).
+\textbf{Control Variables}
+
+\emph{Human Capital Index} consists of educational attainment, prior career experience in executive positions (C-level positions), team tenure, and prior founding experience (Colombo \& Grilli, 2005; Dimov \& Shepherd, 2005; Estrin, Mickiewicz, \& Stephan, 2016).
 I measure the educational attainment of a founding team by calculating the percentage of founders with a graduate degree in the founding team (Graduate Percentage).
@@
 
-\textbf{Gender composition} the proportion female co-founders in each venture team.
+\emph{Gender composition} the proportion female co-founders in each venture team.
 
@@
 
-Mixed-effects logit and probit
+The ventures in our sample are nested within countries.
+To account for such nested (or hierarchical) structure of the data, I opt for a linear mixed effects model to estimate the effects of each resource alone and when it interacts with institutional level of the resource.
+This helps us account for fixed effects and random effects associated with non-nested grouping factors.
+Namely, it allows us to take into account the institutional (i.e.~country) effect on venture outcomes and quantify the extent to which differences in outcomes reflect differences in the effects of country-specific features, specifically institutional level capital.
 
-Given the structure of the data I used a model that incorporates both fixed- and random-effects terms.
-This helps me take into account the institutional (i.e.~country) effect on venture outcomes and quantify the extent to which differences in outcomes reflect differences in the effects of country-specific features, specifically institutional level capital.
+The following equation (formulas) show all the models by outcome category.
+Of note, I run all the following models with conrols and without controls as robustness check.
+Control vriables are HCI refering to Human Capital Index and GC refering to Gender composition (i.e.~female percentage in a team).
+
+\textbf{Resource mobilization}
+
+\begin{enumerate}
+\def\labelenumi{(\arabic{enumi})}
+\tightlist
+\item
+  \emph{Participated \textasciitilde{} AHC + (AHC \textbar{} Country) ; AHC = Attention to Human Capital}
+\item
+  \emph{Participated \textasciitilde{} AHC + (AHC x Ease of finding skilled employees \textbar{} Country)}
+\item
+  \emph{Participated \textasciitilde{} AFC + (AFC \textbar{} Country) ; AHC = Attention to Financial Capital}
+\item
+  \emph{Participated \textasciitilde{} AFC + (AFC x Financing of SMEs\textbar{} Country)}\\
+\item
+  \emph{Participated \textasciitilde{} AFC + (AFC x VC availability \textbar{} Country)}\\
+\item
+  \emph{Participated \textasciitilde{} AFC + (AFC x Domestic Credit Gaps \textbar{} Country)}\\
+\item
+  \emph{Participated \textasciitilde{} ASC + (ASC \textbar{} Country) ; ASC = Attention to Social Capital}\\
+\item
+  \emph{Participated \textasciitilde{} ASC + (ASC x State of cluster development \textbar{} Country)}
+\end{enumerate}
+
+\textbf{Resource acquisition}
+
+\begin{enumerate}
+\def\labelenumi{(\arabic{enumi})}
+\setcounter{enumi}{8}
+\tightlist
+\item
+  \emph{Total employees \textasciitilde{} AHC + (AHC \textbar{} Country)}
+\item
+  \emph{Total employees \textasciitilde{} AHC + (AHC x Ease of finding skilled employees \textbar{} Country)}
+\item
+  \emph{Capital Raised \textasciitilde{} AFC + (AFC \textbar{} Country)}
+\item
+  \emph{Capital Raised \textasciitilde{} AFC + (AFC x Financing of SMEs\textbar{} Country)}
+\item
+  \emph{Capital Raised \textasciitilde{} AFC + (AFC x VC availability \textbar{} Country)}
+\item
+  \emph{Capital Raised \textasciitilde{} AFC + (AFC x VC availability \textbar{} Country)}
+\item
+  \emph{Capital sources \textasciitilde{} ASC + (ASC \textbar{} Country)}\\
+\item
+  \emph{Capital sources \textasciitilde{} ASC + (ASC x State of cluster development \textbar{} Country)}
+\end{enumerate}
+
+\textbf{Performance}
+
+\begin{enumerate}
+\def\labelenumi{(\arabic{enumi})}
+\setcounter{enumi}{16}
+\tightlist
+\item
+  \emph{Revenue \textasciitilde{} AHC + (AHC \textbar{} Country)}
+\item
+  \emph{Revenue \textasciitilde{} AHC + (AHC x Ease of finding skilled employees \textbar{} Country)}
+\item
+  \emph{Revenue \textasciitilde{} AFC + (AFC \textbar{} Country)}
+\item
+  \emph{Revenue \textasciitilde{} AFC + (AFC x Financing of SMEs\textbar{} Country)}\\
+\item
+  \emph{Revenue \textasciitilde{} AFC + (AFC x VC availability \textbar{} Country)}\\
+\item
+  \emph{Revenue \textasciitilde{} AFC + (AFC x Domestic Credit Gaps \textbar{} Country)}\\
+\item
+  \emph{Revenue \textasciitilde{} ASC + (ASC \textbar{} Country)}\\
+\item
+  \emph{Revenue \textasciitilde{} ASC + (ASC x State of cluster development \textbar{} Country)}
+\end{enumerate}
 
@@
 
-\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-4-1.pdf} \includegraphics{Manuscript_files/figure-latex/unnamed-chunk-4-2.pdf}
+\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-5-1.pdf} \includegraphics{Manuscript_files/figure-latex/unnamed-chunk-5-2.pdf}
 
-\#Attention to capital - venture data
+\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-7-1.pdf} \includegraphics{Manuscript_files/figure-latex/unnamed-chunk-7-2.pdf}
 
-\#\#Control variables
+\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-12-1.pdf} \includegraphics{Manuscript_files/figure-latex/unnamed-chunk-12-2.pdf}
 
-\#\#Constrcuting human capital index (control variable)
-\#\#\#Graduate percentage, Prior C-level Executive Percentage, Average Team Tenure , Team Prior Founding
+\begin{table}
 
-\#\#Gender decomposition variable
+\caption{\label{tab:unnamed-chunk-18}Table 1: Effect of attention to human capital}
+\centering
+\begin{tabular}[t]{lllllllll}
+\toprule
+\multicolumn{1}{c}{\em{ }} & \multicolumn{4}{c}{\em{Model w/ controls}} & \multicolumn{4}{c}{\em{Model w/o controls}} \\
+\cmidrule(l{3pt}r{3pt}){2-5} \cmidrule(l{3pt}r{3pt}){6-9}
+  & $b$ & SE & $z$ & $p$ & $b$ & SE & $z$ & $p$\\
+\midrule
+Intercept & -1.54 & 0.08 & -19.82 & 0.000 & -1.46 & 0.08 & -19.18 & 0.000\\
+Attention to Human capital(AHC) & 0.09 & 0.07 & 1.24 & 0.215 & 0.11 & 0.07 & 1.54 & 0.123\\
+\addlinespace[2em]
+\multicolumn{9}{l}{\textbf{Control variables}}\\
+\hspace{1em}HCI & 0.01 & 0.01 & 1.46 & 0.144 & NA & NA & NA & NA\\
+\hspace{1em}GC & 0.24 & 0.06 & 4.17 & 0.000 & NA & NA & NA & NA\\
+\bottomrule
+\end{tabular}
+\end{table}
 
-\#Reverse code attention variable
+\begin{table}
 
-\#Distribution of attention
-
-\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-6-1.pdf} \includegraphics{Manuscript_files/figure-latex/unnamed-chunk-6-2.pdf}
-
-\#\#Outcomes
-
-\#Revenues
-
-\#Human capital acquisition
-
-\#Social capital acquisition
-
-\#Fiancial Capital acquisiton total
-
-\#Predictor and outcome plots
-\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-11-1.pdf} \includegraphics{Manuscript_files/figure-latex/unnamed-chunk-11-2.pdf}
-
-\#Join all 3 datasets
-
-\hypertarget{results}{%
-\section{Results}\label{results}}
-
-\#Mixed model analysis - Human capital
-
-\begin{tabular}{l|l|l|l}
+\caption{\label{tab:unnamed-chunk-18}Table 2: Effect of congruency of venture attention and institutional level of human capital}
+\centering
+\begin{tabular}[t]{l|l|l|l|l|l|l|l|l}
 \hline
-  & $b$ & SE & $z$\\
+\multicolumn{1}{c|}{\em{ }} & \multicolumn{4}{c|}{\em{Model w/ controls}} & \multicolumn{4}{c}{\em{Model w/o controls}} \\
+\cline{2-5} \cline{6-9}
+  & \$b\$ & SE & \$z\$ & \$p\$ & \$b\$ & SE & \$z\$ & \$p\$\\
 \hline
-Intercept & -1.46 & 0.08 & -19.18\\
+Intercept & -0.94 & 0.53 & -1.80 & 0.073 & -0.85 & 0.53 & -1.61 & 0.108\\
 \hline
-Attention to Human capital(AHC) & 0.11 & 0.07 & 1.54\\
+AHC & 0.90 & 0.45 & 2.01 & 0.044 & 0.92 & 0.45 & 2.05 & 0.040\\
+\hline
+\multicolumn{9}{l}{\textbf{Control variables}}\\
+\hline
+\hspace{1em}Ease of finding skilled employees & -0.13 & 0.12 & -1.11 & 0.269 & -0.14 & 0.12 & -1.14 & 0.253\\
+\hline
+\hspace{1em}AHCxEase of finding skilled employees & 0.01 & 0.01 & 1.37 & 0.171 & -0.17 & 0.10 & -1.79 & 0.074\\
+\hline
+HCI & 0.24 & 0.06 & 4.06 & 0.000 & NA & NA & NA & NA\\
+\hline
+GC & -0.17 & 0.10 & -1.80 & 0.073 & NA & NA & NA & NA\\
 \hline
 \end{tabular}
+\end{table}
 
-\begin{tabular}{l|l|l|l}
+\begin{table}
+
+\caption{\label{tab:unnamed-chunk-18}Table 3: Effect of attention to financial capital}
+\centering
+\begin{tabular}[t]{l|l|l|l|l|l|l|l|l}
 \hline
-  & $b$ & SE & $z$\\
+\multicolumn{1}{c|}{\em{ }} & \multicolumn{4}{c|}{\em{Model w/ controls}} & \multicolumn{4}{c}{\em{Model w/o controls}} \\
+\cline{2-5} \cline{6-9}
+  & \$b\$ & SE & \$z\$ & \$p\$ & \$b\$ & SE & \$z\$ & \$p\$\\
 \hline
-Intercept & -0.85 & 0.53 & -1.61\\
+Intercept & -1.53 & 0.08 & -19.55 & 0.000 & -1.45 & 0.08 & -18.82 & 0.000\\
 \hline
-AHC & 0.92 & 0.45 & 2.05\\
+Attention to Financial capital & -0.19 & 0.06 & -3.02 & 0.003 & -0.19 & 0.06 & -3.06 & 0.002\\
 \hline
-Ease of finding skilled employees & -0.14 & 0.12 & -1.14\\
+\multicolumn{9}{l}{\textbf{Control variables}}\\
 \hline
-AHCxEase of finding skilled employees & -0.17 & 0.10 & -1.79\\
+\hspace{1em}HCI & 0.01 & 0.01 & 1.39 & 0.165 & NA & NA & NA & NA\\
+\hline
+\hspace{1em}GC & 0.25 & 0.06 & 4.34 & 0.000 & NA & NA & NA & NA\\
 \hline
 \end{tabular}
+\end{table}
 
-\begin{tabular}{l|l|l|l}
+\begin{table}
+
+\caption{\label{tab:unnamed-chunk-18}Table 4: Effect of congruency of venture attention and institutional level (SME financing) of financial capital}
+\centering
+\begin{tabular}[t]{l|l|l|l|l|l|l|l|l}
 \hline
-  & $b$ & SE & $t$\\
+\multicolumn{1}{c|}{\em{ }} & \multicolumn{4}{c|}{\em{Model w/ controls}} & \multicolumn{4}{c}{\em{Model w/o controls}} \\
+\cline{2-5} \cline{6-9}
+  & \$b\$ & SE & \$z\$ & \$p\$ & \$b\$ & SE & \$z\$ & \$p\$\\
 \hline
-Intercept & 762.25 & 502.25 & 1.52\\
+Intercept & -1.43 & 0.43 & -3.35 & 0.001 & -1.35 & 0.43 & -3.11 & 0.002\\
 \hline
-Attention to Human capital & 2,955.97 & 2,238.11 & 1.32\\
+AFC & -0.19 & 0.29 & -0.66 & 0.509 & -0.21 & 0.29 & -0.74 & 0.460\\
+\hline
+\multicolumn{9}{l}{\textbf{Control variables}}\\
+\hline
+\hspace{1em}Financing of SMEs & -0.02 & 0.11 & -0.20 & 0.845 & -0.02 & 0.11 & -0.19 & 0.847\\
+\hline
+\hspace{1em}AFCxFinancing of SMEs & 0.01 & 0.01 & 1.30 & 0.193 & 0.00 & 0.07 & 0.05 & 0.959\\
+\hline
+HCI & 0.25 & 0.06 & 4.25 & 0.000 & NA & NA & NA & NA\\
+\hline
+GC & 0.00 & 0.07 & -0.02 & 0.988 & NA & NA & NA & NA\\
 \hline
 \end{tabular}
+\end{table}
 
-\begin{tabular}{l|l|l|l}
+\begin{table}
+
+\caption{\label{tab:unnamed-chunk-18}Table 5: Effect of congruency of venture attention and institutional level (VC) of financial capital}
+\centering
+\begin{tabular}[t]{l|l|l|l|l|l|l|l|l}
 \hline
-  & $b$ & SE & $t$\\
+\multicolumn{1}{c|}{\em{ }} & \multicolumn{4}{c|}{\em{Model w/ controls}} & \multicolumn{4}{c}{\em{Model w/o controls}} \\
+\cline{2-5} \cline{6-9}
+  & \$b\$ & SE & \$z\$ & \$p\$ & \$b\$ & SE & \$z\$ & \$p\$\\
 \hline
-Intercept & -1,955.91 & 3,599.05 & -0.54\\
+Intercept & -1.31 & 0.28 & -4.74 & 0.000 & -1.22 & 0.28 & -4.35 & 0.000\\
 \hline
-AHC & -10,174.65 & 16,704.03 & -0.61\\
+AFC & -0.23 & 0.20 & -1.17 & 0.244 & -0.24 & 0.20 & -1.24 & 0.217\\
 \hline
-Ease of finding skilled employees & 641.03 & 813.08 & 0.79\\
+\multicolumn{9}{l}{\textbf{Control variables}}\\
 \hline
-AHCxEase of finding skilled employees & 3,118.93 & 3,842.90 & 0.81\\
+\hspace{1em}VC Availability & -0.07 & 0.09 & -0.75 & 0.454 & -0.07 & 0.09 & -0.79 & 0.432\\
+\hline
+\hspace{1em}AFCxVC Availability & 0.01 & 0.01 & 1.31 & 0.190 & 0.01 & 0.05 & 0.28 & 0.778\\
+\hline
+HCI & 0.24 & 0.06 & 4.23 & 0.000 & NA & NA & NA & NA\\
+\hline
+GC & 0.01 & 0.05 & 0.22 & 0.824 & NA & NA & NA & NA\\
 \hline
 \end{tabular}
+\end{table}
 
-\#Mixed model analysis - Financial capital
+\begin{table}
 
-\begin{verbatim}
-## Generalized linear mixed model fit by maximum likelihood (Laplace
-##   Approximation) [glmerMod]
-##  Family: binomial  ( logit )
-## Formula: 
-## participated ~ accel_ben_rank_direct_funding + (accel_ben_rank_direct_funding |  
-##     country)
-##    Data: gali_joined
-## 
-##      AIC      BIC   logLik deviance df.resid 
-##  14773.7  14812.1  -7381.8  14763.7    15976 
-## 
-## Scaled residuals: 
-##     Min      1Q  Median      3Q     Max 
-## -1.0388 -0.4890 -0.4207 -0.3515  3.0479 
-## 
-## Random effects:
-##  Groups  Name                          Variance Std.Dev. Corr 
-##  country (Intercept)                   0.300861 0.54851       
-##          accel_ben_rank_direct_funding 0.007982 0.08934  -1.00
-## Number of obs: 15981, groups:  country, 82
-## 
-## Fixed effects:
-##                               Estimate Std. Error z value Pr(>|z|)    
-## (Intercept)                   -1.45326    0.07722 -18.821  < 2e-16 ***
-## accel_ben_rank_direct_funding -0.19333    0.06321  -3.059  0.00222 ** 
-## ---
-## Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
-## 
-## Correlation of Fixed Effects:
-##             (Intr)
-## accl_bn_r__ -0.171
-## convergence code: 0
-## boundary (singular) fit: see ?isSingular
-\end{verbatim}
+\caption{\label{tab:unnamed-chunk-18}Table 6: Effect of congruency of venture attention and institutional level (Credit gaps) of financial capital}
+\centering
+\begin{tabular}[t]{l|l|l|l|l|l|l|l|l}
+\hline
+\multicolumn{1}{c|}{\em{ }} & \multicolumn{4}{c|}{\em{Model w/ controls}} & \multicolumn{4}{c}{\em{Model w/o controls}} \\
+\cline{2-5} \cline{6-9}
+  & \$b\$ & SE & \$z\$ & \$p\$ & \$b\$ & SE & \$z\$ & \$p\$\\
+\hline
+Intercept & -1.46 & 0.13 & -11.62 & 0.000 & -1.37 & 0.13 & -10.93 & 0.000\\
+\hline
+AFC & -0.20 & 0.10 & -1.91 & 0.056 & -0.21 & 0.10 & -1.99 & 0.047\\
+\hline
+\multicolumn{9}{l}{\textbf{Control variables}}\\
+\hline
+\hspace{1em}Domestic Credit Gaps & 0.00 & 0.00 & -0.57 & 0.572 & 0.00 & 0.00 & -0.60 & 0.550\\
+\hline
+\hspace{1em}AFCxDomestic Credit Gaps & 0.01 & 0.01 & 1.30 & 0.192 & 0.00 & 0.00 & 0.15 & 0.882\\
+\hline
+HCI & 0.25 & 0.06 & 4.24 & 0.000 & NA & NA & NA & NA\\
+\hline
+GC & 0.00 & 0.00 & 0.08 & 0.938 & NA & NA & NA & NA\\
+\hline
+\end{tabular}
+\end{table}
 
-\begin{verbatim}
-## Generalized linear mixed model fit by maximum likelihood (Laplace
-##   Approximation) [glmerMod]
-##  Family: binomial  ( logit )
-## Formula: 
-## participated ~ accel_ben_rank_direct_funding * EOSQ425 + (accel_ben_rank_direct_funding |  
-##     country)
-##    Data: gali_joined
-## 
-##      AIC      BIC   logLik deviance df.resid 
-##  14562.1  14615.8  -7274.1  14548.1    15720 
-## 
-## Scaled residuals: 
-##     Min      1Q  Median      3Q     Max 
-## -1.0463 -0.4908 -0.4210 -0.3513  3.0165 
-## 
-## Random effects:
-##  Groups  Name                          Variance Std.Dev. Corr 
-##  country (Intercept)                   0.287438 0.53613       
-##          accel_ben_rank_direct_funding 0.009936 0.09968  -1.00
-## Number of obs: 15727, groups:  country, 73
-## 
-## Fixed effects:
-##                                        Estimate Std. Error z value Pr(>|z|)   
-## (Intercept)                           -1.349694   0.434021  -3.110  0.00187 **
-## accel_ben_rank_direct_funding         -0.210801   0.285396  -0.739  0.46013   
-## EOSQ425                               -0.021755   0.112408  -0.194  0.84654   
-## accel_ben_rank_direct_funding:EOSQ425  0.003382   0.065751   0.051  0.95898   
-## ---
-## Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
-## 
-## Correlation of Fixed Effects:
-##             (Intr) ac____ EOSQ42
-## accl_bn_r__ -0.246              
-## EOSQ425     -0.983  0.246       
-## a____:EOSQ4  0.280 -0.974 -0.289
-## convergence code: 0
-## boundary (singular) fit: see ?isSingular
-\end{verbatim}
+\begin{table}
 
-\begin{verbatim}
-## Generalized linear mixed model fit by maximum likelihood (Laplace
-##   Approximation) [glmerMod]
-##  Family: binomial  ( logit )
-## Formula: 
-## participated ~ accel_ben_rank_direct_funding * EOSQ089 + (accel_ben_rank_direct_funding |  
-##     country)
-##    Data: gali_joined
-## 
-##      AIC      BIC   logLik deviance df.resid 
-##  14561.6  14615.2  -7273.8  14547.6    15720 
-## 
-## Scaled residuals: 
-##     Min      1Q  Median      3Q     Max 
-## -1.0482 -0.4904 -0.4209 -0.3510  3.0323 
-## 
-## Random effects:
-##  Groups  Name                          Variance Std.Dev. Corr 
-##  country (Intercept)                   0.284084 0.53299       
-##          accel_ben_rank_direct_funding 0.009676 0.09837  -1.00
-## Number of obs: 15727, groups:  country, 73
-## 
-## Fixed effects:
-##                                       Estimate Std. Error z value Pr(>|z|)    
-## (Intercept)                           -1.21998    0.28033  -4.352 1.35e-05 ***
-## accel_ben_rank_direct_funding         -0.24283    0.19650  -1.236    0.217    
-## EOSQ089                               -0.07084    0.09006  -0.787    0.432    
-## accel_ben_rank_direct_funding:EOSQ089  0.01463    0.05184   0.282    0.778    
-## ---
-## Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
-## 
-## Correlation of Fixed Effects:
-##             (Intr) ac____ EOSQ08
-## accl_bn_r__ -0.232              
-## EOSQ089     -0.960  0.230       
-## a____:EOSQ0  0.281 -0.944 -0.300
-## convergence code: 0
-## boundary (singular) fit: see ?isSingular
-\end{verbatim}
+\caption{\label{tab:unnamed-chunk-18}Table 7: Effect of attention to social capital}
+\centering
+\begin{tabular}[t]{l|l|l|l|l|l|l|l|l}
+\hline
+\multicolumn{1}{c|}{\em{ }} & \multicolumn{4}{c|}{\em{Model w/ controls}} & \multicolumn{4}{c}{\em{Model w/o controls}} \\
+\cline{2-5} \cline{6-9}
+  & \$b\$ & SE & \$z\$ & \$p\$ & \$b\$ & SE & \$z\$ & \$p\$\\
+\hline
+Intercept & -1.53 & 0.08 & -19.37 & 0.000 & -1.45 & 0.08 & -18.62 & 0.000\\
+\hline
+Attention to Social capital & 0.12 & 0.07 & 1.79 & 0.073 & 0.11 & 0.07 & 1.69 & 0.091\\
+\hline
+\multicolumn{9}{l}{\textbf{Control variables}}\\
+\hline
+\hspace{1em}HCI & 0.01 & 0.01 & 1.29 & 0.197 & NA & NA & NA & NA\\
+\hline
+\hspace{1em}GC & 0.25 & 0.06 & 4.42 & 0.000 & NA & NA & NA & NA\\
+\hline
+\end{tabular}
+\end{table}
 
-\begin{verbatim}
-## Generalized linear mixed model fit by maximum likelihood (Laplace
-##   Approximation) [glmerMod]
-##  Family: binomial  ( logit )
-## Formula: participated ~ accel_ben_rank_direct_funding * DOMCREDITGDP +  
-##     (accel_ben_rank_direct_funding | country)
-##    Data: gali_joined
-## 
-##      AIC      BIC   logLik deviance df.resid 
-##  14561.8  14615.5  -7273.9  14547.8    15720 
-## 
-## Scaled residuals: 
-##     Min      1Q  Median      3Q     Max 
-## -1.0466 -0.4909 -0.4213 -0.3514  3.0629 
-## 
-## Random effects:
-##  Groups  Name                          Variance Std.Dev. Corr 
-##  country (Intercept)                   0.289392 0.53795       
-##          accel_ben_rank_direct_funding 0.009926 0.09963  -1.00
-## Number of obs: 15727, groups:  country, 73
-## 
-## Fixed effects:
-##                                              Estimate Std. Error z value
-## (Intercept)                                -1.3735020  0.1256629 -10.930
-## accel_ben_rank_direct_funding              -0.2051438  0.1031016  -1.990
-## DOMCREDITGDP                               -0.0010317  0.0017273  -0.597
-## accel_ben_rank_direct_funding:DOMCREDITGDP  0.0001439  0.0009667   0.149
-##                                            Pr(>|z|)    
-## (Intercept)                                  <2e-16 ***
-## accel_ben_rank_direct_funding                0.0466 *  
-## DOMCREDITGDP                                 0.5503    
-## accel_ben_rank_direct_funding:DOMCREDITGDP   0.8817    
-## ---
-## Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
-## 
-## Correlation of Fixed Effects:
-##             (Intr) ac____ DOMCRE
-## accl_bn_r__ -0.193              
-## DOMCREDITGD -0.778  0.159       
-## a____:DOMCR  0.233 -0.779 -0.313
-## convergence code: 0
-## boundary (singular) fit: see ?isSingular
-\end{verbatim}
+\begin{table}
 
-\begin{verbatim}
-## Linear mixed model fit by maximum likelihood  ['lmerMod']
-## Formula: capital_raised_tot ~ +(accel_ben_rank_direct_funding | country)
-##    Data: gali_joined
-## 
-##       AIC       BIC    logLik  deviance  df.resid 
-##  541645.1  541683.5 -270817.5  541635.1     15976 
-## 
-## Scaled residuals: 
-##     Min      1Q  Median      3Q     Max 
-##  -0.316  -0.040  -0.029  -0.018 120.803 
-## 
-## Random effects:
-##  Groups   Name                          Variance  Std.Dev. Corr
-##  country  (Intercept)                   1.187e+11  344600      
-##           accel_ben_rank_direct_funding 2.332e+09   48286  1.00
-##  Residual                               3.062e+13 5533830      
-## Number of obs: 15981, groups:  country, 82
-## 
-## Fixed effects:
-##             Estimate Std. Error t value
-## (Intercept)   226024      79869    2.83
-## convergence code: 0
-## boundary (singular) fit: see ?isSingular
-\end{verbatim}
-
-\begin{verbatim}
-## Linear mixed model fit by maximum likelihood  ['lmerMod']
-## Formula: capital_raised_tot ~ accel_ben_rank_direct_funding * EOSQ425 +  
-##     (accel_ben_rank_direct_funding | country)
-##    Data: gali_joined
-## 
-##       AIC       BIC    logLik  deviance  df.resid 
-##  533280.8  533342.1 -266632.4  533264.8     15719 
-## 
-## Scaled residuals: 
-##     Min      1Q  Median      3Q     Max 
-##  -0.311  -0.041  -0.028  -0.016 119.888 
-## 
-## Random effects:
-##  Groups   Name                          Variance  Std.Dev. Corr
-##  country  (Intercept)                   1.247e+11  353102      
-##           accel_ben_rank_direct_funding 2.606e+09   51053  1.00
-##  Residual                               3.109e+13 5575911      
-## Number of obs: 15727, groups:  country, 73
-## 
-## Fixed effects:
-##                                       Estimate Std. Error t value
-## (Intercept)                              -4885     444377  -0.011
-## accel_ben_rank_direct_funding          -191024     590675  -0.323
-## EOSQ425                                  59478     112868   0.527
-## accel_ben_rank_direct_funding:EOSQ425    31388     134942   0.233
-## 
-## Correlation of Fixed Effects:
-##             (Intr) ac____ EOSQ42
-## accl_bn_r__  0.106              
-## EOSQ425     -0.982 -0.103       
-## a____:EOSQ4 -0.111 -0.975  0.111
-## convergence code: 0
-## boundary (singular) fit: see ?isSingular
-\end{verbatim}
-
-\begin{verbatim}
-## Linear mixed model fit by maximum likelihood  ['lmerMod']
-## Formula: capital_raised_tot ~ accel_ben_rank_direct_funding * EOSQ089 +  
-##     (accel_ben_rank_direct_funding | country)
-##    Data: gali_joined
-## 
-##       AIC       BIC    logLik  deviance  df.resid 
-##  533280.7  533342.0 -266632.3  533264.7     15719 
-## 
-## Scaled residuals: 
-##     Min      1Q  Median      3Q     Max 
-##  -0.310  -0.041  -0.028  -0.015 119.888 
-## 
-## Random effects:
-##  Groups   Name                          Variance  Std.Dev. Corr
-##  country  (Intercept)                   1.245e+11  352894      
-##           accel_ben_rank_direct_funding 2.412e+09   49109  1.00
-##  Residual                               3.109e+13 5575889      
-## Number of obs: 15727, groups:  country, 73
-## 
-## Fixed effects:
-##                                       Estimate Std. Error t value
-## (Intercept)                              66014     285162   0.231
-## accel_ben_rank_direct_funding          -205433     401458  -0.512
-## EOSQ089                                  51858      88843   0.584
-## accel_ben_rank_direct_funding:EOSQ089    41162     104375   0.394
-## 
-## Correlation of Fixed Effects:
-##             (Intr) ac____ EOSQ08
-## accl_bn_r__  0.083              
-## EOSQ089     -0.957 -0.080       
-## a____:EOSQ0 -0.094 -0.944  0.098
-## convergence code: 0
-## boundary (singular) fit: see ?isSingular
-\end{verbatim}
-
-\begin{verbatim}
-## Linear mixed model fit by maximum likelihood  ['lmerMod']
-## Formula: capital_raised_tot ~ accel_ben_rank_direct_funding * DOMCREDITGDP +  
-##     (accel_ben_rank_direct_funding | country)
-##    Data: gali_joined
-## 
-##       AIC       BIC    logLik  deviance  df.resid 
-##  533280.9  533342.2 -266632.4  533264.9     15719 
-## 
-## Scaled residuals: 
-##     Min      1Q  Median      3Q     Max 
-##  -0.310  -0.041  -0.028  -0.016 119.887 
-## 
-## Random effects:
-##  Groups   Name                          Variance  Std.Dev. Corr
-##  country  (Intercept)                   1.245e+11  352820      
-##           accel_ben_rank_direct_funding 2.381e+09   48795  1.00
-##  Residual                               3.109e+13 5575926      
-## Number of obs: 15727, groups:  country, 73
-## 
-## Fixed effects:
-##                                             Estimate Std. Error t value
-## (Intercept)                                 190993.0   128015.3   1.492
-## accel_ben_rank_direct_funding              -121351.9   210078.0  -0.578
-## DOMCREDITGDP                                   572.9     1620.3   0.354
-## accel_ben_rank_direct_funding:DOMCREDITGDP     768.4     1952.7   0.393
-## 
-## Correlation of Fixed Effects:
-##             (Intr) ac____ DOMCRE
-## accl_bn_r__  0.058              
-## DOMCREDITGD -0.761 -0.043       
-## a____:DOMCR -0.062 -0.776  0.085
-## convergence code: 0
-## boundary (singular) fit: see ?isSingular
-\end{verbatim}
-
-\#Mixed model analysis - Social capital
-
-\begin{verbatim}
-##                          Estimate  Std. Error   t value
-## (Intercept)            0.20316446 0.012552069 16.185735
-## accel_ben_rank_network 0.01831386 0.009581619  1.911353
-\end{verbatim}
-
-\begin{verbatim}
-##                                     Estimate Std. Error      t value
-## (Intercept)                     3.133837e-01 0.06847055  4.576912615
-## accel_ben_rank_network          1.746818e-02 0.05079577  0.343890367
-## EOSQ109                        -2.763492e-02 0.01732516 -1.595074599
-## accel_ben_rank_network:EOSQ109 -4.430267e-05 0.01131854 -0.003914168
-\end{verbatim}
-
-\begin{verbatim}
-##                          Estimate Std. Error   t value
-## (Intercept)            0.57925930 0.04337800 13.353759
-## accel_ben_rank_network 0.06485941 0.04797524  1.351935
-\end{verbatim}
-
-\begin{verbatim}
-##                                  Estimate Std. Error   t value
-## (Intercept)                    -0.2751093 0.21194630 -1.298014
-## accel_ben_rank_network         -0.6038282 0.24619417 -2.452650
-## EOSQ109                         0.2185398 0.05339006  4.093266
-## accel_ben_rank_network:EOSQ109  0.1708510 0.05804559  2.943393
-\end{verbatim}
-
-\hypertarget{data-and-methods}{%
-\section{Data and Methods}\label{data-and-methods}}
+\caption{\label{tab:unnamed-chunk-18}Table 8: Effect of congruency of venture attention and institutional level of social capital}
+\centering
+\begin{tabular}[t]{l|l|l|l|l|l|l|l|l}
+\hline
+\multicolumn{1}{c|}{\em{ }} & \multicolumn{4}{c|}{\em{Model w/ controls}} & \multicolumn{4}{c}{\em{Model w/o controls}} \\
+\cline{2-5} \cline{6-9}
+  & \$b\$ & SE & \$z\$ & \$p\$ & \$b\$ & SE & \$z\$ & \$p\$\\
+\hline
+Intercept & -0.89 & 0.41 & -2.16 & 0.031 & -0.78 & 0.42 & -1.87 & 0.061\\
+\hline
+ASC & 0.06 & 0.35 & 0.19 & 0.852 & 0.06 & 0.35 & 0.18 & 0.860\\
+\hline
+\multicolumn{9}{l}{\textbf{Control variables}}\\
+\hline
+\hspace{1em}State of cluster development & -0.16 & 0.10 & -1.52 & 0.128 & -0.17 & 0.11 & -1.56 & 0.119\\
+\hline
+\hspace{1em}ASCxState of cluster development & 0.01 & 0.01 & 1.22 & 0.223 & 0.01 & 0.08 & 0.15 & 0.883\\
+\hline
+HCI & 0.25 & 0.06 & 4.30 & 0.000 & NA & NA & NA & NA\\
+\hline
+GC & 0.01 & 0.08 & 0.16 & 0.876 & NA & NA & NA & NA\\
+\hline
+\end{tabular}
+\end{table}
 

### 2021-03-13 Manuscript.Rmd
Figured out kableextra issue and added more to the manuscript

@@
 footnotelist      : no
-linenumbers       : yes
+linenumbers       : no
 mask              : no
@@
 set.seed(42)
-knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
+knitr::opts_chunk$set(cache.extra = knitr::rand_seed, warning = F, message = F, fig.pos = "!H", out.extra = "")
 #options(knitr.table.format = "latex")
@@
 (19)	*Revenue ~  AFC + (AFC | Country)*
-(20)	*Revenue ~  AFC + (AFC x Financing of SMEs| Country)*   
-(21)	*Revenue ~  AFC + (AFC x VC availability | Country)*   
-(22)	*Revenue ~  AFC + (AFC x Domestic Credit Gaps | Country)*   
+(20)	*Revenue ~  AFC + (AFC x Financing of SMEs| Country) + (AFC x VC availability | Country) + (AFC x Domestic Credit Gaps | Country)*   
 (23)	*Revenue ~  ASC + (ASC | Country)*   
@@
 library(kableExtra)
-
 ```
@@
 
+```{r message=FALSE, warning=FALSE, include=FALSE}
 #CGI data
-```{r message=FALSE, warning=FALSE, include=FALSE}
 gci <- import("Data/GCI_2018.xlsx")
@@
 
+```{r echo=FALSE, fig.height=10, fig.width=10, message=FALSE, warning=FALSE}
 #Plotting all countries along the 3 dimensions
-
-```{r echo=FALSE, fig.height=10, fig.width=10, message=FALSE, warning=FALSE}
 
@@
     , "$t$" = "t value"
-    , "$p$" = "Pr(>|t|)"
   ) %>%
@@
   ) %>%
-  select(Effect, `$b$`, `SE`, `$t$`, `$p$`)}
+  select(Effect, `$b$`, `SE`, `$t$`)}
 
@@
 rownames(hc0_c) <- c("Intercept","Attention to Human capital(AHC)", "HCI", "GC")
-#rownames(hc1) <- c("Intercept","AHC", "Ease of finding skilled employees", "AHCxEase of finding skilled employees")
 rownames(hc1_c) <- c("Intercept","AHC", "Ease of finding skilled employees", "AHCxEase of finding skilled employees", "HCI", "GC")
-#rownames(fc0) <- c("Intercept","Attention to Financial capital")
 rownames(fc0_c) <- c("Intercept","Attention to Financial capital", "HCI", "GC")
-#rownames(fc1) <- c("Intercept","AFC", "Financing of SMEs", "AFCxFinancing of SMEs")
 rownames(fc1_c) <- c("Intercept","AFC", "Financing of SMEs", "AFCxFinancing of SMEs", "HCI", "GC")
-#rownames(fc2) <- c("Intercept","AFC", "VC Availability", "AFCxVC Availability")
 rownames(fc2_c) <- c("Intercept","AFC", "VC Availability", "AFCxVC Availability", "HCI", "GC")
-#rownames(fc3) <- c("Intercept","AFC", "Domestic Credit Gaps", "AFCxDomestic Credit Gaps")
 rownames(fc3_c) <- c("Intercept","AFC", "Domestic Credit Gaps", "AFCxDomestic Credit Gaps", "HCI", "GC")
-#rownames(sc0) <- c("Intercept","Attention to Social capital")
 rownames(sc0_c) <- c("Intercept","Attention to Social capital", "HCI", "GC")
-#rownames(sc1) <- c("Intercept","ASC", "State of cluster development","ASCxState of cluster development")
 rownames(sc1_c) <- c("Intercept","ASC", "State of cluster development","ASCxState of cluster development", "HCI", "GC")
@@
 
-kable(hc_zero, booktabs = T, caption = "Table 1: Effect of attention to human capital", escape = F) %>%
+kable(hc_zero, escape = F, caption = "Effect of attention to human capital") %>%
   add_header_above(c(" ", "Model w/ controls" = 4, "Model w/o controls" = 4), italic = T) %>%
@@
 
-kable(hc_one, caption = "Table 2: Effect of congruency of venture attention and institutional level of human capital", format = "latex") %>%
+kable(hc_one, escape = F, caption = "Effect of congruency of venture attention and institutional level of human capital", format = "latex") %>%
+  add_header_above(c(" ", "Model w/ controls" = 4, "Model w/o controls" = 4), italic = T) %>%
+  kable_styling(latex_options = c("repeat_header")) %>%
+  pack_rows("Control variables", 5, 6, latex_gap_space = "2em")
+
+kbl(fc_zero, escape = F, caption = "Effect of attention to financial capital") %>%
   add_header_above(c(" ", "Model w/ controls" = 4, "Model w/o controls" = 4), italic = T) %>%
@@
 
-kbl(fc_zero, caption = "Table 3: Effect of attention to financial capital") %>%
+kbl(fc_one, escape = F, caption = "Effect of congruency of venture attention and institutional level (SME financing) of financial capital") %>%
+  add_header_above(c(" ", "Model w/ controls" = 4, "Model w/o controls" = 4), italic = T) %>%
+  kable_styling(latex_options = c("repeat_header")) %>%
+  pack_rows("Control variables", 5, 6, latex_gap_space = "2em")
+
+kbl(fc_two, escape = F, caption = "Effect of congruency of venture attention and institutional level (VC) of financial capital") %>%
+  add_header_above(c(" ", "Model w/ controls" = 4, "Model w/o controls" = 4), italic = T) %>%
+  kable_styling(latex_options = c("repeat_header")) %>%
+  pack_rows("Control variables", 5, 6, latex_gap_space = "2em")
+
+kbl(fc_three, escape = F, caption = "Effect of congruency of venture attention and institutional level (Credit gaps) of financial capital") %>%
+  add_header_above(c(" ", "Model w/ controls" = 4, "Model w/o controls" = 4), italic = T) %>%
+  kable_styling(latex_options = c("repeat_header")) %>%
+  pack_rows("Control variables", 5, 6, latex_gap_space = "2em")
+
+kbl(sc_zero, escape = F, caption = "Effect of attention to social capital") %>%
   add_header_above(c(" ", "Model w/ controls" = 4, "Model w/o controls" = 4), italic = T) %>%
@@
 
-kbl(fc_one, caption = "Table 4: Effect of congruency of venture attention and institutional level (SME financing) of financial capital") %>%
+kbl(sc_one, escape = F, caption = "Effect of congruency of venture attention and institutional level of social capital") %>%
   add_header_above(c(" ", "Model w/ controls" = 4, "Model w/o controls" = 4), italic = T) %>%
   kable_styling(latex_options = c("repeat_header")) %>%
-  pack_rows("Control variables", 3, 4, latex_gap_space = "2em")
-
-kbl(fc_two, caption = "Table 5: Effect of congruency of venture attention and institutional level (VC) of financial capital") %>%
-  add_header_above(c(" ", "Model w/ controls" = 4, "Model w/o controls" = 4), italic = T) %>%
-  kable_styling(latex_options = c("repeat_header")) %>%
-  pack_rows("Control variables", 3, 4, latex_gap_space = "2em")
-
-kbl(fc_three, caption = "Table 6: Effect of congruency of venture attention and institutional level (Credit gaps) of financial capital") %>%
-  add_header_above(c(" ", "Model w/ controls" = 4, "Model w/o controls" = 4), italic = T) %>%
-  kable_styling(latex_options = c("repeat_header")) %>%
-  pack_rows("Control variables", 3, 4, latex_gap_space = "2em")
-
-kbl(sc_zero, caption = "Table 7: Effect of attention to social capital") %>%
-  add_header_above(c(" ", "Model w/ controls" = 4, "Model w/o controls" = 4), italic = T) %>%
-  kable_styling(latex_options = c("repeat_header")) %>%
-  pack_rows("Control variables", 3, 4, latex_gap_space = "2em")
-
-kbl(sc_one, caption = "Table 8: Effect of congruency of venture attention and institutional level of social capital") %>%
-  add_header_above(c(" ", "Model w/ controls" = 4, "Model w/o controls" = 4), italic = T) %>%
-  kable_styling(latex_options = c("repeat_header")) %>%
-  pack_rows("Control variables", 3, 4, latex_gap_space = "2em")
-
-#kable(sc1_c[,-1], escape = FALSE, caption = "Table 16: Effect of congruency of venture attention and institutional level of social capital - Model with controls")
+  pack_rows("Control variables", 5, 6, latex_gap_space = "2em")
 
@@
 
-```{r eval=FALSE, message=FALSE, warning=FALSE, include=FALSE}
+```{r echo=FALSE, message=FALSE, warning=FALSE}
 #Outcome: Resource acquistion 
@@
 fit11sc <- lmer(equity_sources_tot ~ accel_ben_rank_network*EOSQ109 + (accel_ben_rank_network | country), data = gali_joined, REML = F)
+```
+
+```{r echo=FALSE}
+#summary tables
 
@@
 
-#kable(hc00[,-1], escape = FALSE)
-#kable(hc11[,-1], escape = FALSE)
-#kable(fc00[,-1], escape = FALSE)
-#kable(fc11[,-1], escape = FALSE)
-#kable(fc22[,-1], escape = FALSE)
-#kable(fc33[,-1], escape = FALSE)
-#kable(sc00[,-1], escape = FALSE)
-#kable(sc11[,-1], escape = FALSE, caption = "This is the table caption")
+hc <- cbindX(hc11[,-1], hc00[,-1]) 
+fc <- cbindX(fc11[,-1], fc00[,-1]) 
+sc <- cbindX(sc11[,-1], sc00[,-1])
+
+```
+
+```{r echo=FALSE}
+#Print summaries
+
+kable(hc, escape = F, caption = "Effect on total employees") %>%
+  add_header_above(c(" ", "Congruence" = 3, "AHC only" = 3), italic = T)
+
+kable(fc, escape = F, caption = "Effect on capital raised") %>%
+  add_header_above(c(" ", "Congruence" = 3, "AFC only" = 3), italic = T)
+
+kable(fc22[,-1], escape = F, caption = "Effect on capital raised")
+
+kable(fc33[,-1], escape = F, caption = "Effect on capital raised")
+
+kable(sc, escape = F, caption = "Effect on sources of capital") %>%
+  add_header_above(c(" ", "Congruence" = 3, "ASC only" = 3), italic =T)
+
+```
+
+```{r}
+#Outcome: Revenue
+library(lme4)
+
+fit0_hc <- lmer(revenue_tot ~  accel_ben_rank_business_skills + (accel_ben_rank_business_skills|country), data = gali_joined, REML = F)
+
+fit1_hc <- lmer(revenue_tot ~  accel_ben_rank_business_skills*EOSQ403 + (accel_ben_rank_business_skills|country), data = gali_joined, REML = F)
+
+fit0_fc <- lmer(revenue_tot ~ + accel_ben_rank_direct_funding+ (accel_ben_rank_direct_funding|country), data = gali_joined, REML = F)
+
+fit1_fc <- lmer(revenue_tot ~ + accel_ben_rank_direct_funding*EOSQ425+ accel_ben_rank_direct_funding*EOSQ089 + accel_ben_rank_direct_funding*DOMCREDITGDP + (accel_ben_rank_direct_funding|country), data = gali_joined, REML = F)
+
+fit0_sc <- lmer(revenue_tot ~ accel_ben_rank_network + (accel_ben_rank_network |country), data = gali_joined, REML = F)
+
+fit1_sc <- lmer(revenue_tot ~ accel_ben_rank_network*EOSQ109 + (accel_ben_rank_network | country), data = gali_joined, REML = F)
+
+```
+
+```{r}
+#summary tables
+
+hc_0 <- summary_table(summary(fit0_hc))
+hc_1 <- summary_table(summary(fit1_hc))
+fc_0 <- summary_table(summary(fit0_fc))
+fc_1 <- summary_table(summary(fit1_fc))
+sc_0 <- summary_table(summary(fit0_sc))
+sc_1 <- summary_table(summary(fit1_sc))
+
+rownames(hc_0) <- c("Intercept","Attention to Human capital")
+rownames(hc_1) <- c("Intercept","AHC", "Ease of finding skilled employees", "AHCxEase of finding skilled employees")
+rownames(fc_0) <- c("Intercept","Attention to Financial capital")
+rownames(fc_1) <- c("Intercept","AFC", "Financing of SMEs", "VC Availability", "Domestic Credit Gaps", "AFCxFinancing of SMEs", "AFCxVC Availability", "AFCxDomestic Credit Gaps")
+rownames(sc_0) <- c("Intercept","Attention to Social capital")
+rownames(sc_1) <- c("Intercept","ASC", "State of cluster development","ASCxState of cluster development")
+
+hc_r <- cbindX(hc_1[,-1], hc_0[,-1]) 
+fc_r <- cbindX(fc_1[,-1], fc_0[,-1]) 
+sc_r <- cbindX(sc_1[,-1], sc_0[,-1])
+
+```
+
+```{r}
+#Print summaries
+
+kable(hc_r, escape = F, caption = "Effect on revenues", digits = 0) %>%
+  add_header_above(c(" ", "Congruence" = 3, "AHC only" = 3), italic = T) %>%
+kable_styling(font_size = 8)
+
+kable(fc_r, escape = F, caption = "Effect on revenues", digits = 0) %>%
+  add_header_above(c(" ", "Congruence" = 3, "AFC only" = 3), italic = T) %>%
+kable_styling(font_size = 8)
+
+kable(sc_r, escape = F, caption = "Effect on revenues", digits = 0) %>%
+  add_header_above(c(" ", "Congruence" = 3, "ASC only" = 3), italic =T) %>%
+kable_styling(font_size = 8)
 

### 2021-03-13 Manuscript.tex
Figured out kableextra issue and added more to the manuscript

@@
 \makeatother
-\usepackage{lineno}
-
-\linenumbers
 \usepackage{csquotes}
@@
 
-\#CGI data
+\begin{figure}[!H]
+\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-5-1} \caption{ }\label{fig:unnamed-chunk-5-1}
+\end{figure}
+\begin{figure}[!H]
+\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-5-2} \caption{ }\label{fig:unnamed-chunk-5-2}
+\end{figure}
 
-\#Plotting all countries along the 3 dimensions
+\begin{figure}[!H]
+\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-7-1} \caption{ }\label{fig:unnamed-chunk-7-1}
+\end{figure}
+\begin{figure}[!H]
+\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-7-2} \caption{ }\label{fig:unnamed-chunk-7-2}
+\end{figure}
 
-\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-5-1.pdf} \includegraphics{Manuscript_files/figure-latex/unnamed-chunk-5-2.pdf}
-
-\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-7-1.pdf} \includegraphics{Manuscript_files/figure-latex/unnamed-chunk-7-2.pdf}
-
-\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-12-1.pdf} \includegraphics{Manuscript_files/figure-latex/unnamed-chunk-12-2.pdf}
+\begin{figure}[!H]
+\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-12-1} \caption{ }\label{fig:unnamed-chunk-12-1}
+\end{figure}
+\begin{figure}[!H]
+\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-12-2} \caption{ }\label{fig:unnamed-chunk-12-2}
+\end{figure}
 
@@
 
-\caption{\label{tab:unnamed-chunk-18}Table 1: Effect of attention to human capital}
-\centering
-\begin{tabular}[t]{lllllllll}
-\toprule
-\multicolumn{1}{c}{\em{ }} & \multicolumn{4}{c}{\em{Model w/ controls}} & \multicolumn{4}{c}{\em{Model w/o controls}} \\
-\cmidrule(l{3pt}r{3pt}){2-5} \cmidrule(l{3pt}r{3pt}){6-9}
-  & $b$ & SE & $z$ & $p$ & $b$ & SE & $z$ & $p$\\
-\midrule
-Intercept & -1.54 & 0.08 & -19.82 & 0.000 & -1.46 & 0.08 & -19.18 & 0.000\\
-Attention to Human capital(AHC) & 0.09 & 0.07 & 1.24 & 0.215 & 0.11 & 0.07 & 1.54 & 0.123\\
-\addlinespace[2em]
-\multicolumn{9}{l}{\textbf{Control variables}}\\
-\hspace{1em}HCI & 0.01 & 0.01 & 1.46 & 0.144 & NA & NA & NA & NA\\
-\hspace{1em}GC & 0.24 & 0.06 & 4.17 & 0.000 & NA & NA & NA & NA\\
-\bottomrule
-\end{tabular}
-\end{table}
-
-\begin{table}
-
-\caption{\label{tab:unnamed-chunk-18}Table 2: Effect of congruency of venture attention and institutional level of human capital}
+\caption{\label{tab:unnamed-chunk-18}Effect of attention to human capital}
 \centering
@@
 \cline{2-5} \cline{6-9}
-  & \$b\$ & SE & \$z\$ & \$p\$ & \$b\$ & SE & \$z\$ & \$p\$\\
+  & $b$ & SE & $z$ & $p$ & $b$ & SE & $z$ & $p$\\
 \hline
-Intercept & -0.94 & 0.53 & -1.80 & 0.073 & -0.85 & 0.53 & -1.61 & 0.108\\
+Intercept & -1.54 & 0.08 & -19.82 & 0.000 & -1.46 & 0.08 & -19.18 & 0.000\\
 \hline
-AHC & 0.90 & 0.45 & 2.01 & 0.044 & 0.92 & 0.45 & 2.05 & 0.040\\
+Attention to Human capital(AHC) & 0.09 & 0.07 & 1.24 & 0.215 & 0.11 & 0.07 & 1.54 & 0.123\\
 \hline
@@
 \hline
-\hspace{1em}Ease of finding skilled employees & -0.13 & 0.12 & -1.11 & 0.269 & -0.14 & 0.12 & -1.14 & 0.253\\
+\hspace{1em}HCI & 0.01 & 0.01 & 1.46 & 0.144 & NA & NA & NA & NA\\
 \hline
-\hspace{1em}AHCxEase of finding skilled employees & 0.01 & 0.01 & 1.37 & 0.171 & -0.17 & 0.10 & -1.79 & 0.074\\
-\hline
-HCI & 0.24 & 0.06 & 4.06 & 0.000 & NA & NA & NA & NA\\
-\hline
-GC & -0.17 & 0.10 & -1.80 & 0.073 & NA & NA & NA & NA\\
+\hspace{1em}GC & 0.24 & 0.06 & 4.17 & 0.000 & NA & NA & NA & NA\\
 \hline
@@
 
-\caption{\label{tab:unnamed-chunk-18}Table 3: Effect of attention to financial capital}
+\caption{\label{tab:unnamed-chunk-18}Effect of congruency of venture attention and institutional level of human capital}
 \centering
@@
 \cline{2-5} \cline{6-9}
-  & \$b\$ & SE & \$z\$ & \$p\$ & \$b\$ & SE & \$z\$ & \$p\$\\
+  & $b$ & SE & $z$ & $p$ & $b$ & SE & $z$ & $p$\\
+\hline
+Intercept & -0.94 & 0.53 & -1.80 & 0.073 & -0.85 & 0.53 & -1.61 & 0.108\\
+\hline
+AHC & 0.90 & 0.45 & 2.01 & 0.044 & 0.92 & 0.45 & 2.05 & 0.040\\
+\hline
+Ease of finding skilled employees & -0.13 & 0.12 & -1.11 & 0.269 & -0.14 & 0.12 & -1.14 & 0.253\\
+\hline
+AHCxEase of finding skilled employees & 0.01 & 0.01 & 1.37 & 0.171 & -0.17 & 0.10 & -1.79 & 0.074\\
+\hline
+\multicolumn{9}{l}{\textbf{Control variables}}\\
+\hline
+\hspace{1em}HCI & 0.24 & 0.06 & 4.06 & 0.000 & NA & NA & NA & NA\\
+\hline
+\hspace{1em}GC & -0.17 & 0.10 & -1.80 & 0.073 & NA & NA & NA & NA\\
+\hline
+\end{tabular}
+\end{table}
+
+\begin{table}
+
+\caption{\label{tab:unnamed-chunk-18}Effect of attention to financial capital}
+\centering
+\begin{tabular}[t]{l|l|l|l|l|l|l|l|l}
+\hline
+\multicolumn{1}{c|}{\em{ }} & \multicolumn{4}{c|}{\em{Model w/ controls}} & \multicolumn{4}{c}{\em{Model w/o controls}} \\
+\cline{2-5} \cline{6-9}
+  & $b$ & SE & $z$ & $p$ & $b$ & SE & $z$ & $p$\\
 \hline
@@
 
-\caption{\label{tab:unnamed-chunk-18}Table 4: Effect of congruency of venture attention and institutional level (SME financing) of financial capital}
+\caption{\label{tab:unnamed-chunk-18}Effect of congruency of venture attention and institutional level (SME financing) of financial capital}
 \centering
@@
 \cline{2-5} \cline{6-9}
-  & \$b\$ & SE & \$z\$ & \$p\$ & \$b\$ & SE & \$z\$ & \$p\$\\
+  & $b$ & SE & $z$ & $p$ & $b$ & SE & $z$ & $p$\\
 \hline
@@
 \hline
+Financing of SMEs & -0.02 & 0.11 & -0.20 & 0.845 & -0.02 & 0.11 & -0.19 & 0.847\\
+\hline
+AFCxFinancing of SMEs & 0.01 & 0.01 & 1.30 & 0.193 & 0.00 & 0.07 & 0.05 & 0.959\\
+\hline
 \multicolumn{9}{l}{\textbf{Control variables}}\\
 \hline
-\hspace{1em}Financing of SMEs & -0.02 & 0.11 & -0.20 & 0.845 & -0.02 & 0.11 & -0.19 & 0.847\\
+\hspace{1em}HCI & 0.25 & 0.06 & 4.25 & 0.000 & NA & NA & NA & NA\\
 \hline
-\hspace{1em}AFCxFinancing of SMEs & 0.01 & 0.01 & 1.30 & 0.193 & 0.00 & 0.07 & 0.05 & 0.959\\
-\hline
-HCI & 0.25 & 0.06 & 4.25 & 0.000 & NA & NA & NA & NA\\
-\hline
-GC & 0.00 & 0.07 & -0.02 & 0.988 & NA & NA & NA & NA\\
+\hspace{1em}GC & 0.00 & 0.07 & -0.02 & 0.988 & NA & NA & NA & NA\\
 \hline
@@
 
-\caption{\label{tab:unnamed-chunk-18}Table 5: Effect of congruency of venture attention and institutional level (VC) of financial capital}
+\caption{\label{tab:unnamed-chunk-18}Effect of congruency of venture attention and institutional level (VC) of financial capital}
 \centering
@@
 \hline
+VC Availability & -0.07 & 0.09 & -0.75 & 0.454 & -0.07 & 0.09 & -0.79 & 0.432\\
+\hline
+AFCxVC Availability & 0.01 & 0.01 & 1.31 & 0.190 & 0.01 & 0.05 & 0.28 & 0.778\\
+\hline
 \multicolumn{9}{l}{\textbf{Control variables}}\\
 \hline
-\hspace{1em}VC Availability & -0.07 & 0.09 & -0.75 & 0.454 & -0.07 & 0.09 & -0.79 & 0.432\\
+\hspace{1em}HCI & 0.24 & 0.06 & 4.23 & 0.000 & NA & NA & NA & NA\\
 \hline
-\hspace{1em}AFCxVC Availability & 0.01 & 0.01 & 1.31 & 0.190 & 0.01 & 0.05 & 0.28 & 0.778\\
-\hline
-HCI & 0.24 & 0.06 & 4.23 & 0.000 & NA & NA & NA & NA\\
-\hline
-GC & 0.01 & 0.05 & 0.22 & 0.824 & NA & NA & NA & NA\\
+\hspace{1em}GC & 0.01 & 0.05 & 0.22 & 0.824 & NA & NA & NA & NA\\
 \hline
@@
 
-\caption{\label{tab:unnamed-chunk-18}Table 6: Effect of congruency of venture attention and institutional level (Credit gaps) of financial capital}
+\caption{\label{tab:unnamed-chunk-18}Effect of congruency of venture attention and institutional level (Credit gaps) of financial capital}
 \centering
@@
 \hline
+Domestic Credit Gaps & 0.00 & 0.00 & -0.57 & 0.572 & 0.00 & 0.00 & -0.60 & 0.550\\
+\hline
+AFCxDomestic Credit Gaps & 0.01 & 0.01 & 1.30 & 0.192 & 0.00 & 0.00 & 0.15 & 0.882\\
+\hline
 \multicolumn{9}{l}{\textbf{Control variables}}\\
 \hline
-\hspace{1em}Domestic Credit Gaps & 0.00 & 0.00 & -0.57 & 0.572 & 0.00 & 0.00 & -0.60 & 0.550\\
+\hspace{1em}HCI & 0.25 & 0.06 & 4.24 & 0.000 & NA & NA & NA & NA\\
 \hline
-\hspace{1em}AFCxDomestic Credit Gaps & 0.01 & 0.01 & 1.30 & 0.192 & 0.00 & 0.00 & 0.15 & 0.882\\
-\hline
-HCI & 0.25 & 0.06 & 4.24 & 0.000 & NA & NA & NA & NA\\
-\hline
-GC & 0.00 & 0.00 & 0.08 & 0.938 & NA & NA & NA & NA\\
+\hspace{1em}GC & 0.00 & 0.00 & 0.08 & 0.938 & NA & NA & NA & NA\\
 \hline
@@
 
-\caption{\label{tab:unnamed-chunk-18}Table 7: Effect of attention to social capital}
+\caption{\label{tab:unnamed-chunk-18}Effect of attention to social capital}
 \centering
@@
 
-\caption{\label{tab:unnamed-chunk-18}Table 8: Effect of congruency of venture attention and institutional level of social capital}
+\caption{\label{tab:unnamed-chunk-18}Effect of congruency of venture attention and institutional level of social capital}
 \centering
@@
 \hline
+State of cluster development & -0.16 & 0.10 & -1.52 & 0.128 & -0.17 & 0.11 & -1.56 & 0.119\\
+\hline
+ASCxState of cluster development & 0.01 & 0.01 & 1.22 & 0.223 & 0.01 & 0.08 & 0.15 & 0.883\\
+\hline
 \multicolumn{9}{l}{\textbf{Control variables}}\\
 \hline
-\hspace{1em}State of cluster development & -0.16 & 0.10 & -1.52 & 0.128 & -0.17 & 0.11 & -1.56 & 0.119\\
+\hspace{1em}HCI & 0.25 & 0.06 & 4.30 & 0.000 & NA & NA & NA & NA\\
 \hline
-\hspace{1em}ASCxState of cluster development & 0.01 & 0.01 & 1.22 & 0.223 & 0.01 & 0.08 & 0.15 & 0.883\\
+\hspace{1em}GC & 0.01 & 0.08 & 0.16 & 0.876 & NA & NA & NA & NA\\
 \hline
-HCI & 0.25 & 0.06 & 4.30 & 0.000 & NA & NA & NA & NA\\
+\end{tabular}
+\end{table}
+
+\begin{table}
+
+\caption{\label{tab:unnamed-chunk-21}Effect on total employees}
+\centering
+\begin{tabular}[t]{l|l|l|l|l|l|l}
 \hline
-GC & 0.01 & 0.08 & 0.16 & 0.876 & NA & NA & NA & NA\\
+\multicolumn{1}{c|}{\em{ }} & \multicolumn{3}{c|}{\em{Congruence}} & \multicolumn{3}{c}{\em{AHC only}} \\
+\cline{2-4} \cline{5-7}
+  & $b$ & SE & $t$ & $b$ & SE & $t$\\
+\hline
+Intercept & -1,955.91 & 3,599.05 & -0.54 & 762.25 & 502.25 & 1.52\\
+\hline
+AHC & -10,174.65 & 16,704.03 & -0.61 & 2,955.97 & 2,238.11 & 1.32\\
+\hline
+Ease of finding skilled employees & 641.03 & 813.08 & 0.79 & NA & NA & NA\\
+\hline
+AHCxEase of finding skilled employees & 3,118.93 & 3,842.90 & 0.81 & NA & NA & NA\\
+\hline
+\end{tabular}
+\end{table}
+
+\begin{table}
+
+\caption{\label{tab:unnamed-chunk-21}Effect on capital raised}
+\centering
+\begin{tabular}[t]{l|l|l|l|l|l|l}
+\hline
+\multicolumn{1}{c|}{\em{ }} & \multicolumn{3}{c|}{\em{Congruence}} & \multicolumn{3}{c}{\em{AFC only}} \\
+\cline{2-4} \cline{5-7}
+  & $b$ & SE & $t$ & $b$ & SE & $t$\\
+\hline
+Intercept & -4,884.58 & 444,377.03 & -0.01 & 223,507.35 & 80,002.22 & 2.79\\
+\hline
+AFC & -191,023.97 & 590,674.78 & -0.32 & -62,834.51 & 130,477.16 & -0.48\\
+\hline
+Financing of SMEs & 59,478.10 & 112,868.11 & 0.53 & NA & NA & NA\\
+\hline
+AFCxFinancing of SMEs & 31,388.20 & 134,941.74 & 0.23 & NA & NA & NA\\
+\hline
+\end{tabular}
+\end{table}
+
+\begin{table}
+
+\caption{\label{tab:unnamed-chunk-21}Effect on capital raised}
+\centering
+\begin{tabular}[t]{l|l|l|l}
+\hline
+  & $b$ & SE & $t$\\
+\hline
+Intercept & 66,014.34 & 285,161.56 & 0.23\\
+\hline
+AFC & -205,432.60 & 401,457.67 & -0.51\\
+\hline
+VC Availability & 51,857.72 & 88,842.97 & 0.58\\
+\hline
+AFCxVC Availability & 41,162.01 & 104,375.22 & 0.39\\
+\hline
+\end{tabular}
+\end{table}
+
+\begin{table}
+
+\caption{\label{tab:unnamed-chunk-21}Effect on capital raised}
+\centering
+\begin{tabular}[t]{l|l|l|l}
+\hline
+  & $b$ & SE & $t$\\
+\hline
+Intercept & 190,992.97 & 128,015.34 & 1.49\\
+\hline
+AFC & -121,351.86 & 210,077.95 & -0.58\\
+\hline
+Domestic Credit Gaps & 572.94 & 1,620.34 & 0.35\\
+\hline
+AFCxDomestic Credit Gaps & 768.35 & 1,952.74 & 0.39\\
+\hline
+\end{tabular}
+\end{table}
+
+\begin{table}
+
+\caption{\label{tab:unnamed-chunk-21}Effect on sources of capital}
+\centering
+\begin{tabular}[t]{l|l|l|l|l|l|l}
+\hline
+\multicolumn{1}{c|}{\em{ }} & \multicolumn{3}{c|}{\em{Congruence}} & \multicolumn{3}{c}{\em{ASC only}} \\
+\cline{2-4} \cline{5-7}
+  & $b$ & SE & $t$ & $b$ & SE & $t$\\
+\hline
+Intercept & -0.28 & 0.21 & -1.30 & 0.58 & 0.04 & 13.35\\
+\hline
+ASC & -0.60 & 0.25 & -2.45 & 0.06 & 0.05 & 1.35\\
+\hline
+State of cluster development & 0.22 & 0.05 & 4.09 & NA & NA & NA\\
+\hline
+ASCxState of cluster development & 0.17 & 0.06 & 2.94 & NA & NA & NA\\
+\hline
+\end{tabular}
+\end{table}
+
+\begin{table}
+
+\caption{\label{tab:unnamed-chunk-24}Effect on revenues}
+\centering
+\fontsize{7}{9}\selectfont
+\begin{tabular}[t]{l|l|l|l|l|l|l}
+\hline
+\multicolumn{1}{c|}{\em{ }} & \multicolumn{3}{c|}{\em{Congruence}} & \multicolumn{3}{c}{\em{AHC only}} \\
+\cline{2-4} \cline{5-7}
+  & $b$ & SE & $t$ & $b$ & SE & $t$\\
+\hline
+Intercept & 5,033,422.50 & 8,779,342.42 & 0.57 & 2,061,441.83 & 1,172,119.94 & 1.76\\
+\hline
+AHC & 12,174,047.87 & 13,178,734.99 & 0.92 & 1,309,266.88 & 2,015,947.62 & 0.65\\
+\hline
+Ease of finding skilled employees & -677,452.53 & 1,991,735.94 & -0.34 & NA & NA & NA\\
+\hline
+AHCxEase of finding skilled employees & -2,337,599.95 & 2,803,682.74 & -0.83 & NA & NA & NA\\
+\hline
+\end{tabular}
+\end{table}
+
+\begin{table}
+
+\caption{\label{tab:unnamed-chunk-24}Effect on revenues}
+\centering
+\fontsize{7}{9}\selectfont
+\begin{tabular}[t]{l|l|l|l|l|l|l}
+\hline
+\multicolumn{1}{c|}{\em{ }} & \multicolumn{3}{c|}{\em{Congruence}} & \multicolumn{3}{c}{\em{AFC only}} \\
+\cline{2-4} \cline{5-7}
+  & $b$ & SE & $t$ & $b$ & SE & $t$\\
+\hline
+Intercept & 1,091,420.63 & 7,860,432.48 & 0.14 & 1,812,535.35 & 1,024,606.34 & 1.77\\
+\hline
+AFC & -3,691,743.30 & 26,035,557.36 & -0.14 & -5,533,248.45 & 3,452,852.29 & -1.60\\
+\hline
+Financing of SMEs & 220,995.73 & 4,112,461.43 & 0.05 & NA & NA & NA\\
+\hline
+VC Availability & -20,625.49 & 3,293,858.39 & -0.01 & NA & NA & NA\\
+\hline
+Domestic Credit Gaps & 112.62 & 29,302.15 & 0.00 & NA & NA & NA\\
+\hline
+AFCxFinancing of SMEs & -450,299.34 & 13,580,706.25 & -0.03 & NA & NA & NA\\
+\hline
+AFCxVC Availability & -265,392.62 & 10,933,461.08 & -0.02 & NA & NA & NA\\
+\hline
+AFCxDomestic Credit Gaps & 5,897.33 & 98,489.71 & 0.06 & NA & NA & NA\\
+\hline
+\end{tabular}
+\end{table}
+
+\begin{table}
+
+\caption{\label{tab:unnamed-chunk-24}Effect on revenues}
+\centering
+\fontsize{7}{9}\selectfont
+\begin{tabular}[t]{l|l|l|l|l|l|l}
+\hline
+\multicolumn{1}{c|}{\em{ }} & \multicolumn{3}{c|}{\em{Congruence}} & \multicolumn{3}{c}{\em{ASC only}} \\
+\cline{2-4} \cline{5-7}
+  & $b$ & SE & $t$ & $b$ & SE & $t$\\
+\hline
+Intercept & 3,743,005.06 & 6,777,362.02 & 0.55 & 2,072,186.10 & 1,151,987.55 & 1.80\\
+\hline
+ASC & -5,807,873.96 & 17,276,071.97 & -0.34 & -2,440,778.66 & 2,993,083.09 & -0.82\\
+\hline
+State of cluster development & -401,960.58 & 1,679,258.60 & -0.24 & NA & NA & NA\\
+\hline
+ASCxState of cluster development & 825,623.52 & 4,199,015.96 & 0.20 & NA & NA & NA\\
 \hline

### 2021-03-15 Manuscript.Rmd
Finalizing manuscript

@@
 abstract: |
-  One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.
-
-  <!-- https://tinyurl.com/ybremelq -->
+  Early stage entrepreneurs have access to limited resources and must decide what should garner their attention.
+The literatures on entrepreneurial resources and entrepreneurial attention show mixed results and often do not take into account the institutional context of the venture.
+I approach the question of entrepreneurial attention from an institutional perspective using the Global Accelerator Learning Initiative Data.
+In contrast to expectation based on the literature, I find that entrepreneurs do not have to align their attention to resources with the availability of resources in their institutional environment.
+However, their attention to internal human capital (i.e.
+building their own business skills) becomes important if we consider the outcome as being selection to an incubation program to mobilize resources and prepare for long-term resource acquisition.
+Resource acquisition is a long-term goal and that is why I do not see any effects in the short term.
+In contrast, selection to an incubation program is a short-term goal that opens the door for the long-term effects and that is how  early stage ventures should approach their resource base strategy.
+Mobilization comes first and acquisition would follow.
+Thus, the question is not what resources to seek, but when to seek mobilization and when to engage in acquisition of a resource.
 
@@
 
-## Measures
+## Data and Measures
+The dataset from the Global Accelerator Learning Initiative (GALI) covers entrepreneurs who applied to scores of accelerators that began accepting applications between 2013 and 2020.
+Our data include information – collected during program applications – about ventures, founding teams, and pre-program performance.
+They also identify which applicants went on to participate in each program.
+Finally, these data include follow-up information collected from selected and rejected applicants in the years following each application window.
+The anonymized dataset containing both application and follow-up data can be accessed at [GALI Data](www.galidata.org/data-request).
+This is multi-country dataset.
+It typically contains hundreds of ventures per country.
+
+When entrepreneurs apply to a GALI-participating accelerator, they are asked to complete a standardized survey which asks basic questions about their venture’s business model, financial performance, and founding team.
+Then, after one year, they are asked to complete a follow-up survey, whether or not they were accepted into the program to which they applied.
+
+The initial sample consists of 22,928 venture from 73 countries.
+I set aside nonprofit organizations and  observations that are missing relevant venture information or preference ranking, resulting in 15981 observations in the final sample.
+All financial statistics are in United States Dollars (USD).
 
@@
 
+Figure 3 shows us the distribution of venture attention to resources by type of resource.
+We observe that the majority of entrepreneurs focus their attention on direct finding, access to investors and general networking.
+Business training comes second in the entreprenerus radar.
+Credibility and access to peers are the two resources that entrepreneurs rank the lowest in their preference and thus they do not pay attention to acquiring these resources.
+Figure 4 helps us dive in into this distribution by classification of country in terms of income (High income, upper middle income, lower middle income, and low income).
+We see that the distribution is very similar regardless of the country classification.
+
 *Institutional level capital* To measure the level of capital of a certain resource at the country level, I used data from the World Economic Forum Global Competitiveness Index (GCI).
@@
 
+Figure 1 displays all countries in the sample with their positioning along the three dimensions of institutional capital.
+We see that the United States has the highest scores along all three dimensions, meaning that it has a strong infrastructure in terms of all three of forms of capital.
+This explains the mixed results of the research on attention capital given that the majority of this literature is based in the US context.
+Namely, entrepreneurs in the US operate within a rich resource environment and attention to resources depends more in their own strategy and initial resource capital rather than their institutional level captial.
+On the other side of the figure we find Angola as the country with lowest scores along all the dimension of institutional level capital.
+Figure 2 zooms in to get a closer look at the group of countries positioned in the middle at the center of figure 1.
+
 **Outcomes**
 
-*Resource mobilization* is coded as a dichotomous measure *Participated* equal to one
-if an applicant participate to an accelerator program of choice, and zero otherwise.
+*Resource mobilization* is coded as a dichotomous measure *Participated* equal to one if an applicant participate to an accelerator program of choice, and zero otherwise.
 I assume that pariticipating to an acceleration program is the first step to mobiliza all types of resources provided by the accelerator.
@@
 (a), (b), and (c) are all resource acquisition outcomes.
+
+Figure 5 shows us the correlation between the venture network (i.e.
+total equity sources) and the venture attention level to network by country classification.
+Similarly, Figure 6 shows us the correlation between the venture's total capital raised and the its attention level to direct funding by country classification.
 
@@
 
-## Data
-The dataset from the Global Accelerator Learning Initiative (GALI) covers entrepreneurs who applied to scores of accelerators that began accepting applications between 2013 and 2020.
-Our data include information – collected during program applications – about ventures, founding teams, and pre-program performance.
-They also identify which applicants went on to participate in each program.
-Finally, these data include follow-up information collected from selected and rejected applicants in the years following each application window.
-The anonymized dataset containing both application and follow-up data can be accessed at [GALI Data](www.galidata.org/data-request).
-This is multi-country dataset.
-It typically contains hundreds of ventures per country.
-
-When entrepreneurs apply to a GALI-participating accelerator, they are asked to complete a standardized survey which asks basic questions about their venture’s business model, financial performance, and founding team.
-Then, after one year, they are asked to complete a follow-up survey, whether or not they were accepted into the program to which they applied.
-
-I set aside XXX nonprofit organizations and XXX observations that are missing relevant venture information or preference ranking, resulting in xxx observations in the final sample.
-All financial statistics are in United States Dollars (USD).
-********
-
 ## Methods
-The ventures in our sample are nested within countries.
+The ventures in the sample are nested within countries.
 To account for such nested (or hierarchical) structure of the data, I opt for a linear mixed effects model to estimate the effects of each resource alone and when it interacts with institutional level of the resource.
@@
 
-The following equation (formulas) show all the models by outcome category.
-Of note, I run all the following models with conrols and without controls as robustness check.
-Control vriables are HCI refering to Human Capital Index and GC refering to Gender composition (i.e.
-female percentage in a team).
+The following equations show all the models by outcome category.
+Of note, I run all the initial models (i.e.
+resource mobilization models) with conrols and without controls as robustness check.
+Control vriables are the Human Capital Index and Gender composition (i.e.
+female percentage in a team) that were highlight in the previous section about measures.
+AHC, AFC, and ASC refer to our key predictors; Attention to Human Capital, Attention to Financial Capital, and Attention to Social Capital respectively.
 
@@
 
-(1)	*Participated ~  AHC + (AHC | Country)    ; AHC = Attention to Human Capital* 
-(2)	*Participated ~  AHC + (AHC x Ease of finding skilled employees | Country)*
-(3)	*Participated ~  AFC + (AFC | Country)   ; AHC = Attention to Financial Capital*
-(4)	*Participated ~  AFC + (AFC x Financing of SMEs| Country)*   
-(5)	*Participated ~  AFC + (AFC x VC availability | Country)*   
-(6)	*Participated ~  AFC + (AFC x Domestic Credit Gaps | Country)*   
-(7)	*Participated ~  ASC + (ASC | Country) ; ASC = Attention to Social Capital*   
-(8)	*Participated ~  ASC + (ASC x State of cluster development | Country)*
+$${Participated_i} =  \beta_0 + b AHC_i + Controls_i + \epsilon_i $$
+
+$${Participated_i} =  \beta_0 + b_1 AHC_i + b_2 AHC_i * Ease of finding skilled employees_c+ Controls_i + \epsilon_i $$
+$${Participated_i} =  \beta_0 + b AFC_i +Controls_i + \epsilon_i $$   
+$${Participated_i} =  \beta_0 + b_1 AFC_i + b_2 AFC_i * Financing of SMEs_c+ Controls_i + \epsilon_i $$
+$${Participated_i} =  \beta_0 + b_1 AFC_i + b_2 AFC_i * VC availability_c+ Controls_i + \epsilon_i $$
+$${Participated_i} =  \beta_0 + b_1 AFC_i + b_2 AFC_i * Domestic Credit Gaps_c+ Controls_i + \epsilon_i $$
+$${Participated_i} =  \beta_0 + b ASC_i + Controls_i + \epsilon_i $$
+$${Participated_i} =  \beta_0 + b_1 ASC_i + b_2 ASC_i * State of cluster development_c+ Controls_i + \epsilon_i $$
 
@@
 
-(9) *Total employees ~ AHC + (AHC | Country)*
-(10) *Total employees ~ AHC + (AHC x Ease of finding skilled employees | Country)*
-(11) *Capital Raised ~ AFC + (AFC | Country)* 
-(12) *Capital Raised ~ AFC + (AFC x Financing of SMEs| Country)*
-(13) *Capital Raised ~ AFC + (AFC x VC availability | Country)*
-(14) *Capital Raised ~ AFC + (AFC x VC availability | Country)*
-(15) *Capital sources ~ ASC + (ASC | Country)*   
-(16) *Capital sources ~  ASC + (ASC x State of cluster development | Country)*
+$${Total Employees_i} =  \beta_0 + b AHC_i + \epsilon_i $$
+$${Total Employees_i} =  \beta_0 + b_1 AHC_i + b_2 AHC_i * Ease of finding skilled employees_c+ \epsilon_i $$
+$${CapitalRaised_i} =  \beta_0 + b AFC_i + \epsilon_i $$ 
+$${CapitalRaised_i} =  \beta_0 + b_1 AFC_i + b_2 AFC_i * Financing of SMEs_c + \epsilon_i $$
+$${CapitalRaised_i} =  \beta_0 + b_1 AFC_i + b_2 AFC_i * VC availability_c + \epsilon_i $$
+$${CapitalRaised_i} =  \beta_0 + b_1 AFC_i + b_2 AFC_i * Domestic Credit Gaps_c + \epsilon_i $$
+$${CapitalSources_i} =  \beta_0 + b ASC_i + \epsilon_i $$ 
+$${CapitalSources_i} =  \beta_0 + b_1 ASC_i + b_2 ASC_i * State of cluster development_c+ \epsilon_i $$
 
@@
 
-(17)	*Revenue ~  AHC + (AHC | Country)* 
-(18)	*Revenue ~  AHC + (AHC x Ease of finding skilled employees | Country)*
-(19)	*Revenue ~  AFC + (AFC | Country)*
-(20)	*Revenue ~  AFC + (AFC x Financing of SMEs| Country) + (AFC x VC availability | Country) + (AFC x Domestic Credit Gaps | Country)*   
-(23)	*Revenue ~  ASC + (ASC | Country)*   
-(24)	*Revenue ~  ASC + (ASC x State of cluster development | Country)*
+$${Revenue_i} =  \beta_0 + b AHC_i + \epsilon_i $$ 
+$${Revenue_i} =  \beta_0 + b_1 AHC_i + b_2 AHC_i * Ease of finding skilled employees_c+ \epsilon_i $$
+$${Revenue_i} =  \beta_0 + b AFC_i + \epsilon_i $$ 
+$${Revenue_i} =  \beta_0 + b_1 AFC_i + b_2 AFC_i * Financing of SMEs_c + b_3 AFC_i * VC availability_c + b_4 AFC_i * Domestic Credit Gaps_c + \epsilon_i $$
+$${Revenue_i} =  \beta_0 + b ASC_i + \epsilon_i $$
+$${Revenue_i} =  \beta_0 + b_1 ASC_i + b_2 ASC_i * State of cluster development_c+ \epsilon_i $$
 
@@
   facet_grid(~Attention) +
-  theme_bw()
+  theme_bw()+
+  ylab("")+
+  xlab("Attention score")
 
@@
   facet_grid(vars(`Income group`), vars(Attention)) +
-  theme_bw()
+  theme_bw() +
+  ylab("")+
+  xlab("Attention score")
 
@@
   facet_grid(~`Income group`)+
+  xlab("Attention to Network")+
   theme_bw()
@@
   facet_grid(~`Income group`)+
+  xlab("Attention to Direct Funding")+
   theme_bw()
@@
 
-kable(hc_zero, escape = F, caption = "Effect of attention to human capital") %>%
+kable(hc_zero, escape = F, caption = "Effect of attention to human capital on likelihood of participation") %>%
   add_header_above(c(" ", "Model w/ controls" = 4, "Model w/o controls" = 4), italic = T) %>%
@@
 
-kable(hc_one, escape = F, caption = "Effect of congruency of venture attention and institutional level of human capital", format = "latex") %>%
+kable(hc_one, escape = F, caption = "Effect of congruency of venture attention and institutional level of human capital on likelihood of participation", format = "latex") %>%
   add_header_above(c(" ", "Model w/ controls" = 4, "Model w/o controls" = 4), italic = T) %>%
@@
 
-kbl(fc_zero, escape = F, caption = "Effect of attention to financial capital") %>%
+kbl(fc_zero, escape = F, caption = "Effect of attention to financial capital on likelihood of participation") %>%
   add_header_above(c(" ", "Model w/ controls" = 4, "Model w/o controls" = 4), italic = T) %>%
@@
 
-kbl(fc_one, escape = F, caption = "Effect of congruency of venture attention and institutional level (SME financing) of financial capital") %>%
+kbl(fc_one, escape = F, caption = "Effect of congruency of venture attention and institutional level (SME financing) of financial capital on likelihood of participation") %>%
   add_header_above(c(" ", "Model w/ controls" = 4, "Model w/o controls" = 4), italic = T) %>%
@@
 
-kbl(fc_two, escape = F, caption = "Effect of congruency of venture attention and institutional level (VC) of financial capital") %>%
+kbl(fc_two, escape = F, caption = "Effect of congruency of venture attention and institutional level (VC) of financial capital on likelihood of participation") %>%
   add_header_above(c(" ", "Model w/ controls" = 4, "Model w/o controls" = 4), italic = T) %>%
@@
 
-kbl(fc_three, escape = F, caption = "Effect of congruency of venture attention and institutional level (Credit gaps) of financial capital") %>%
+kbl(fc_three, escape = F, caption = "Effect of congruency of venture attention and institutional level (Credit gaps) of financial capital on likelihood of participation") %>%
   add_header_above(c(" ", "Model w/ controls" = 4, "Model w/o controls" = 4), italic = T) %>%
@@
 
-kbl(sc_zero, escape = F, caption = "Effect of attention to social capital") %>%
+kbl(sc_zero, escape = F, caption = "Effect of attention to social capital on likelihood of participation") %>%
   add_header_above(c(" ", "Model w/ controls" = 4, "Model w/o controls" = 4), italic = T) %>%
@@
 
-kbl(sc_one, escape = F, caption = "Effect of congruency of venture attention and institutional level of social capital") %>%
+kbl(sc_one, escape = F, caption = "Effect of congruency of venture attention and institutional level of social capital on likelihood of participation") %>%
   add_header_above(c(" ", "Model w/ controls" = 4, "Model w/o controls" = 4), italic = T) %>%
@@
 
-# Discussion
+# Results and Discussion
+**Resource mobilization**
+
+I find no support for hypothesis 1, with exception for certain resources.
+Specifically, Table 1 shows that an increase in venture attention to human capital causes an increase in the venture's likelihood to participate to the acceleration program and mobilize resources.
+However, this effect is not statistically significant.
+The model is robust to the addition of control variables.
+Similarly, table 7 show that an increase in venture to attention social capital causes an increase in the venture's likelihood to mobilize resources within the acceleration program.
+These effects are not statistically signification.
+Table 3 on the other hand, show that an increase in venture attention to social capital results in a significant decrease in the venture's likelihood to mobilize resources.
+This shows that early stage ventures applying to accelerator programs benefit the most if they first focus on mobilizing human and social capital resources before turning attention to financial capital.
+To examine our hypotheses exploring these same relationships within the institutional context of the venture, we turn to tables 2, 4, 5, 6, and 8.
+When I interact the venture level attention to human capital with the institutional level human capital (Table 2), I find that attention to this resource results in a significant increase in the likelihood to mobilize resources within the accelerator program ($b = 0.9$), and the model is robust to control variables.
+In contrast, tables 3 to 5 show that attention to financial capital has a non-significant effect on the venture's likelihood to mobilize resources regardless of the institutional context.
+We find the same results whether we consider institutional level capital for SMEs, VC oriented ventures, or ventures seeking loans and other forms of financing from financial establishments.
+This is in line with our initial finding that human and social capital should garner the attention of ventures seeking resources in their early stage from incubators and accelerators.
+Finally, table 8 shows us that the congruency of venture attention and the institutional level of social capital does not have any significant effect on the venture's likelihood to mobilize resources.
+
+This first part of the analysis focuses on resource mobilization within accelerator programs and explores the relationship between venture attention to a certain type of resources and its influence on the venture's likelihood to participate to the program.
+I find that social and human capital are the key resources that should be on the venture's radar in their early stage of strategy formation.
+I then investigate the impact of the congruency between the venture attention and the institutional level capital to better understand these relationships within their institutional context.
+I find that human capital is not only one of the key resources to focus on but it becomes even more important if it aligns with the venture's country to provide skillful human resources.
+
+**Resource acquisition**
+
+Similar to hypothesis 1, I find no support for the second hypothesis.
+Table 9 shows the impact of venture attention to human capital and its congruency level with the institutional capital on the acquisition of human capital (total number of employees) post-acceleration program.
+I find no significant effect in the two models.
+Tables 10 to 12 show the impact of venture attention to financial capital and its congruency level with the institutional capital on the acquisition of financial capital (capital raised in USD) post-acceleration program.
+I find no significant effect in the two models.
+Finally, table 13 shows the the impact of venture attention to social capital and its congruency level with the institutional capital on the acquisition of social capital (sources of capital) post-acceleration program.
+I find no significant effect in the two models.
+
+It is important to highlight here, that not only I find no significant effect but also all the coefficients are negative.
+This negative effect on resource acquisition post-acceleration program can be interpreted economically, as an opportunity cost.
+Ventures that succeed in mobilizing resources put their time and efforts into acquiring business skills, developing their network, and seeking funding resources.
+While these efforts might result in resource acquisition, over the long-term, we would not be able to observe this within a year or two post resource mobilization.
+This is a key limitation of our data and analysis.
+
+**Performance**
+
+Based on the results of resource acquisition we would expect similar results for venture performance (hypothesis 3) since revenues are often accumulated post resource acquisition.
+We can consider this part of the analysis as a robustness check for the previous analysis on resource acquisition.
+Tables 14 to 16 confirm these expectations.
+I find only null effects of the impact of venture attention to a resource and its congruency level with the institutional level of the resource on performance (measured based on firm revenues) post acceleration program.
+
+There are several channels to interpret the results of all three outcomes.
+The most plausible explanation is that at their early stages of venturing, entrepreneurs do not have to align their attention to resources with the availability of resources in their institutional environment.
+However, their attention to internal human capital (i.e.
+building their own business skills) becomes important if we consider the outcome as being selection to an incubation program instead to mobilize resources and prepare for long-term resource acquisition.
+Resource acquisition is a long-term goal and that is why I do not see any effects in the short term (2 years post acceleration).
+In contrast, selection to an incubation program is a short-term goal that opens the door for the long-term effects and that is how ventures in our sample should approach their resource base strategy (i.e.
+mobilization first and acquisition would follow).
 

### 2021-03-15 Manuscript.tex
Finalizing manuscript

@@
 \abstract{
-One or two sentences providing a \textbf{basic introduction} to the field, comprehensible to a scientist in any discipline.
+Early stage entrepreneurs have access to limited resources and must decide what should garner their attention.
+The literatures on entrepreneurial resources and entrepreneurial attention show mixed results and often do not take into account the institutional context of the venture.
+I approach the question of entrepreneurial attention from an institutional perspective using the Global Accelerator Learning Initiative Data.
+In contrast to expectation based on the literature, I find that entrepreneurs do not have to align their attention to resources with the availability of resources in their institutional environment.
+However, their attention to internal human capital (i.e.~building their own business skills) becomes important if we consider the outcome as being selection to an incubation program to mobilize resources and prepare for long-term resource acquisition.
+Resource acquisition is a long-term goal and that is why I do not see any effects in the short term.
+In contrast, selection to an incubation program is a short-term goal that opens the door for the long-term effects and that is how early stage ventures should approach their resource base strategy.
+Mobilization comes first and acquisition would follow.
+Thus, the question is not what resources to seek, but when to seek mobilization and when to engage in acquisition of a resource.
 }
@@
 
-\hypertarget{measures}{%
-\subsection{Measures}\label{measures}}
+\hypertarget{data-and-measures}{%
+\subsection{Data and Measures}\label{data-and-measures}}
+
+The dataset from the Global Accelerator Learning Initiative (GALI) covers entrepreneurs who applied to scores of accelerators that began accepting applications between 2013 and 2020.
+Our data include information -- collected during program applications -- about ventures, founding teams, and pre-program performance.
+They also identify which applicants went on to participate in each program.
+Finally, these data include follow-up information collected from selected and rejected applicants in the years following each application window.
+The anonymized dataset containing both application and follow-up data can be accessed at \href{www.galidata.org/data-request}{GALI Data}.
+This is multi-country dataset.
+It typically contains hundreds of ventures per country.
+
+When entrepreneurs apply to a GALI-participating accelerator, they are asked to complete a standardized survey which asks basic questions about their venture's business model, financial performance, and founding team.
+Then, after one year, they are asked to complete a follow-up survey, whether or not they were accepted into the program to which they applied.
+
+The initial sample consists of 22,928 venture from 73 countries.
+I set aside nonprofit organizations and observations that are missing relevant venture information or preference ranking, resulting in 15981 observations in the final sample.
+All financial statistics are in United States Dollars (USD).
 
@@
 
+Figure 3 shows us the distribution of venture attention to resources by type of resource.
+We observe that the majority of entrepreneurs focus their attention on direct finding, access to investors and general networking.
+Business training comes second in the entreprenerus radar.
+Credibility and access to peers are the two resources that entrepreneurs rank the lowest in their preference and thus they do not pay attention to acquiring these resources.
+Figure 4 helps us dive in into this distribution by classification of country in terms of income (High income, upper middle income, lower middle income, and low income).
+We see that the distribution is very similar regardless of the country classification.
+
 \emph{Institutional level capital} To measure the level of capital of a certain resource at the country level, I used data from the World Economic Forum Global Competitiveness Index (GCI).
@@
 
+Figure 1 displays all countries in the sample with their positioning along the three dimensions of institutional capital.
+We see that the United States has the highest scores along all three dimensions, meaning that it has a strong infrastructure in terms of all three of forms of capital.
+This explains the mixed results of the research on attention capital given that the majority of this literature is based in the US context.
+Namely, entrepreneurs in the US operate within a rich resource environment and attention to resources depends more in their own strategy and initial resource capital rather than their institutional level captial.
+On the other side of the figure we find Angola as the country with lowest scores along all the dimension of institutional level capital.
+Figure 2 zooms in to get a closer look at the group of countries positioned in the middle at the center of figure 1.
+
 \textbf{Outcomes}
 
-\emph{Resource mobilization} is coded as a dichotomous measure \emph{Participated} equal to one
-if an applicant participate to an accelerator program of choice, and zero otherwise.
+\emph{Resource mobilization} is coded as a dichotomous measure \emph{Participated} equal to one if an applicant participate to an accelerator program of choice, and zero otherwise.
 I assume that pariticipating to an acceleration program is the first step to mobiliza all types of resources provided by the accelerator.
@@
 (a), (b), and (c) are all resource acquisition outcomes.
+
+Figure 5 shows us the correlation between the venture network (i.e.~total equity sources) and the venture attention level to network by country classification.
+Similarly, Figure 6 shows us the correlation between the venture's total capital raised and the its attention level to direct funding by country classification.
 
@@
 
-\hypertarget{data}{%
-\subsection{Data}\label{data}}
-
-The dataset from the Global Accelerator Learning Initiative (GALI) covers entrepreneurs who applied to scores of accelerators that began accepting applications between 2013 and 2020.
-Our data include information -- collected during program applications -- about ventures, founding teams, and pre-program performance.
-They also identify which applicants went on to participate in each program.
-Finally, these data include follow-up information collected from selected and rejected applicants in the years following each application window.
-The anonymized dataset containing both application and follow-up data can be accessed at \href{www.galidata.org/data-request}{GALI Data}.
-This is multi-country dataset.
-It typically contains hundreds of ventures per country.
-
-When entrepreneurs apply to a GALI-participating accelerator, they are asked to complete a standardized survey which asks basic questions about their venture's business model, financial performance, and founding team.
-Then, after one year, they are asked to complete a follow-up survey, whether or not they were accepted into the program to which they applied.
-
-I set aside XXX nonprofit organizations and XXX observations that are missing relevant venture information or preference ranking, resulting in xxx observations in the final sample.
-All financial statistics are in United States Dollars (USD).
-********
-
 \hypertarget{methods}{%
@@
 
-The ventures in our sample are nested within countries.
+The ventures in the sample are nested within countries.
 To account for such nested (or hierarchical) structure of the data, I opt for a linear mixed effects model to estimate the effects of each resource alone and when it interacts with institutional level of the resource.
@@
 
-The following equation (formulas) show all the models by outcome category.
-Of note, I run all the following models with conrols and without controls as robustness check.
-Control vriables are HCI refering to Human Capital Index and GC refering to Gender composition (i.e.~female percentage in a team).
+The following equations show all the models by outcome category.
+Of note, I run all the initial models (i.e.~resource mobilization models) with conrols and without controls as robustness check.
+Control vriables are the Human Capital Index and Gender composition (i.e.~female percentage in a team) that were highlight in the previous section about measures.
+AHC, AFC, and ASC refer to our key predictors; Attention to Human Capital, Attention to Financial Capital, and Attention to Social Capital respectively.
 
@@
 
-\begin{enumerate}
-\def\labelenumi{(\arabic{enumi})}
-\tightlist
-\item
-  \emph{Participated \textasciitilde{} AHC + (AHC \textbar{} Country) ; AHC = Attention to Human Capital}
-\item
-  \emph{Participated \textasciitilde{} AHC + (AHC x Ease of finding skilled employees \textbar{} Country)}
-\item
-  \emph{Participated \textasciitilde{} AFC + (AFC \textbar{} Country) ; AHC = Attention to Financial Capital}
-\item
-  \emph{Participated \textasciitilde{} AFC + (AFC x Financing of SMEs\textbar{} Country)}\\
-\item
-  \emph{Participated \textasciitilde{} AFC + (AFC x VC availability \textbar{} Country)}\\
-\item
-  \emph{Participated \textasciitilde{} AFC + (AFC x Domestic Credit Gaps \textbar{} Country)}\\
-\item
-  \emph{Participated \textasciitilde{} ASC + (ASC \textbar{} Country) ; ASC = Attention to Social Capital}\\
-\item
-  \emph{Participated \textasciitilde{} ASC + (ASC x State of cluster development \textbar{} Country)}
-\end{enumerate}
+\[{Participated_i} =  \beta_0 + b AHC_i + Controls_i + \epsilon_i \]
+
+\[{Participated_i} =  \beta_0 + b_1 AHC_i + b_2 AHC_i * Ease of finding skilled employees_c+ Controls_i + \epsilon_i \]
+\[{Participated_i} =  \beta_0 + b AFC_i +Controls_i + \epsilon_i \]\\
+\[{Participated_i} =  \beta_0 + b_1 AFC_i + b_2 AFC_i * Financing of SMEs_c+ Controls_i + \epsilon_i \]
+\[{Participated_i} =  \beta_0 + b_1 AFC_i + b_2 AFC_i * VC availability_c+ Controls_i + \epsilon_i \]
+\[{Participated_i} =  \beta_0 + b_1 AFC_i + b_2 AFC_i * Domestic Credit Gaps_c+ Controls_i + \epsilon_i \]
+\[{Participated_i} =  \beta_0 + b ASC_i + Controls_i + \epsilon_i \]
+\[{Participated_i} =  \beta_0 + b_1 ASC_i + b_2 ASC_i * State of cluster development_c+ Controls_i + \epsilon_i \]
 
@@
 
-\begin{enumerate}
-\def\labelenumi{(\arabic{enumi})}
-\setcounter{enumi}{8}
-\tightlist
-\item
-  \emph{Total employees \textasciitilde{} AHC + (AHC \textbar{} Country)}
-\item
-  \emph{Total employees \textasciitilde{} AHC + (AHC x Ease of finding skilled employees \textbar{} Country)}
-\item
-  \emph{Capital Raised \textasciitilde{} AFC + (AFC \textbar{} Country)}
-\item
-  \emph{Capital Raised \textasciitilde{} AFC + (AFC x Financing of SMEs\textbar{} Country)}
-\item
-  \emph{Capital Raised \textasciitilde{} AFC + (AFC x VC availability \textbar{} Country)}
-\item
-  \emph{Capital Raised \textasciitilde{} AFC + (AFC x VC availability \textbar{} Country)}
-\item
-  \emph{Capital sources \textasciitilde{} ASC + (ASC \textbar{} Country)}\\
-\item
-  \emph{Capital sources \textasciitilde{} ASC + (ASC x State of cluster development \textbar{} Country)}
-\end{enumerate}
+\[{Total Employees_i} =  \beta_0 + b AHC_i + \epsilon_i \]
+\[{Total Employees_i} =  \beta_0 + b_1 AHC_i + b_2 AHC_i * Ease of finding skilled employees_c+ \epsilon_i \]
+\[{CapitalRaised_i} =  \beta_0 + b AFC_i + \epsilon_i \]
+\[{CapitalRaised_i} =  \beta_0 + b_1 AFC_i + b_2 AFC_i * Financing of SMEs_c + \epsilon_i \]
+\[{CapitalRaised_i} =  \beta_0 + b_1 AFC_i + b_2 AFC_i * VC availability_c + \epsilon_i \]
+\[{CapitalRaised_i} =  \beta_0 + b_1 AFC_i + b_2 AFC_i * Domestic Credit Gaps_c + \epsilon_i \]
+\[{CapitalSources_i} =  \beta_0 + b ASC_i + \epsilon_i \]
+\[{CapitalSources_i} =  \beta_0 + b_1 ASC_i + b_2 ASC_i * State of cluster development_c+ \epsilon_i \]
 
@@
 
-\begin{enumerate}
-\def\labelenumi{(\arabic{enumi})}
-\setcounter{enumi}{16}
-\tightlist
-\item
-  \emph{Revenue \textasciitilde{} AHC + (AHC \textbar{} Country)}
-\item
-  \emph{Revenue \textasciitilde{} AHC + (AHC x Ease of finding skilled employees \textbar{} Country)}
-\item
-  \emph{Revenue \textasciitilde{} AFC + (AFC \textbar{} Country)}
-\item
-  \emph{Revenue \textasciitilde{} AFC + (AFC x Financing of SMEs\textbar{} Country)}\\
-\item
-  \emph{Revenue \textasciitilde{} AFC + (AFC x VC availability \textbar{} Country)}\\
-\item
-  \emph{Revenue \textasciitilde{} AFC + (AFC x Domestic Credit Gaps \textbar{} Country)}\\
-\item
-  \emph{Revenue \textasciitilde{} ASC + (ASC \textbar{} Country)}\\
-\item
-  \emph{Revenue \textasciitilde{} ASC + (ASC x State of cluster development \textbar{} Country)}
-\end{enumerate}
+\[{Revenue_i} =  \beta_0 + b AHC_i + \epsilon_i \]
+\[{Revenue_i} =  \beta_0 + b_1 AHC_i + b_2 AHC_i * Ease of finding skilled employees_c+ \epsilon_i \]
+\[{Revenue_i} =  \beta_0 + b AFC_i + \epsilon_i \]
+\[{Revenue_i} =  \beta_0 + b_1 AFC_i + b_2 AFC_i * Financing of SMEs_c + b_3 AFC_i * VC availability_c + b_4 AFC_i * Domestic Credit Gaps_c + \epsilon_i \]
+\[{Revenue_i} =  \beta_0 + b ASC_i + \epsilon_i \]
+\[{Revenue_i} =  \beta_0 + b_1 ASC_i + b_2 ASC_i * State of cluster development_c+ \epsilon_i \]
 
@@
 
-\caption{\label{tab:unnamed-chunk-18}Effect of attention to human capital}
+\caption{\label{tab:unnamed-chunk-18}Effect of attention to human capital on likelihood of participation}
 \centering
@@
 
-\caption{\label{tab:unnamed-chunk-18}Effect of congruency of venture attention and institutional level of human capital}
+\caption{\label{tab:unnamed-chunk-18}Effect of congruency of venture attention and institutional level of human capital on likelihood of participation}
 \centering
@@
 
-\caption{\label{tab:unnamed-chunk-18}Effect of attention to financial capital}
+\caption{\label{tab:unnamed-chunk-18}Effect of attention to financial capital on likelihood of participation}
 \centering
@@
 
-\caption{\label{tab:unnamed-chunk-18}Effect of congruency of venture attention and institutional level (SME financing) of financial capital}
+\caption{\label{tab:unnamed-chunk-18}Effect of congruency of venture attention and institutional level (SME financing) of financial capital on likelihood of participation}
 \centering
@@
 
-\caption{\label{tab:unnamed-chunk-18}Effect of congruency of venture attention and institutional level (VC) of financial capital}
+\caption{\label{tab:unnamed-chunk-18}Effect of congruency of venture attention and institutional level (VC) of financial capital on likelihood of participation}
 \centering
@@
 
-\caption{\label{tab:unnamed-chunk-18}Effect of congruency of venture attention and institutional level (Credit gaps) of financial capital}
+\caption{\label{tab:unnamed-chunk-18}Effect of congruency of venture attention and institutional level (Credit gaps) of financial capital on likelihood of participation}
 \centering
@@
 
-\caption{\label{tab:unnamed-chunk-18}Effect of attention to social capital}
+\caption{\label{tab:unnamed-chunk-18}Effect of attention to social capital on likelihood of participation}
 \centering
@@
 
-\caption{\label{tab:unnamed-chunk-18}Effect of congruency of venture attention and institutional level of social capital}
+\caption{\label{tab:unnamed-chunk-18}Effect of congruency of venture attention and institutional level of social capital on likelihood of participation}
 \centering
@@
 \centering
-\fontsize{7}{9}\selectfont
+\fontsize{8}{10}\selectfont
 \begin{tabular}[t]{l|l|l|l|l|l|l}
@@
 
-\hypertarget{discussion}{%
-\section{Discussion}\label{discussion}}
+\hypertarget{results-and-discussion}{%
+\section{Results and Discussion}\label{results-and-discussion}}
+
+\textbf{Resource mobilization}
+
+I find no support for hypothesis 1, with exception for certain resources.
+Specifically, Table 1 shows that an increase in venture attention to human capital causes an increase in the venture's likelihood to participate to the acceleration program and mobilize resources.
+However, this effect is not statistically significant.
+The model is robust to the addition of control variables.
+Similarly, table 7 show that an increase in venture to attention social capital causes an increase in the venture's likelihood to mobilize resources within the acceleration program.
+These effects are not statistically signification.
+Table 3 on the other hand, show that an increase in venture attention to social capital results in a significant decrease in the venture's likelihood to mobilize resources.
+This shows that early stage ventures applying to accelerator programs benefit the most if they first focus on mobilizing human and social capital resources before turning attention to financial capital.
+To examine our hypotheses exploring these same relationships within the institutional context of the venture, we turn to tables 2, 4, 5, 6, and 8.
+When I interact the venture level attention to human capital with the institutional level human capital (Table 2), I find that attention to this resource results in a significant increase in the likelihood to mobilize resources within the accelerator program (\(b = 0.9\)), and the model is robust to control variables.
+In contrast, tables 3 to 5 show that attention to financial capital has a non-significant effect on the venture's likelihood to mobilize resources regardless of the institutional context.
+We find the same results whether we consider institutional level capital for SMEs, VC oriented ventures, or ventures seeking loans and other forms of financing from financial establishments.
+This is in line with our initial finding that human and social capital should garner the attention of ventures seeking resources in their early stage from incubators and accelerators.
+Finally, table 8 shows us that the congruency of venture attention and the institutional level of social capital does not have any significant effect on the venture's likelihood to mobilize resources.
+
+This first part of the analysis focuses on resource mobilization within accelerator programs and explores the relationship between venture attention to a certain type of resources and its influence on the venture's likelihood to participate to the program.
+I find that social and human capital are the key resources that should be on the venture's radar in their early stage of strategy formation.
+I then investigate the impact of the congruency between the venture attention and the institutional level capital to better understand these relationships within their institutional context.
+I find that human capital is not only one of the key resources to focus on but it becomes even more important if it aligns with the venture's country to provide skillful human resources.
+
+\textbf{Resource acquisition}
+
+Similar to hypothesis 1, I find no support for the second hypothesis.
+Table 9 shows the impact of venture attention to human capital and its congruency level with the institutional capital on the acquisition of human capital (total number of employees) post-acceleration program.
+I find no significant effect in the two models.
+Tables 10 to 12 show the impact of venture attention to financial capital and its congruency level with the institutional capital on the acquisition of financial capital (capital raised in USD) post-acceleration program.
+I find no significant effect in the two models.
+Finally, table 13 shows the the impact of venture attention to social capital and its congruency level with the institutional capital on the acquisition of social capital (sources of capital) post-acceleration program.
+I find no significant effect in the two models.
+
+It is important to highlight here, that not only I find no significant effect but also all the coefficients are negative.
+This negative effect on resource acquisition post-acceleration program can be interpreted economically, as an opportunity cost.
+Ventures that succeed in mobilizing resources put their time and efforts into acquiring business skills, developing their network, and seeking funding resources.
+While these efforts might result in resource acquisition, over the long-term, we would not be able to observe this within a year or two post resource mobilization.
+This is a key limitation of our data and analysis.
+
+\textbf{Performance}
+
+Based on the results of resource acquisition we would expect similar results for venture performance (hypothesis 3) since revenues are often accumulated post resource acquisition.
+We can consider this part of the analysis as a robustness check for the previous analysis on resource acquisition.
+Tables 14 to 16 confirm these expectations.
+I find only null effects of the impact of venture attention to a resource and its congruency level with the institutional level of the resource on performance (measured based on firm revenues) post acceleration program.
+
+There are several channels to interpret the results of all three outcomes.
+The most plausible explanation is that at their early stages of venturing, entrepreneurs do not have to align their attention to resources with the availability of resources in their institutional environment.
+However, their attention to internal human capital (i.e.~building their own business skills) becomes important if we consider the outcome as being selection to an incubation program instead to mobilize resources and prepare for long-term resource acquisition.
+Resource acquisition is a long-term goal and that is why I do not see any effects in the short term (2 years post acceleration).
+In contrast, selection to an incubation program is a short-term goal that opens the door for the long-term effects and that is how ventures in our sample should approach their resource base strategy (i.e.~mobilization first and acquisition would follow).
 

### 2021-03-15 Manuscript.Rmd
Final manuscript for capstone submission - more to come later

@@
   Lundquist College of Business 
-
   Department of Management
@@
 
-```{r fig.height=5, fig.width=8}
+```{r fig.height=7, fig.width=9}
 #Distribution of attention
@@
   ylab("")+
-  xlab("Attention score")
+  xlab("Attention score")+
+  labs(title =  "Distribution of venture attention to resources by type of resource")
 
@@
   ylab("")+
-  xlab("Attention score")
+  xlab("Attention score")+
+  labs(title =  "Distribution of venture attention to resources by type of resource and country classification")
 
@@
 
+#Function to wrap long titles 
+wrapper <- function(x, ...) 
+{
+  paste(strwrap(x, ...), collapse = "\n")
+}
+
 filter(b, Attention == "Network")  %>%
@@
   xlab("Attention to Network")+
+  ggtitle(wrapper("Correlation between the venture network and the venture attention level to network by country classification", width = 80))+
   theme_bw()
@@
   xlab("Attention to Direct Funding")+
+  ggtitle(wrapper("Correlation between  the venture’s total capital raised and the its attention level to direct funding by country classification", width = 80))+
   theme_bw()
@@
 
+# Conclusion
+
 There are several channels to interpret the results of all three outcomes.

### 2021-03-16 Manuscript.Rmd
jftn feedback/suggestions

@@
 ---
-title             : "An institutional approach to attention allocation and venture resource mobilization and acquisition"
+title             : "An Institutional Approach to Attention Allocation and Venture Resource Mobilization and Acquisition"
 shorttitle        : "An institutional approach to venture attention allocation"
@@
 I approach the question of entrepreneurial attention from an institutional perspective using the Global Accelerator Learning Initiative Data.
-In contrast to expectation based on the literature, I find that entrepreneurs do not have to align their attention to resources with the availability of resources in their institutional environment.
+In contrast to expectation based on the literature, I found that entrepreneurs do not have to align their attention to resources with the availability of resources in their institutional environment.
 However, their attention to internal human capital (i.e.
-building their own business skills) becomes important if we consider the outcome as being selection to an incubation program to mobilize resources and prepare for long-term resource acquisition.
-Resource acquisition is a long-term goal and that is why I do not see any effects in the short term.
+building their own business skills) becomes important if we consider selection to an incubation program to mobilize resources and prepare for long-term resource acquisition.
+Resource acquisition is a long-term goal and perhaps that is why I did not see any effects in the short term.
 In contrast, selection to an incubation program is a short-term goal that opens the door for the long-term effects and that is how  early stage ventures should approach their resource base strategy.
@@
 documentclass     : "apa6"
-classoption       : "man"
+classoption: "man, fleqn, noextraspace"
+header-includes:
+  - \raggedbottom
+  - \setlength{\parskip}{0pt}
 output            : papaja::apa6_pdf
@@
 r_refs("r-references.bib")
-```
-
-```{r analysis-preferences}
-# Seed for random number generation
-set.seed(42)
-knitr::opts_chunk$set(cache.extra = knitr::rand_seed, warning = F, message = F, fig.pos = "!H", out.extra = "")
-#options(knitr.table.format = "latex")
 ```
@@
 Where they focus their attention determines the propensity of mobilizing and acquiring resources.
-A venture could miss the chance to exploit an opportunity of resources acquisition if that opportunity never appears on the entrepreneur’s radar screens because they are too focused on an alternative resource.
+A venture could miss the chance to exploit an opportunity of resource acquisition if that opportunity never appears on the entrepreneur’s radar screens because they are too focused on an alternative resource.
 For example, a voluntary work with potential partners who are well connected to other investors might be missed because the founder is too focused on raising capital by honing their business plan over and over and even paying accounting boutique firms to develop that business plan for them.
@@
 The debate over which resource should garner the entrepreneur’s attention concludes that the founding team resource endowment is the key factor that influences resource acquisition.
-For instance, scholars argue that founding teams with a more ties to potential investors are more likely to gain funding [@shane2002organizational].
+For instance, scholars argue that founding teams with more ties to potential investors are more likely to gain funding [@shane2002organizational].
 Furthermore, if we focus on the findings of the stream of research examining the performance implications of acquiring financial capital [@hochberg2007whom] we would expect that early-stage financing should be most likely to garner founders’ attention.
@@
 
-**Hypothesis 1** *The higher the level of congruency of venture’s attention to a resource and its institutional level capital, the higher the odds of mobilization that resource*
-
-**Hypothesis 2** *The higher the level of congruency of venture’s attention to a resource and its institutional level capital, the higher the level of the accumulated resource*
-
-**Hypothesis 3** *The higher the level of congruency of venture’s attention to a resource and its institutional level capital, the higher the venture performance*
+**Hypothesis 1** *The higher the level of congruence of venture’s attention to a resource and its institutional level capital, the higher the odds of mobilization that resource.*
+
+**Hypothesis 2** *The higher the level of congruence of venture’s attention to a resource and its institutional level capital, the higher the level of the accumulated resource.*
+
+**Hypothesis 3** *The higher the level of congruence of venture’s attention to a resource and its institutional level capital, the higher the venture performance.*
 
@@
 The dataset from the Global Accelerator Learning Initiative (GALI) covers entrepreneurs who applied to scores of accelerators that began accepting applications between 2013 and 2020.
-Our data include information – collected during program applications – about ventures, founding teams, and pre-program performance.
+The data include information – collected during program applications – about ventures, founding teams, and pre-program performance.
 They also identify which applicants went on to participate in each program.
@@
 ```{r Countries to analyse in main sample, message=FALSE, warning=FALSE, include=FALSE}
-gali <- import("Data/GALI_External_DataRelease_2020.xlsx") 
+gali <- import("Data/GALI_External_DataRelease_2020.xlsx") %>% 
+  as_tibble() #just easier for me to work with
+
 wb <- import("Data/CLASS.xls")
@@
 countries_to_keep <- gali %>% 
-  group_by(gali$info_venture_country_hq) %>%
+  group_by(info_venture_country_hq) %>% #you do not need to index with $ here
   summarize(Count=n()) %>%
@@
 
-countries_to_keep <- filter(countries_to_keep, `gali$info_venture_country_hq` != 'NA')
+countries_to_keep <- filter(countries_to_keep, 
+                            !is.na(info_venture_country_hq)) #if you remove the $ above, your variable name will change
 
 countries_to_keep <- filter(countries_to_keep, Count >9)
-countries_to_keep$`gali$info_venture_country_hq`
 
 gali <- gali %>%
-  filter(info_venture_country_hq  %in% countries_to_keep$`gali$info_venture_country_hq`)
-
+  filter(info_venture_country_hq  %in% countries_to_keep$info_venture_country_hq)
+
+# you can also use the code below
+
+# gali <- gali %>%
+#   as_tibble() %>% 
+#   inner_join(countries_to_keep) 
 ```
@@
 
+## This may be more efficient
+# gali %>% 
+#   filter(found_name1_age > 14 & found_name1_age < 70 | is.na(found_name1_age),
+#          found_name2_age > 14 & found_name2_age < 70 | is.na(found_name2_age),
+#          found_name3_age > 14 & found_name3_age < 70 | is.na(found_name3_age))
+
 #Keep only for porfit firms 
@@
 }  else gali <- filter(gali, info_founding_year > 2012)
+
+# Something like this might be work
+# 
+# gali %>% 
+#   filter(application_year - info_founding_year < 6)
+
 ```
@@
 
+# consider the recode() function
+
 countries_to_keep <- gali %>% 
-  group_by(gali$country) %>%
+  group_by(gali$country) %>% # again $ not needed 
   summarize(Count=n()) %>%
@@
 #CGI data
-gci <- import("Data/GCI_2018.xlsx")
-
-gci <- filter(gci, `Series Global ID` == "EOSQ089" |
+gci <- import("Data/GCI_2018.xlsx") %>% 
+  as_tibble() %>% 
+  filter(
+    `Series Global ID` == "EOSQ089" |
     `Series Global ID` == "EOSQ425" |
@@
     `Series Global ID` == "DOMCREDITGDP" |
-                   `Series Global ID` == "EOSQ403")
-gci <- filter(gci, Edition ==2018 )
-
-gci <- filter(gci, Attribute == "VALUE")
-gci <- select(gci, -c("Index", "Edition", "Freeze date", "Series units", "Series order", "Series code (if applicable)", "Attribute", "Series name"))
-
-gci <- gci %>%
-  gather(country, score, -`Series Global ID`)
-
-gci$country[gci$country == "United States"] <-"USA"
-
-gci <- gci %>%
-  filter(country  %in% countries_to_keep$`gali$country`)
-
-gci$score <- round(as.numeric(gci$score),2)
-
-gci <- clean_names(gci)
-
-gci <- gci %>%
-  pivot_wider(names_from = series_global_id, 
-              values_from = score)
+    `Series Global ID` == "EOSQ403",
+     Edition ==2018,
+     Attribute == "VALUE") %>% 
+  select(-c("Index", "Edition", "Freeze date", "Series units", "Series order", "Series code (if applicable)", "Attribute", "Series name")) %>% 
+  gather(country, score, -`Series Global ID`) %>% 
+  mutate(country = recode(country,
+                         "United States" = "USA")) %>%
+  filter(country  %in% countries_to_keep$`gali$country`) %>% 
+  mutate(score = round(as.numeric(score),2)) %>% 
+  clean_names() %>% 
+  pivot_wider(
+    names_from = series_global_id,
+    values_from = score
+    )
 ```
@@
 
-gali <- filter(gali, accel_ben_rank_network <= 7 & accel_ben_rank_business_skills
-<= 7 & accel_ben_rank_mentorship <= 7 & accel_ben_rank_access_investors <= 7 & accel_ben_rank_direct_funding <= 7 & accel_ben_rank_access_entreprene <= 7 & accel_ben_rank_aware_cred <= 7 )
+#newish dplyr code you might like
+gali <- gali %>% 
+   filter(if_all(starts_with("accel_ben"), ~ . <= 7))
 
@@
 gali_joined <- left_join(gali, gci, by = "country")
+
 ```
@@
 #Models
-library(lme4)
+library(lme4) #generally best practice to load all libraries at the top of the script
+
 fit0hc <- glmer(participated ~  accel_ben_rank_business_skills + (accel_ben_rank_business_skills|country), data = gali_joined, family=binomial)
@@
 The model is robust to the addition of control variables.
-Similarly, table 7 show that an increase in venture to attention social capital causes an increase in the venture's likelihood to mobilize resources within the acceleration program.
+Similarly, Table 7 show that an increase in venture to attention social capital causes an increase in the venture's likelihood to mobilize resources within the acceleration program.
 These effects are not statistically signification.
@@
 To examine our hypotheses exploring these same relationships within the institutional context of the venture, we turn to tables 2, 4, 5, 6, and 8.
-When I interact the venture level attention to human capital with the institutional level human capital (Table 2), I find that attention to this resource results in a significant increase in the likelihood to mobilize resources within the accelerator program ($b = 0.9$), and the model is robust to control variables.
-In contrast, tables 3 to 5 show that attention to financial capital has a non-significant effect on the venture's likelihood to mobilize resources regardless of the institutional context.
+When I interact the venture level attention to human capital with the institutional level human capital (Table 2), I find that attention to this resource results in a significant increase in the likelihood to mobilize resources within the accelerator program ($b = 0.9$) <!-- make this data-responsive -->, and the model is robust to control variables.
+In contrast, Tables 3 to 5 show that attention to financial capital has a non-significant effect on the venture's likelihood to mobilize resources regardless of the institutional context.
 We find the same results whether we consider institutional level capital for SMEs, VC oriented ventures, or ventures seeking loans and other forms of financing from financial establishments.
 This is in line with our initial finding that human and social capital should garner the attention of ventures seeking resources in their early stage from incubators and accelerators.
-Finally, table 8 shows us that the congruency of venture attention and the institutional level of social capital does not have any significant effect on the venture's likelihood to mobilize resources.
+Finally, Table 8 shows us that the congruence of venture attention and the institutional level of social capital does not have any significant effect on the venture's likelihood to mobilize resources.
 
@@
 I find that social and human capital are the key resources that should be on the venture's radar in their early stage of strategy formation.
-I then investigate the impact of the congruency between the venture attention and the institutional level capital to better understand these relationships within their institutional context.
+I then investigate the impact of the congruence between the venture attention and the institutional level capital to better understand these relationships within their institutional context.
 I find that human capital is not only one of the key resources to focus on but it becomes even more important if it aligns with the venture's country to provide skillful human resources.
@@
 Similar to hypothesis 1, I find no support for the second hypothesis.
-Table 9 shows the impact of venture attention to human capital and its congruency level with the institutional capital on the acquisition of human capital (total number of employees) post-acceleration program.
+Table 9 shows the impact of venture attention to human capital and its congruence level with the institutional capital on the acquisition of human capital (total number of employees) post-acceleration program.
+I find no statistically significant effect in the two models.
+Tables 10 to 12 show the impact of venture attention to financial capital and its congruence level with the institutional capital on the acquisition of financial capital (capital raised in USD) post-acceleration program.
 I find no significant effect in the two models.
-Tables 10 to 12 show the impact of venture attention to financial capital and its congruency level with the institutional capital on the acquisition of financial capital (capital raised in USD) post-acceleration program.
-I find no significant effect in the two models.
-Finally, table 13 shows the the impact of venture attention to social capital and its congruency level with the institutional capital on the acquisition of social capital (sources of capital) post-acceleration program.
-I find no significant effect in the two models.
-
-It is important to highlight here, that not only I find no significant effect but also all the coefficients are negative.
+Finally, table 13 shows the the impact of venture attention to social capital and its congruence level with the institutional capital on the acquisition of social capital (sources of capital) post-acceleration program.
+I find no statistically significant effect in the two models.
+
+It is important to highlight here, that not only I find no statistically significant effect but also all the coefficients are negative.
 This negative effect on resource acquisition post-acceleration program can be interpreted economically, as an opportunity cost.
@@
 While these efforts might result in resource acquisition, over the long-term, we would not be able to observe this within a year or two post resource mobilization.
-This is a key limitation of our data and analysis.
+This is a key limitation of our data and analyses.
 
@@
 Tables 14 to 16 confirm these expectations.
-I find only null effects of the impact of venture attention to a resource and its congruency level with the institutional level of the resource on performance (measured based on firm revenues) post acceleration program.
+I find only null effects of the impact of venture attention to a resource and its congruence level with the institutional level of the resource on performance (measured based on firm revenues) post acceleration program.
 
